### 2019-02-04 summary.tex
Initial commit of files

\documentclass[14pt]{article}
\usepackage{amsfonts}

\usepackage{mathtools}
\usepackage{cancel}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{dsfont}
\newcommand{\R}{\mathds {R}}
\title{ABM of Cournot Competition with Idiosyncratic Tax}
\author{Nate Dwyer and Sandro Lera}

\begin{document}

\maketitle
\setcounter{section}{0}
\section{Model Definition}
We simulate a basic economy of buyers and sellers by basing it on the
Cournot competition model.

The 'geography' of our model is one-dimensional with periodic boundaries, 
i.e. a topological circle. We denote the length of that circle by $L$. We 
measure physical distances with the metric $min(|x-y|, L-|y-x|)$ for 
any two points ('agents') $x$,$y$ on $L$. Without loss of generality,
we set $L=1$.

\subsection{Buyers}
On that circle we place some $|B|$ buyers randomly distributed. The buyers
all have an identical demand curve $P=a-Q$, and each buyer $b\in B$ buys a 
quantity $\vec{b}$, where $b_i$ is the amount $b$ buys from the $i$th
seller. Each buyer tries to buy as much total quantity as they can while
staying under the curve, i.e. they try to maximize $sum(\vec{b})$.

\subsection{Sellers}
On that circle we will also find some $|S|$ sellers, who all offer the same
product, but at potentially different prices and in potentially different
quantities. We denote the prices that are offered by a vector $\vec{p}$ and 
the quantities by the vector $\vec{q}$, where the $i$th seller offers $q_i$
amount of the product at a price $p_i$. Each seller chooses $q_i$ and $p_i$ 
simultaneously in an attempt to maximize profit.

\subsection{Idiosyncratic tax}
For any buyer $b$ and seller $s$, we define a product-distance $D = D(b,s)$ 
such that the seller s that is physically closest to b has distance 
$D(b,s)=1$, the next closest has distance $D=2$, and so on.

If buyer b buys from seller s, the total price, including transaction cost
(tax), is given by $p(b,s) = p_s *  D(b,s)^\gamma$ where gamma is a 
scaling coefficient.

\subsection{Profit Function}
The profit function is as follows: $\Pi_i = p_i * q_i^s - c*q_i$, where $c$
is the price to produce each unit of product, and $q_i^s$ is the quantity 
the $i$th seller sells.

\section{Setup}
We construct a set of buyers $B$ and a set of sellers $S$, and transaction cost
function $t: (B\times S)\rightarrow \R$, which has subfunctions $t_b:
S\rightarrow \R$ s.t. for all $s\in S$, $t(b,s) = t_b(s)$.

Also, we construct an demand curve for all $b\in B$, namely $P = a - Q$.

\section{Function to put into nashpy}
We construct a function $\Pi : (\R\times\R)^{|S|} \rightarrow \R^{|S|}$ s.t.
$\Pi(\vec{s}) = \vec{\pi}$, where the elements of $\vec{s}$ are the tuples
$(q_i,p_i)$ listing the quantity produced and the price offered by the $i$th
seller, and the elements of $\vec{\pi}$ are $\pi_i$, the profits of the $i$th seller.

Given $\vec{s}$, $\vec{\pi}$ is calculated by first calculating $\vec{q}^s$, the
vector of total quantity sold, then using it to calculate $\vec{\pi}$ using the formula $\pi_i = p_iq^s_i$.

$q^s_i = \sum _{b\in B} b_i$, where $b_i$ is the amount seller $b$ buys from
the $i$th seller.

Each buyer $b$ chooses a vector $\vec{b}$, where each element of the vector
$b_i$ is the amount $b$ bought from the $i$th buyer.

Set $\vec{q}^{unsold} = \vec{q}$

For each $b_i \in \vec{b}$, have it maximize the total quantity bought by $b$
while remaining under the individual demand curve $P=a-Q$.  The resulting
vector that lists the amount $b$ buys from each seller is $\vec{b}$.  Subtract $\vec{b}$ from $\vec{q}^{unsold}$ to get a new $\vec{q}^{unsold}$.

\subsection{Algorithm to determining what a buyer purchases}
To determine $\vec{b}$, do the following:

Calculate $b$'s perceived prices, $t_b(s_i) * p_i = \vec{p}^b$, then turn it
into a $|S|$ by 2 matrix $M$ with the first column being the price, $\vec{p}$
the second column being the remaining quantity, $\vec{q}^{unsold}$.

Sort $M$'s rows by the perceived price column, and re-index the rows\newline
$0, 1, \cdots , j, \cdots , |S|$.

Find the maximal index $j$ and quantity $q^{*}_j \le q^{unsold}_j$ such that
$p_j + q^{*}_j + \sum_{k=0}^j q_k \le a$.  Now we have a vector of amount
bought by $b$ as follows: $<q_0, q_1,\cdots q_{j-1}, q^{*}_j, 0, 0, \cdots, 0>.$

Finally, re-index this new vector using the $i$-index instead of the $j$ index
to get $\vec{b}$.
\end{document}

### 2019-02-04 Model_v2.0.py

@@ -1,0 +1,246 @@
+# Technical debt from pricing model. can speed up by factor of n
+# also, occasional errors in negative prices
+# improved pricing model in 1.2
+import numpy as np
+import pandas as pd
+from sklearn.externals import joblib as jl
+
+
+
+#####################
+#####################
+##### FUNCTIONS #####
+#####################
+#####################
+
+#####################
+### CALCULATE TAX ###
+#####################
+
+def circle_dist(a, b):
+    return .5-abs(abs(a-b)-.5)
+
+
+def get_m_tax():
+    # Matrix with absolute dist
+    m_dist = [[circle_dist(buyer_loc, seller_loc)
+        for buyer_loc in A_BUYER_LOC] for seller_loc in a_seller_loc]
+    # Matrix with rel dist with list of prices. '+ 1' because min dist is 1.
+    m_rel_dist = np.argsort(m_dist, axis=0) + 1.0
+    # Lot of potential speed up here, only need to do exponent once.
+    m_tax = np.array(m_rel_dist**GAMMA + 0.0)
+    return m_tax, m_rel_dist
+
+
+#######################
+### FIND NEXT PRICE ###
+#######################
+
+def update_all_prices(m_rel_price, m_tax):
+    m_price_perc_other = find_all_price_perc(m_rel_price)
+    m_price_to_beat = m_price_perc_other/m_tax
+
+    m_price_to_beat[:, ::-1].sort()
+    m_profit = m_price_to_beat * np.arange(1, 1 + m_price_to_beat.shape[1])
+    a_best_ind = m_profit.argmax(1)
+    a_prices = m_price_to_beat[range(len(a_best_ind)), a_best_ind]
+    a_prices = [np.nextafter(price, 0) for price in a_prices]
+    return a_prices
+
+def find_all_price_perc(m_rel_price):
+    a_a_ret = []
+    m_tmp = m_rel_price.T
+    for col in m_tmp:
+        minVal, minVal2 = get2minFromArray(col)
+        a_tmp = [minVal if value != minVal else minVal2 for value in col]
+        a_a_ret.append(a_tmp)
+    return np.array(a_a_ret).T
+
+def get2minFromArray(array):
+    minVal = minVal2 = np.inf
+    for value in array:
+        if value < minVal:
+            minVal2 = minVal
[…]

### 2019-02-04 summary.tex
added minor changes to tex file to show you how we can work on the document together.
Implemented Edits Sandro suggested.

@@
 \newcommand{\R}{\mathds {R}}
-\title{ABM of Cournot Competition with Idiosyncratic Tax}
+\title{Cournot Competition with Idiosyncratic Tax}
 \author{Nate Dwyer and Sandro Lera}
@@
 \section{Model Definition}
-We simulate a basic economy of buyers and sellers by basing it on the
-Cournot competition model.
+We simulate a basic economy of buyers and sellers by basing it on the Cournot
+competition model.
 
-The 'geography' of our model is one-dimensional with periodic boundaries, 
-i.e. a topological circle. We denote the length of that circle by $L$. We 
-measure physical distances with the metric $min(|x-y|, L-|y-x|)$ for 
-any two points ('agents') $x$,$y$ on $L$. Without loss of generality,
-we set $L=1$.
+The `geography' of our model is one-dimensional with periodic boundaries, i.e. a
+topological circle. We denote the length of that circle by $L$. We measure
+physical distances with the metric $min(|x-y|, L-|y-x|)$ for any two points
+('agents') $x$,$y$ on $L$. Without loss of generality, we set $L=1$.
 
 \subsection{Buyers}
-On that circle we place some $|B|$ buyers randomly distributed. The buyers
-all have an identical demand curve $P=a-Q$, and each buyer $b\in B$ buys a 
-quantity $\vec{b}$, where $b_i$ is the amount $b$ buys from the $i$th
-seller. Each buyer tries to buy as much total quantity as they can while
-staying under the curve, i.e. they try to maximize $sum(\vec{b})$.
+On that circle we place some $|B|$ buyers randomly distributed. The buyers all
+have an identical demand curve $P + Q = a$, and each buyer $b\in B$ buys a quantity
+$\vec{b}$, where $b_i$ is the amount $b$ buys from the $i$th seller. Each buyer
+tries to buy as much total quantity as they can while keeping $P + Q < a$ i.e.
+they try to maximize $\sum_{i=0}^{|S|}b_i$.
 
@@
 product, but at potentially different prices and in potentially different
-quantities. We denote the prices that are offered by a vector $\vec{p}$ and 
-the quantities by the vector $\vec{q}$, where the $i$th seller offers $q_i$
-amount of the product at a price $p_i$. Each seller chooses $q_i$ and $p_i$ 
+quantities. We denote the prices that are offered by a vector $\vec{p}$ and the
+quantities by the vector $\vec{q}$, where the $i$th seller offers $q_i$ amount
+of the product at a price $p_i$. Each seller chooses $q_i$ and $p_i$
 simultaneously in an attempt to maximize profit.
@@
 \subsection{Idiosyncratic tax}
-For any buyer $b$ and seller $s$, we define a product-distance $D = D(b,s)$ 
-such that the seller s that is physically closest to b has distance 
-$D(b,s)=1$, the next closest has distance $D=2$, and so on.
+For any buyer $b$ and seller $s$, we define a product-distance $D = D(b,s)$ such
+that the seller s that is physically closest to b has distance $D(b,s)=1$, the
+next closest has distance $D=2$, and so on.
 
 If buyer b buys from seller s, the total price, including transaction cost
-(tax), is given by $p(b,s) = p_s *  D(b,s)^\gamma$ where gamma is a 
-scaling coefficient.
+(tax), is given by $p(b,s) = p_s *  D(b,s)^\gamma$ where gamma is a scaling
+coefficient.
 
 \subsection{Profit Function}
-The profit function is as follows: $\Pi_i = p_i * q_i^s - c*q_i$, where $c$
-is the price to produce each unit of product, and $q_i^s$ is the quantity 
-the $i$th seller sells.
 
-\section{Setup}
+The profit function is as follows:
+\begin{equation}
+    $\Pi_i = p_iq_i^s - cq_i$
+\end{equation}
+where $c$ is the price to produce each unit of product, and $q_i^s$ is the
+quantity the $i$th seller sells.
+
+\section{Mathematical Representation}
 We construct a set of buyers $B$ and a set of sellers $S$, and transaction cost
@@
 
-\section{Function to put into nashpy}
+\section{Function to put into Gambit}
+
 We construct a function $\Pi : (\R\times\R)^{|S|} \rightarrow \R^{|S|}$ s.t.
@@
 $(q_i,p_i)$ listing the quantity produced and the price offered by the $i$th
-seller, and the elements of $\vec{\pi}$ are $\pi_i$, the profits of the $i$th seller.
+seller, and the elements of $\vec{\pi}$ are $\pi_i$, the profits of the $i$th
+seller.
 
 Given $\vec{s}$, $\vec{\pi}$ is calculated by first calculating $\vec{q}^s$, the
-vector of total quantity sold, then using it to calculate $\vec{\pi}$ using the formula $\pi_i = p_iq^s_i$.
+vector of total quantity sold, then using it to calculate $\vec{\pi}$ using 
+equation (1).
 
-$q^s_i = \sum _{b\in B} b_i$, where $b_i$ is the amount seller $b$ buys from
-the $i$th seller.
+$q^s_i = \sum _{b\in B} b_i$, where $b_i$ is the amount seller $b$ buys from the
+$i$th seller.
 
@@
 For each $b_i \in \vec{b}$, have it maximize the total quantity bought by $b$
-while remaining under the individual demand curve $P=a-Q$.  The resulting
-vector that lists the amount $b$ buys from each seller is $\vec{b}$.  Subtract $\vec{b}$ from $\vec{q}^{unsold}$ to get a new $\vec{q}^{unsold}$.
+while remaining under the individual demand curve $P=a-Q$.  The resulting vector
+that lists the amount $b$ buys from each seller is $\vec{b}$.  Subtract
+$\vec{b}$ from $\vec{q}^{unsold}$ to get a new $\vec{q}^{unsold}$.
 
@@
 
-Sort $M$'s rows by the perceived price column, and re-index the rows\newline
-$0, 1, \cdots , j, \cdots , |S|$.
+Sort $M$'s rows by the perceived price column, and re-index the rows\newline $0,
+1, \cdots , j, \cdots , |S|$.
 
 Find the maximal index $j$ and quantity $q^{*}_j \le q^{unsold}_j$ such that
-$p_j + q^{*}_j + \sum_{k=0}^j q_k \le a$.  Now we have a vector of amount
-bought by $b$ as follows: $<q_0, q_1,\cdots q_{j-1}, q^{*}_j, 0, 0, \cdots, 0>.$
+$p_j + q^{*}_j + \sum_{k=0}^j q_k \le a$.  Now we have a vector of amount bought
+by $b$ as follows: $<q_0, q_1,\cdots q_{j-1}, q^{*}_j, 0, 0, \cdots, 0>.$
 
@@
 to get $\vec{b}$.
+
 \end{document}

### 2019-02-05 summary.tex
adjusted the documents with several details.

@@
-\documentclass[14pt]{article}
+\documentclass[11pt]{article}
+\usepackage[a4paper,margin=2.8cm]{geometry}
 \usepackage{amsfonts}
@@
 \usepackage{amssymb}
+\usepackage{dsfont}
+\usepackage[dvipsnames,usenames]{color}
+\usepackage[colorlinks=true,linkcolor=NavyBlue,citecolor=NavyBlue,urlcolor=NavyBlue]{hyperref} % for hyperlinks
 
-\usepackage{dsfont}
+% makros 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newcommand{\R}{\mathds {R}}
-\title{Cournot Competition with Idiosyncratic Tax}
+\newcommand{\red}[1]{\textcolor{red}{#1}} % for color for remarks
+
+\title{Cournot Competition with Idiosyncratic Taxation}
+
 \author{Nate Dwyer and Sandro Lera}
@@
 \section{Model Definition}
-We simulate a basic economy of buyers and sellers by basing it on the Cournot
-competition model.
+We simulate an economy of buyers and sellers as an extension of the Cournot competition model, 
+with additional buyer-seller specific (`idiosyncratic') transaction cost (`tax'). 
+The goal of this tax is to avoid market dominance by one single seller based on initially only small differences in quality. 
+Instead, the model is aimed at striking a `fair' balance between market competition and seller protection.
 
-The `geography' of our model is one-dimensional with periodic boundaries, i.e. a
-topological circle. We denote the length of that circle by $L$. We measure
-physical distances with the metric $min(|x-y|, L-|y-x|)$ for any two points
-('agents') $x$,$y$ on $L$. Without loss of generality, we set $L=1$.
+The `geography' of our model is one-dimensional with periodic boundaries, i.e. a topological circle, of length $L$. 
+Due to the periodic boundary conditions, we measure physical distances with the metric $\min(|x-y|, L-|y-x|)$ for any two points (`agents') $x$,$y$ on $L$. 
+Without loss of generality, we set $L=1$. 
+Our model does not rely on the implemented geography, and any other, potentially more realistic topology could be considered.
 
@@
 On that circle we place some $|B|$ buyers randomly distributed. The buyers all
-have an identical demand curve $P + Q = a$, and each buyer $b\in B$ buys a quantity
+have an identical demand curve $Q+P = a$, and each buyer $b\in B$ buys a quantity
 $\vec{b}$, where $b_i$ is the amount $b$ buys from the $i$th seller. Each buyer
@@
 If buyer b buys from seller s, the total price, including transaction cost
-(tax), is given by $p(b,s) = p_s *  D(b,s)^\gamma$ where gamma is a scaling
+(tax), is given by $p(b,s) = p_s  \cdot D(b,s)^\gamma$ where $\gamma$ is a scaling
 coefficient.
@@
 
-The profit function is as follows:
+The profit function for seller $i$ reads
 \begin{equation}
-    $\Pi_i = p_iq_i^s - cq_i$
+    \Pi_i = p_iq_i^s - cq_i, 
+    \label{eq:profit_function}
 \end{equation}
-where $c$ is the price to produce each unit of product, and $q_i^s$ is the
-quantity the $i$th seller sells.
+where $c$ is the price to produce each unit of product, and $q_i^s$ is the quantity the $i$th seller sells
+(which may be less but never more than the quantity $q_i$ that was produced). 
+Below, we then introduce the profit vector $\vec{\pi} = (\pi_1, \ldots, \pi_{|S|})$
+to find the Nash-equilibrium based on the profit functions of all sellers.
 
@@
 S\rightarrow \R$ s.t. for all $s\in S$, $t(b,s) = t_b(s)$.
+\red{
+I don't see what are these sub-functions for. 
+The way I see it, a specific customer-seller tax is a mapping from $B \times S$ to $\R$.
+There is no subfunction.}
 
@@
 seller, and the elements of $\vec{\pi}$ are $\pi_i$, the profits of the $i$th
-seller.
+seller. \red{Write from seller $s$, here and everywhere else.}
 
@@
 vector of total quantity sold, then using it to calculate $\vec{\pi}$ using 
-equation (1).
+equation \eqref{eq:profit_function}.
 
+\red{(don't start a sentence like that)}
 $q^s_i = \sum _{b\in B} b_i$, where $b_i$ is the amount seller $b$ buys from the
 $i$th seller.  
+\red{Turn that thing into vectorial notation. You have two matrices, $Q$ and $Q^s$, and the same for prices. Then you have $Q_{sb}$ instead of $Q_{ji}$}
 
-Each buyer $b$ chooses a vector $\vec{b}$, where each element of the vector
+Each buyer $b$ chooses a vector $\vec{b}$, where each element
 $b_i$ is the amount $b$ bought from the $i$th buyer.
@@
 To determine $\vec{b}$, do the following:
+\red{Use a proper enumeration environment}
+
+\begin{enumerate}
+	\item bla 
+	\item bla 
+\end{enumerate}
 
@@
 
+\section{Open Questions}
+
+\begin{itemize}
+
+	\item With this model, we want to demonstrate that initially small differences in quality do not lead to proportional feedback
+		mechanisms that lead to an unequal output distribution
+		So it might be questionable if the current Cournot model is the model of our interests, 
+		because it assumes all buyers set the same price.
+
+\end{itemize}
+
 \end{document}

### 2019-02-06 summary.tex
Fixed most comments and responded to the other two.  Matrix stuff hasn't been done yet.

@@
 \usepackage{amsfonts}
-
 \usepackage{mathtools}
@@
 % makros 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newcommand{\R}{\mathds {R}}
@@
 \section{Model Definition}
-We simulate an economy of buyers and sellers as an extension of the Cournot competition model, 
-with additional buyer-seller specific (`idiosyncratic') transaction cost (`tax'). 
-The goal of this tax is to avoid market dominance by one single seller based on initially only small differences in quality. 
-Instead, the model is aimed at striking a `fair' balance between market competition and seller protection.
+We simulate an economy of buyers and sellers as an extension of the Cournot
+competition model, with additional buyer-seller specific (`idiosyncratic')
+transaction cost (`tax').  The goal of this tax is to avoid market dominance by
+one single seller based on initially only small differences in quality.
+Instead, the model is aimed at striking a `fair' balance between market
+competition and seller protection.
 
-The `geography' of our model is one-dimensional with periodic boundaries, i.e. a topological circle, of length $L$. 
-Due to the periodic boundary conditions, we measure physical distances with the metric $\min(|x-y|, L-|y-x|)$ for any two points (`agents') $x$,$y$ on $L$. 
-Without loss of generality, we set $L=1$. 
-Our model does not rely on the implemented geography, and any other, potentially more realistic topology could be considered.
+The `geography' of our model is one-dimensional with periodic boundaries, i.e. a
+topological circle, of length $L$.  Due to the periodic boundary conditions, we
+measure physical distances with the metric $\min(|x-y|, L-|y-x|)$ for any two
+points (`agents') $x$,$y$ on $L$.  Without loss of generality, we set $L=1$.
+Our model does not rely on the implemented geography, and any other, potentially
+more realistic topology could be considered.
 
@@
 On that circle we place some $|B|$ buyers randomly distributed. The buyers all
-have an identical demand curve $Q+P = a$, and each buyer $b\in B$ buys a quantity
-$\vec{b}$, where $b_i$ is the amount $b$ buys from the $i$th seller. Each buyer
-tries to buy as much total quantity as they can while keeping $P + Q < a$ i.e.
-they try to maximize $\sum_{i=0}^{|S|}b_i$.
+have an identical demand curve $P + Q = a$, and each buyer $b\in B$ buys a
+quantity $\vec{b}$, where $b_s$ is the amount $b$ buys from the seller $s$. Each
+buyer tries to buy as much total quantity as they can while keeping $P + Q \le
+a$ i.e.  they try to maximize $\sum_{i=0}^{|S|}b_s$.
 
@@
 quantities. We denote the prices that are offered by a vector $\vec{p}$ and the
-quantities by the vector $\vec{q}$, where the $i$th seller offers $q_i$ amount
-of the product at a price $p_i$. Each seller chooses $q_i$ and $p_i$
-simultaneously in an attempt to maximize profit.
+quantities by the vector $\vec{q}$, where the seller $s$ offers $q_s$ amount of
+the product at a price $p_s$. Each seller chooses $q_s$ and $p_s$ simultaneously
+in an attempt to maximize profit.
 
@@
 
-If buyer b buys from seller s, the total price, including transaction cost
-(tax), is given by $p(b,s) = p_s  \cdot D(b,s)^\gamma$ where $\gamma$ is a scaling
-coefficient.
+If buyer $b$ buys from seller $s$, the total price, including transaction cost
+(tax), is given by $p(b,s) = p_s  \cdot D(b,s)^\gamma$ where $\gamma$ is the
+scaling coefficient of the tax.
 
@@
 
-The profit function for seller $i$ reads
+The profit function for seller $s$ reads
 \begin{equation}
-    \Pi_i = p_iq_i^s - cq_i, 
+    \Pi_s = p_sq_s^{sold} - cq_s, 
     \label{eq:profit_function}
 \end{equation}
-where $c$ is the price to produce each unit of product, and $q_i^s$ is the quantity the $i$th seller sells
-(which may be less but never more than the quantity $q_i$ that was produced). 
-Below, we then introduce the profit vector $\vec{\pi} = (\pi_1, \ldots, \pi_{|S|})$
-to find the Nash-equilibrium based on the profit functions of all sellers.
+where $c$ is the price to produce each unit of product, and $q_s^{sold}$ is the
+quantity the seller $s$ sells (which may be less but never more than the
+quantity $q_s$ that was produced).  Below, we then introduce the profit vector
+$\vec{\pi} = (\pi_1, \ldots, \pi_{|S|})$ to find the Nash-equilibrium based on
+the profit functions of all sellers.
 
@@
 S\rightarrow \R$ s.t. for all $s\in S$, $t(b,s) = t_b(s)$.
-\red{
-I don't see what are these sub-functions for. 
-The way I see it, a specific customer-seller tax is a mapping from $B \times S$ to $\R$.
-There is no subfunction.}
+\red{ I don't see what are these sub-functions for.  The way I see it, a
+specific customer-seller tax is a mapping from $B \times S$ to $\R$.  There is
+no subfunction. NATE Response: $t_b$ is used in the Algorithm part.}
 
@@
 $\Pi(\vec{s}) = \vec{\pi}$, where the elements of $\vec{s}$ are the tuples
-$(q_i,p_i)$ listing the quantity produced and the price offered by the $i$th
-seller, and the elements of $\vec{\pi}$ are $\pi_i$, the profits of the $i$th
-seller. \red{Write from seller $s$, here and everywhere else.}
+$(q_s,p_s)$ listing the quantity produced and the price offered by the seller
+$s$, and the elements of $\vec{\pi}$ are $\pi_s$, the profits of the seller $s$.
 
-Given $\vec{s}$, $\vec{\pi}$ is calculated by first calculating $\vec{q}^s$, the
-vector of total quantity sold, then using it to calculate $\vec{\pi}$ using 
-equation \eqref{eq:profit_function}.
+Given $\vec{s}$, $\vec{\pi}$ is calculated by first calculating
+$\vec{q}^{sold}$, the vector of total quantity sold, then using it to calculate
+$\vec{\pi}$ using equation \eqref{eq:profit_function}.
 
-\red{(don't start a sentence like that)}
-$q^s_i = \sum _{b\in B} b_i$, where $b_i$ is the amount seller $b$ buys from the
-$i$th seller.  
-\red{Turn that thing into vectorial notation. You have two matrices, $Q$ and $Q^s$, and the same for prices. Then you have $Q_{sb}$ instead of $Q_{ji}$}
+Calculate $\vec{q}^{sold} = \sum _{b\in B} \vec{b}$, where $\vec{b}$ represents
+the amount buyer $b$ buys from each seller. 
+\red{You have two matrices, $Q$ and $Q^{sold}$, and the same for prices. Then
+you have $Q_{sb}$ instead of $Q_{ji}$. NATE Response: currently, I think it
+might be clearer with vectors.  If we do go to matrices, then we should probably
+go there for price as well, and we can get rid of the subfunctions that way.}
 
-Each buyer $b$ chooses a vector $\vec{b}$, where each element
-$b_i$ is the amount $b$ bought from the $i$th buyer.
+\subsection{Algorithm to calculate $\vec{q}^{sold}$}
 
-Set $\vec{q}^{unsold} = \vec{q}$
+To determine $\vec{b}$, do the following:
 
-For each $b_i \in \vec{b}$, have it maximize the total quantity bought by $b$
+For each $b_s \in \vec{b}$, have it maximize the total quantity bought by $b$
 while remaining under the individual demand curve $P=a-Q$.  The resulting vector
@@
 
-\subsection{Algorithm to determining what a buyer purchases}
-To determine $\vec{b}$, do the following:
-\red{Use a proper enumeration environment}
-
 \begin{enumerate}
-	\item bla 
-	\item bla 
+    \item Set $\vec{q}^{unsold} = \vec{q}$ to start.
+    \item For each $b\in B$:
+	\item Calculate $b$'s perceived prices: $t_b(s_s) * p_s = \vec{p}^b$.  
+    \item Turn $\vec{p}^b$ into a $|S|$ by 2 matrix $M$ with the first column
+        being the price, $\vec{p}$ the second column being the remaining
+        quantity, $\vec{q}^{unsold}$. 
+    \item Sort $M$'s rows by the perceived price column, and re-index the
+        rows $0, 1, \cdots , i, \cdots , |S|$. 
+    \item Find the maximal index $i$ and quantity $q^{*}_i \le q^{unsold}_i$
+        such that $p_i + q^{*}_i + \sum_{k=0}^i q_k \le a$. 
+    \item Now we have a vector $\vec{b}'$ of amount bought by $b$ : $\vec{b}' =
+        <q_0, q_1,\cdots q_{j-1}, q^{*}_i, 0, 0, \cdots, 0>.$
+    \item Re-index this new vector using the seller order instead of the price
+        index to get $\vec{b}$.
+    \item Set $\vec{q}^{unsold} = \vec{q}^{unsold}-\vec{b}$.
+    \item Go to step 3.
+    \item Calculate $\vec{q}^{sold} = \sum _{b\in B} \vec{b}$.
+    \item Calculate $\vec{\Pi} = \vec{p}\vec{q}^{sold} - c\vec{q}$, 
 \end{enumerate}
-
-Calculate $b$'s perceived prices, $t_b(s_i) * p_i = \vec{p}^b$, then turn it
-into a $|S|$ by 2 matrix $M$ with the first column being the price, $\vec{p}$
-the second column being the remaining quantity, $\vec{q}^{unsold}$.
-
-Sort $M$'s rows by the perceived price column, and re-index the rows\newline $0,
-1, \cdots , j, \cdots , |S|$.
-
-Find the maximal index $j$ and quantity $q^{*}_j \le q^{unsold}_j$ such that
-$p_j + q^{*}_j + \sum_{k=0}^j q_k \le a$.  Now we have a vector of amount bought
-by $b$ as follows: $<q_0, q_1,\cdots q_{j-1}, q^{*}_j, 0, 0, \cdots, 0>.$
-
-Finally, re-index this new vector using the $i$-index instead of the $j$ index
-to get $\vec{b}$.
 
@@
 
-	\item With this model, we want to demonstrate that initially small differences in quality do not lead to proportional feedback
-		mechanisms that lead to an unequal output distribution
-		So it might be questionable if the current Cournot model is the model of our interests, 
-		because it assumes all buyers set the same price.
+    \item With this model, we want to demonstrate that initially small
+        differences in quality do not lead to proportional feedback mechanisms
+        that lead to an unequal output distribution So it might be questionable
+        if the current Cournot model is the model of our interests, because it
+        assumes all buyers set the same price.
 

### 2019-02-07 Model_v2.0.py
The profit function and its subfunctions are done. Also I removed all of the useless stuff.

@@ -20,95 +20,68 @@ from sklearn.externals import joblib as jl
 def circle_dist(a, b):
     return .5-abs(abs(a-b)-.5)
 
-
-def get_m_tax():
+def get_m_tax(a_buyer_loc, a_seller_loc, gamma=GAMMA):
     # Matrix with absolute dist
     m_dist = [[circle_dist(buyer_loc, seller_loc)
-        for buyer_loc in A_BUYER_LOC] for seller_loc in a_seller_loc]
+        for buyer_loc in a_buyer_loc] for seller_loc in a_seller_loc]
     # Matrix with rel dist with list of prices. '+ 1' because min dist is 1.
     m_rel_dist = np.argsort(m_dist, axis=0) + 1.0
     # Lot of potential speed up here, only need to do exponent once.
-    m_tax = np.array(m_rel_dist**GAMMA + 0.0)
-    return m_tax, m_rel_dist
+    m_tax = np.array(m_rel_dist**gamma, dtype=float)
+    return m_tax
 
 
-#######################
-### FIND NEXT PRICE ###
-#######################
+###################
+### FIND BUNDLE ###
+###################
 
-def update_all_prices(m_rel_price, m_tax):
-    m_price_perc_other = find_all_price_perc(m_rel_price)
-    m_price_to_beat = m_price_perc_other/m_tax
-
-    m_price_to_beat[:, ::-1].sort()
-    m_profit = m_price_to_beat * np.arange(1, 1 + m_price_to_beat.shape[1])
-    a_best_ind = m_profit.argmax(1)
-    a_prices = m_price_to_beat[range(len(a_best_ind)), a_best_ind]
-    a_prices = [np.nextafter(price, 0) for price in a_prices]
-    return a_prices
-
-def find_all_price_perc(m_rel_price):
-    a_a_ret = []
-    m_tmp = m_rel_price.T
-    for col in m_tmp:
-        minVal, minVal2 = get2minFromArray(col)
-        a_tmp = [minVal if value != minVal else minVal2 for value in col]
-        a_a_ret.append(a_tmp)
-    return np.array(a_a_ret).T
-
-def get2minFromArray(array):
-    minVal = minVal2 = np.inf
-    for value in array:
-        if value < minVal:
-            minVal2 = minVal
-            minVal = value
-        elif value < minVal2:
-            minVal2 = value
[…]

### 2019-02-07 IC2S2_abstract/IC2S2_abstract.tex
added abstract for IC2S2 conference

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{mathptmx}
\usepackage[singlespacing]{setspace}
\usepackage[headheight=1in,margin=1in]{geometry}
\usepackage{fancyhdr}

\usepackage{amssymb}
\usepackage{enumerate}  
\usepackage[shortlabels]{enumitem} 
\usepackage[dvipsnames,usenames]{color}
\usepackage{comment}

\newcommand{\red}[1]{\textcolor{red}{#1}} % for color for remarks

\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\chead{%
  $5$$^{th}$ International Conference on Computational Social Science IC$^{2}$S$^{2}$\\
  July 17-20, 2019, University of Amsterdam, The Netherlands%
}

\graphicspath{{images/}}

\title{Decentralised Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}

\author[]{} % Please leave Author-field blank for blind review and remove information that may identify the author(s)

\date{}

\begin{document}

\maketitle
\thispagestyle{fancy}

\vspace{-6em}
\begin{center}
\textbf{\textit{Keywords: decentralised exchange, fair competition, game theory, Cournot economy, bipartite network}} 
\newline
\end{center}

\section*{Extended Abstract}

Until not too long ago, people used to live in more self-contained villages, with local markets where people buy different products. 
Take clothing as an example. Most villages had one or several clothing merchants competing for customers. 
There is some healthy competition among merchants within a village, as people can flexibly switch according to prices and preferences.
But customers would hardly buy clothing from a far-away village, as the `transaction cost' associated with visiting that village would be high, 
and could not offset a marginally better price or quality. 
On the other hand, people living far away from any village are disadvantaged as they always incur such high costs.
Similarly, if there is a more specialised product that can only be produced in some villages, it was harder to find customers across village borders, 
making it overall harder for new products and technologies to succeed.

From the industrial to the technological revolution, more efficient distribution channels have emerged, enabling people to buy almost any product in online-stores. 
Independent of a customer's physical location, orders get delivered to their door often even within a day. 
More specialised products are now sold globally, and people living far away from hubs benefit from a wide range of products. 
While such efficiencies are beneficial for the economy as a whole, it comes at the cost of potential centralisation and monopolies. 
Consider a merchant that manages to sell a product for some cents cheaper than its competitors.
Given modern distribution channels, and ignoring potential differences in quality, every buyer is now incentivised to buy from that one seller at that cheaper price.
One potential outcome is that the competitors follow along, increase their efficiency, and a new equilibrium is reached. 
However, in a less optimal scenario, that one seller leverages the temporarily increased revenue to further outpace and potentially undercut its competitors. 
In short-time, feedback mechanisms kick in, and an initially minor gap in competitive advantage, mixed with efficient distribution channels, manifests itself in a major monopoly situation.

We conclude that geographical constraints can lead to unfair and inefficient conditions for the customers, whereas removal of those constraints can lead to unfair conditions for the sellers. 
In this work, we show that a good trade-off is based on the integration of two rather unusual concepts:
\begin{enumerate}[(i),topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]

	\item quenched localisation of buyers and sellers,

	\item and a buyer-seller specific trading cost.

\end{enumerate}

Specifically, we first select any topology on which some $|B|$ buyers and $|S|$ sellers are located. 
This topology may be either natural, as in the real physical world, or imposed, for instance on top of a digital market place.  
Buyers and sellers are now distributed on that topology, either at random or at their choice, depending on the model set-up. 
For the remainder of the simulation, their location is then held fixed, or at least assumed to change on a much slower time-scale than numerous transactions with clients (quenched order).

We then introduce a distance metric on that topology, which we shall call the \textit{physical metric}, as it would correspond (for instance) to actual physical distances in a real world topology. 
For any buyer $b \in B$ on that topology, we can now measure the physical distance $d_{bs}$ to any seller $s \in S$. 
By sorting these physical distances, we create a \textit{taxation metric}, which assigns a distance $D_{bs}=1$ 
to the seller $s \in S$ that is physically closest to $b$, a distance $D_{b\tilde{s}}=2$ for seller $\tilde{s} \in S$ that is physically 2nd-closest to $b$, and so forth. 
If buyer $b$ wants to buy from seller $\hat{s} \in S$ who is physically $n$-th closest to $b$, $D_{b \hat{s}}=n$, 
we impose a transaction cost proportional to $n^\gamma$, where $\gamma \geqslant 0$ is a model parameter. 
This taxation comes with the advantage that sellers which are physically further away from any seller pay the same transaction price as the ones that are physically closer. 
The special case $\gamma = 0$ recovers a non-localised economy where buyers can buy from all sellers for the same transaction cost. 
The other extreme is $\gamma=\infty$, for which buyers can only buy from their physically closest seller. 
A value of $\gamma \in (0, \infty)$ represents an interpolation between those two extremes, where closer buyers are preferred, but can be outpaced by other sellers with lower prices or better quality. 
The remaining model specifications (supply, demand, quantities produces) are such that for $\gamma = 0$ the well-known Cournot competition model from basic game-theory is recovered.

Through tuning of $\gamma$ and targeted redistribution of tax money from transaction costs, we show that this model is able to fuel a self-consistent economy, 
with fair competition, where innovations can spread across the topology freely, but without the chance of monopolies emerging through disproportional feedback mechanisms.

\red{
@Nate: I am thinking of replacing the `Decentralised' in the title by something like `balanced', to avoid false association with over-hyped blockchain technology.
}

\end{document}

### 2019-02-08 IC2S2_abstract/IC2S2_abstract.tex
Fixed some minor problems, mainly some 'ise'-> 'ize'. A few other things were clarified and I added some notes in red to go over, some for me and some for you.

@@
 
-\title{Decentralised Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}
+\title{Decentralized Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}
 
@@
 
+\red{Add ABM to keywords?}
+
 Until not too long ago, people used to live in more self-contained villages, with local markets where people buy different products. 
@@
 There is some healthy competition among merchants within a village, as people can flexibly switch according to prices and preferences.
-But customers would hardly buy clothing from a far-away village, as the `transaction cost' associated with visiting that village would be high, 
+But customers would rarely buy clothing from a faraway village, as the transaction cost associated with visiting that village would be high, 
 and could not offset a marginally better price or quality. 
 On the other hand, people living far away from any village are disadvantaged as they always incur such high costs.
-Similarly, if there is a more specialised product that can only be produced in some villages, it was harder to find customers across village borders, 
-making it overall harder for new products and technologies to succeed.
+Similarly, if there is a specialized product that can only be produced in some villages, it was harder to find customers across village borders, 
+making it harder for new products and technologies to succeed.
 
-From the industrial to the technological revolution, more efficient distribution channels have emerged, enabling people to buy almost any product in online-stores. 
-Independent of a customer's physical location, orders get delivered to their door often even within a day. 
-More specialised products are now sold globally, and people living far away from hubs benefit from a wide range of products. 
-While such efficiencies are beneficial for the economy as a whole, it comes at the cost of potential centralisation and monopolies. 
-Consider a merchant that manages to sell a product for some cents cheaper than its competitors.
-Given modern distribution channels, and ignoring potential differences in quality, every buyer is now incentivised to buy from that one seller at that cheaper price.
+From the industrial to the technological revolution, more efficient distribution channels have emerged, enabling people to buy almost any product in online stores. 
+Independent of a customer's physical location, orders can be delivered to their door within a day. 
+More specialized products are now sold globally, and people living far away from hubs benefit from the availability of a wide range of products. 
+While such efficiency is beneficial for the economy as a whole, it comes at the
+cost of potential centralization \red{of what?} and monopolies. 
+Consider a merchant that manages to sell a product for a few cents cheaper than its competitors. 
+Given modern distribution channels, and ignoring potential differences in quality, every buyer is now incentivized to buy from that one seller at that cheaper price.
 One potential outcome is that the competitors follow along, increase their efficiency, and a new equilibrium is reached. 
 However, in a less optimal scenario, that one seller leverages the temporarily increased revenue to further outpace and potentially undercut its competitors. 
-In short-time, feedback mechanisms kick in, and an initially minor gap in competitive advantage, mixed with efficient distribution channels, manifests itself in a major monopoly situation.
+In the short term, feedback mechanisms kick in, and an initially minor gap in competitive advantage, mixed with efficient distribution channels, manifests itself in a major monopoly situation.
 
-We conclude that geographical constraints can lead to unfair and inefficient conditions for the customers, whereas removal of those constraints can lead to unfair conditions for the sellers. 
+We conclude that geographical constraints can lead to unfair and inefficient conditions for the customers, whereas removal of those constraints can lead to unfair conditions for the sellers \red{maybe swap this with a comment about monopolies}.
 In this work, we show that a good trade-off is based on the integration of two rather unusual concepts:
@@
 
-	\item quenched localisation of buyers and sellers,
+	\item quenched localization of buyers and sellers,
 
@@
 
-Specifically, we first select any topology on which some $|B|$ buyers and $|S|$ sellers are located. 
+Specifically, we first select any topology \red{not all topologies, need a distance metric} on which some $|B|$ buyers and $|S|$ sellers are located. 
 This topology may be either natural, as in the real physical world, or imposed, for instance on top of a digital market place.  
@@
 For any buyer $b \in B$ on that topology, we can now measure the physical distance $d_{bs}$ to any seller $s \in S$. 
-By sorting these physical distances, we create a \textit{taxation metric}, which assigns a distance $D_{bs}=1$ 
-to the seller $s \in S$ that is physically closest to $b$, a distance $D_{b\tilde{s}}=2$ for seller $\tilde{s} \in S$ that is physically 2nd-closest to $b$, and so forth. 
+By sorting these physical distances, we create a \textit{taxation metric}, which assigns a distance $D_{bs}=1$ to the seller $s \in S$ that is physically closest to $b$, a distance $D_{b\tilde{s}}=2$ for seller $\tilde{s} \in S$ that is physically 2nd-closest to $b$, and so forth.
 If buyer $b$ wants to buy from seller $\hat{s} \in S$ who is physically $n$-th closest to $b$, $D_{b \hat{s}}=n$, 
 we impose a transaction cost proportional to $n^\gamma$, where $\gamma \geqslant 0$ is a model parameter. 
-This taxation comes with the advantage that sellers which are physically further away from any seller pay the same transaction price as the ones that are physically closer. 
-The special case $\gamma = 0$ recovers a non-localised economy where buyers can buy from all sellers for the same transaction cost. 
+This taxation comes with the advantage that sellers which are physically further
+away from any seller pay the same transaction price as the ones that are
+physically closer \red{this sentence is awkward}. 
+The special case $\gamma = 0$ recovers a non-localized economy where buyers can buy from all sellers for the same transaction cost. 
 The other extreme is $\gamma=\infty$, for which buyers can only buy from their physically closest seller. 
@@
 \red{
-@Nate: I am thinking of replacing the `Decentralised' in the title by something like `balanced', to avoid false association with over-hyped blockchain technology.
+@Nate: I am thinking of replacing the `Decentralized' in the title by something like `balanced', to avoid false association with over-hyped blockchain technology.
+@Sandro: That's a good idea.
 }

### 2019-02-08 IC2S2_abstract/IC2S2_abstract.tex
incorporated Nate's feedback to the abstract

@@
 \begin{center}
-\textbf{\textit{Keywords: decentralised exchange, fair competition, game theory, Cournot economy, bipartite network}} 
+\textbf{\textit{Keywords: decentralised exchange, game theory, Cournot economy, agent based model, monopoly}} 
 \newline
@@
 \section*{Extended Abstract}
-
-\red{Add ABM to keywords?}
 
@@
 More specialized products are now sold globally, and people living far away from hubs benefit from the availability of a wide range of products. 
-While such efficiency is beneficial for the economy as a whole, it comes at the
-cost of potential centralization \red{of what?} and monopolies. 
+While such efficiency is beneficial for the economy as a whole, it comes at the cost of potential monopolies. 
 Consider a merchant that manages to sell a product for a few cents cheaper than its competitors. 
@@
 One potential outcome is that the competitors follow along, increase their efficiency, and a new equilibrium is reached. 
-However, in a less optimal scenario, that one seller leverages the temporarily increased revenue to further outpace and potentially undercut its competitors. 
+However, in a suboptimal scenario, that one seller leverages the temporarily increased revenue to further outpace and potentially undercut its competitors. 
 In the short term, feedback mechanisms kick in, and an initially minor gap in competitive advantage, mixed with efficient distribution channels, manifests itself in a major monopoly situation.
 
-We conclude that geographical constraints can lead to unfair and inefficient conditions for the customers, whereas removal of those constraints can lead to unfair conditions for the sellers \red{maybe swap this with a comment about monopolies}.
+We conclude that geographical constraints can lead to unfair and inefficient conditions for the customers, whereas removal of those constraints can lead to monopolies. 
 In this work, we show that a good trade-off is based on the integration of two rather unusual concepts:
@@
 
-	\item quenched localization of buyers and sellers,
+	\item fixed localization of buyers and sellers,
 
-	\item and a buyer-seller specific trading cost.
+	\item and a idiosyncratic buyer-seller transaction cost.
 
@@
 
-Specifically, we first select any topology \red{not all topologies, need a distance metric} on which some $|B|$ buyers and $|S|$ sellers are located. 
+Specifically, we first select any topology on which some $|B|$ buyers and $|S|$ sellers are located. 
 This topology may be either natural, as in the real physical world, or imposed, for instance on top of a digital market place.  
@@
 we impose a transaction cost proportional to $n^\gamma$, where $\gamma \geqslant 0$ is a model parameter. 
-This taxation comes with the advantage that sellers which are physically further
-away from any seller pay the same transaction price as the ones that are
-physically closer \red{this sentence is awkward}. 
+Instead of physical distances dictating a high transaction cost, the cost of buying a good is now only dependent on the relative distance. 
 The special case $\gamma = 0$ recovers a non-localized economy where buyers can buy from all sellers for the same transaction cost. 
@@
 A value of $\gamma \in (0, \infty)$ represents an interpolation between those two extremes, where closer buyers are preferred, but can be outpaced by other sellers with lower prices or better quality.
-The remaining model specifications (supply, demand, quantities produces) are such that for $\gamma = 0$ the well-known Cournot competition model from basic game-theory is recovered.
+The remaining model specifications (supply, demand, quantities produces) are such that for $\gamma = 0$ the well-known Cournot competition model from game-theory is recovered.
 
@@
 \red{
-@Nate: I am thinking of replacing the `Decentralized' in the title by something like `balanced', to avoid false association with over-hyped blockchain technology.
-@Sandro: That's a good idea.
+@Sandy: We are thinking of replacing the `Decentralized' in the title by something like `balanced', to avoid false association with over-hyped blockchain technology.
+What are your thoughts?
 }

### 2019-02-08 Model_v2.0.py
Adds heatmap and example with two sellers.

@@ -1,11 +1,29 @@
 # Technical debt from pricing model. can speed up by factor of n
 # also, occasional errors in negative prices
 # improved pricing model in 1.2
+from matplotlib import pyplot as plt
 import numpy as np
 import pandas as pd
+import seaborn as sns
 from sklearn.externals import joblib as jl
 
 
+
+
+# CONSTANTS 
+NUM_BUYERS = 100
+NUM_SELLERS = 20
+#A_BUYER_LOC = np.random.rand(NUM_BUYERS)
+#A_SELLER_LOC = np.random.rand(NUM_SELLERS)
+COST = 1
+GAMMA = 0
+SLOPE = 1
+ENDOWMENT = 2
+
+a_seller_loc = [.2, .7]
+a_buyer_loc = [.2, .2, .2, .2, .2, .7, .7, .7, .7, .7]
+SELLER_PRICE = 1
+SELLER_QUANTITY = 10
 
 #####################
 #####################
@@ -66,6 +84,8 @@ def find_quantity_sold(a_quantity, m_price_rel):
     for col in m_price_rel.T:
         a_quantity_bought = find_bundle(a_quantity_unsold, col)
         a_quantity_unsold = a_quantity_unsold - a_quantity_bought
+        if sum(a_quantity_unsold) <= 0:
+            return a_quantity
     a_quantity_sold = a_quantity - a_quantity_unsold
     return a_quantity_sold
 
@@ -79,10 +99,21 @@ def find_profit(a_quantity, a_price, m_tax, cost):
     a_quantity_sold = find_quantity_sold(a_quantity, m_price_rel)
     a_revenue = a_price * a_quantity_sold
     a_cost = cost * a_quantity
-    a_quantity_unsold = a_quantity - a_quantity_sold
     a_profit = a_revenue - a_cost
     return a_profit
 
+def find_profit_2(seller0_price, seller0_quantity, seller1_price, seller1_quantity, m_tax, cost):
+    a_profit = find_profit(np.array([seller0_quantity, seller1_quantity]),
+            np.array([seller0_price, seller1_price]), m_tax, cost)
+    return a_profit[1]
+
+
+def heatmap(a_price_range, a_quantity_range, seller0_price, seller0_quantity, m_tax, cost):
[…]

### 2019-02-11 Model_v2.0.py
Fixed two bugs in find_bundle. One was a spelling mistake, the other was referring to the wrong variable.

@@ -23,7 +23,10 @@ ENDOWMENT = 2
 a_seller_loc = [.2, .7]
 a_buyer_loc = [.2, .2, .2, .2, .2, .7, .7, .7, .7, .7]
 SELLER_PRICE = 1
-SELLER_QUANTITY = 10
+SELLER_QUANTITY = 20.
+
+A_SELLER_PRICES = np.arange(1,2.1,.1)
+A_SELLER_QUANTITIES = np.arange(0,12,.5)
 
 #####################
 #####################
@@ -54,11 +57,11 @@ def get_m_tax(a_buyer_loc, a_seller_loc, gamma=GAMMA):
 ###################
 
 def find_bundle(a_quantity_unsold, a_price_rel, endowment = ENDOWMENT):
-    a_quantity_order = np.argsort(a_quantity_unsold)
+    a_quantity_order = np.argsort(a_price_rel)
     tot_quantity = 0
     a_quantity_bought = [0.] * len(a_quantity_unsold)
     for ind in a_quantity_order:
-        tot_quanity = sum(a_quantity_bought)
+        tot_quantity = sum(a_quantity_bought)
         demand_remaining = endowment - tot_quantity - a_price_rel[ind]
         if demand_remaining <= 0:
             return a_quantity_bought
@@ -67,9 +70,7 @@ def find_bundle(a_quantity_unsold, a_price_rel, endowment = ENDOWMENT):
             return a_quantity_bought
         else:
             a_quantity_bought[ind] = a_quantity_unsold[ind]
-
-
-
+    return a_quantity_bought
 
 
 ##########################
@@ -112,7 +113,7 @@ def heatmap(a_price_range, a_quantity_range, seller0_price, seller0_quantity, m_
     heat = [[find_profit_2(seller0_price, seller0_quantity, price_tmp,
         quantity_tmp, m_tax, cost) for quantity_tmp in a_quantity_range]
         for price_tmp in reversed(a_price_range)]
-    return(sns.heatmap(heat))
+    return(sns.heatmap(heat, annot=True))
     
 
 ##################
@@ -125,8 +126,9 @@ print(np.arange(.1,2,.1))
 plt.figure(figsize=(20, 20))
 m_tax = get_m_tax(a_buyer_loc, a_seller_loc, GAMMA)
 
[…]

### 2019-03-05 bar_plots.py
Refactored much make_dic_of_pure_nash into another function, find_profit_handler_nash. Renamed find_profit_handler -> find_profit_handler_ind. Also changed it's output to a dictionary so to make the final creation easer, and altered other functions so they would still work. Moved find_profit_handler* functions to be next to each other. Expanded final pickle file. Still need to find how many buyers each seller has.

@@ -1,0 +1,59 @@
+import os
+import sys
+import pickle
+import numpy  as np
+import pandas as pd
+import seaborn as sb
+from matplotlib import pyplot as plt
+from pprint     import pprint as pp
+from sklearn.externals import joblib as jl
+from itertools  import product,combinations
+
+# Import data
+file_path = "/home/nate/Desktop/"
+file_name = file_path + "here.pickle"
+d_load = jl.load(file_name)
+
+sb.set_style("darkgrid")
+
+cost       = d_load['cost']
+gamma      = d_load['gamma']
+endowment  = d_load['endowment']
+num_sellers= d_load['num_sellers']
+num_buyers = d_load['num_buyers']
+a_price      = d_load['a_price_nash']
+a_quantity      = d_load['a_quantity_nash']
+a_quantity_sold = d_load['a_quantity_sold']
+a_profit = d_load['a_profit']
+
+N       = len(a_price) # number of sellers
+x       = np.arange(1,N+1)
+colors  = sb.color_palette("deep",3)
+w       = 0.2
+
+fig = plt.figure(figsize=(14,5))
+fig.suptitle('Gamma={}, Cost/unit={}, endowment={}, #Sellers={}, #Buyers={}'.format(gamma, cost, endowment, num_sellers, num_buyers))
+ax  = plt.gca()
+ax2 = ax.twinx()
+ax3 = ax.twinx()
+ax2.grid(False)
+ax3.grid(False)
+
+
+ax.bar( x-w, a_price,          width=w,  color=colors[0],  alpha=1.0,  align='center' )
+ax.bar( x-w, cost,             width=w,  color='black',    alpha=0.2,  align='center' )
+ax2.bar(x, a_profit,         width=w,  color=colors[1],  alpha=1.0,  align='center' )
+ax3.bar(x+w, a_quantity,       width=w,  color=colors[2],  alpha=1.0,  align='center' )
+ax3.bar(x+w, a_quantity_sold,  width=w,  color='black',    alpha=0.2,  align='center' )
+
+#ax.axhline(y=cost, color=colors[0], linestyle=':')
+
+
+
+ax.set_xlabel('sellers',                        fontsize=13)
+ax.set_ylabel('prices',      color = colors[0], fontsize=13)
+ax2.set_ylabel('profit',     color = colors[1], fontsize=13)
+ax3.set_ylabel('quantities', color = colors[2], fontsize=13)
+ax.autoscale(tight=True)
+
+plt.show()

### 2019-03-05 model.py

@@ -11,17 +11,16 @@ NUM_BUYERS = 100
 NUM_SELLERS = 2
 COST = 10
 GAMMA = 0
-SLOPE = 1
 ENDOWMENT = 20
 
 ## Setup Constants
-a_seller_loc = [.2, .7]
-a_buyer_loc = [.2, .2, .2, .2, .2, .7, .7, .7, .7, .7]
+a_seller_loc = [.2, .7, .9]
+a_buyer_loc = [.2, .2, .2, .9, .7, .7, .7, .9, .9, ]
 SELLER_PRICE = 1
 SELLER_QUANTITY = 5
 
-A_SELLER_PRICES = np.array([15,14])
-A_SELLER_QUANTITIES = np.arange(40,60,10)
+A_SELLER_PRICES = np.array([12, 12.5, 13.1, 14.0])
+A_SELLER_QUANTITIES = np.array([40.1, 50, 60, 70])
 FILE_OUT = '/home/nate/Desktop/here.pickle'
 
 
@@ -114,6 +113,54 @@ def heatmap(a_price_range, a_quantity_range, seller0_price, seller0_quantity, **
     return(sns.heatmap(heat, annot=True, fmt = '.3g'))
 
 
+###############################
+### HANDLER FOR FIND PROFIT ###
+###############################
+
+def find_profit_handler_ind(a_ind_game_table, a_strat_quantity, a_strat_price,
+        **kwargs):
+    a_ind_quantity, a_ind_price = arrayInd_to_array2Ind(np.array(a_ind_game_table),
+            len(a_strat_quantity), len(a_strat_price))
+    a_quantity = np.array([a_strat_quantity[ind] for ind in a_ind_quantity])
+    a_price = np.array([a_strat_price[ind] for ind in a_ind_price])
+    a_profit, a_quantity_sold = find_profit(a_quantity, a_price, **kwargs)
+    ret = {'a_profit' : a_profit,
+           'a_quantity_nash' : a_quantity,
+           'a_price_nash' : a_price,
+           'a_quantity_sold' : a_quantity_sold}
+    return ret
+
+def find_profit_handler_nash(nash, a_strat_quantity, a_strat_price,
+        num_sellers, **kwargs):
+    print(nash)
+    if len(nash) == 0:
+        raise Exception('Problem with  Nash Equilibrium : No pure Nash Equilibrium found.  Nash Data = {}'.format(nash))
[…]

### 2019-03-06 bar_plots.py
improved plotting file, added circle plot.

@@ -1,59 +1,143 @@
 import os
 import sys
 import pickle
+
 import numpy  as np
 import pandas as pd
 import seaborn as sb
+
 from matplotlib import pyplot as plt
 from pprint     import pprint as pp
 from sklearn.externals import joblib as jl
-from itertools  import product,combinations
 
-# Import data
-file_path = "/home/nate/Desktop/"
-file_name = file_path + "here.pickle"
-d_load = jl.load(file_name)
+from itertools  import product,combinations
 
 sb.set_style("darkgrid")
 
-cost       = d_load['cost']
-gamma      = d_load['gamma']
-endowment  = d_load['endowment']
-num_sellers= d_load['num_sellers']
-num_buyers = d_load['num_buyers']
-a_price      = d_load['a_price_nash']
+# import data
+########################################################################################################################
+file_path 		= "/home/nate/Desktop/"
+file_name 		= file_path + "here.pickle"
+d_load 			= jl.load(file_name)
+
+cost       		= d_load['cost']
+gamma      		= d_load['gamma']
+endowment  		= d_load['endowment']
+num_sellers 	= d_load['num_sellers']
+num_buyers 		= d_load['num_buyers']
+a_price      	= d_load['a_price_nash']
 a_quantity      = d_load['a_quantity_nash']
 a_quantity_sold = d_load['a_quantity_sold']
-a_profit = d_load['a_profit']
+a_profit 		= d_load['a_profit']
+
+
+# set figure size
+####################################################################################################################
+nrow 			= 2
+ncol 			= 2
+width_scale		= 6
+height_scale	= 4
+figsize 		= (width_scale*ncol,height_scale*nrow)
+
+# create the plot window
+####################################################################################################################
+plt.clf()
+plt.rc('text', usetex=True)
+fig = plt.figure(figsize=figsize)
+fig.subplots_adjust(hspace=.12, wspace=0.4)
+
+# set all axes instances
+####################################################################################################################
+circle_axis   	= plt.subplot2grid( (nrow,ncol), (0,0) )
+price_axis    	= plt.subplot2grid( (nrow,ncol), (1,0) )
+profit_axis		= plt.subplot2grid( (nrow,ncol), (2,0) )
[…]

### 2019-03-06 writing/IC2S2_abstract/IC2S2_abstract.tex
added subfolder structure, made plots work.

--- 2019-02-08 IC2S2_abstract/IC2S2_abstract.tex
@@
 
-\title{Decentralized Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}
+\title{Fair, Stable Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}
 
@@
 We conclude that geographical constraints can lead to unfair and inefficient conditions for the customers, whereas removal of those constraints can lead to monopolies. 
-In this work, we show that a good trade-off is based on the integration of two rather unusual concepts:
+In this work, we show that we can avoid both unfairness and monopolies at relatively small cost based on two rather unusual concepts:
+
 \begin{enumerate}[(i),topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
@@
 
-	\item and a idiosyncratic buyer-seller transaction cost.
+	\item and an idiosyncratic buyer-seller transaction cost.
 
@@
 
-Through tuning of $\gamma$ and targeted redistribution of tax money from transaction costs, we show that this model is able to fuel a self-consistent economy, 
+Through tuning of $\gamma$ and targeted redistribution of tax money to regions of low economic activity, we show that this model is able to fuel a self-consistent economy, 
 with fair competition, where innovations can spread across the topology freely, but without the chance of monopolies emerging through disproportional feedback mechanisms. 
-
-\red{
-@Sandy: We are thinking of replacing the `Decentralized' in the title by something like `balanced', to avoid false association with over-hyped blockchain technology.
-What are your thoughts?
-}
+In summary, we present a model that avoids the winner-take-all monopoly tendency and associated negative externalities of today's internet enabled business through a low cost tax based on a topological constraint.
 

### 2019-03-06 code/bar_plots.py

@@ -16,7 +16,7 @@ sb.set_style("darkgrid")
 
 # import data
 ########################################################################################################################
-file_path 		= "/home/nate/Desktop/"
+file_path 		= "./output/data/"
 file_name 		= file_path + "here.pickle"
 d_load 			= jl.load(file_name)
 
@@ -41,24 +41,23 @@ figsize 		= (width_scale*ncol,height_scale*nrow)
 
 # create the plot window
 ####################################################################################################################
-plt.clf()
-plt.rc('text', usetex=True)
 fig = plt.figure(figsize=figsize)
-fig.subplots_adjust(hspace=.12, wspace=0.4)
+fig.subplots_adjust(hspace=.2, wspace=0.2)
+plt.rc('text', usetex=True)
+
 
 # set all axes instances
 ####################################################################################################################
 circle_axis   	= plt.subplot2grid( (nrow,ncol), (0,0) )
-price_axis    	= plt.subplot2grid( (nrow,ncol), (1,0) )
-profit_axis		= plt.subplot2grid( (nrow,ncol), (2,0) )
-who_buys_axis	= plt.subplot2grid( (nrow,ncol), (3,0) )
+price_axis    	= plt.subplot2grid( (nrow,ncol), (0,1) )
+profit_axis		= plt.subplot2grid( (nrow,ncol), (1,0) )
+who_buys_axis	= plt.subplot2grid( (nrow,ncol), (1,1) )
 
 
 # create plot title 
 ########################################################################################################################
-fig = plt.figure(figsize=(14,5))
-
-title = 'Gamma=%s, Cost/unit=%s, endowment=%s, #Sellers=%s, #Buyers=%s'(gamma, cost, endowment, num_sellers, num_buyers)
+fn    = 'gamma=%s_cost=%s_endowment=%s_sellers=%s_buyers=%s'%(gamma, cost, endowment, num_sellers, num_buyers)
+title = fn.replace('_',', ')
 fig.suptitle(title, fontsize=14) 
 
 
@@ -83,7 +82,7 @@ for i, s in enumerate(seller_pos):
     xcoord = [ r * np.sin( 2*np.pi*s ) ]
     ycoord = [ r * np.cos( 2*np.pi*s ) ]
     
-    ax.scatter(xcoord, ycoord, marker='o', color=colors[i], s=400, zorder=3, label='buyer %s'%i)
[…]

### 2019-03-08 code/bar_plots.py
Has a significant bug right now. Not sure which update lead to this bug.

@@ -154,7 +154,7 @@ ax.set_visible(False)
 # write figure to the output 
 ########################################################################################################################
 out_folder = './output/plots/'
-if not os.path.exists(out_folder): os.makedirs(folder)
+if not os.path.exists(out_folder): os.makedirs(out_folder)
 plt.savefig(out_folder + fn + '.pdf', bbox_inches='tight')
 
 

### 2019-03-08 code/model.py

@@ -5,39 +5,46 @@ import seaborn as sns
 import gambit as gmb
 
 
-# CONSTANTS
-## Global Constants
-NUM_BUYERS = 100
-NUM_SELLERS = 2
-COST = 10
-GAMMA = 0
-ENDOWMENT = 20
-
-## Setup Constants
-a_seller_loc = [.2, .7, .9]
-a_buyer_loc = [.2, .2, .2, .9, .7, .7, .7, .9, .9, ]
-SELLER_PRICE = 1
-SELLER_QUANTITY = 5
-
-A_SELLER_PRICES = np.array([12, 12.5, 13.1, 14.0])
-A_SELLER_QUANTITIES = np.array([40.1, 50, 60, 70])
-FILE_OUT = '/home/nate/Desktop/here.pickle'
-
-
 #####################
 #####################
 ##### FUNCTIONS #####
 #####################
 #####################
 
+#######################
+### INNER FUNCTIONS ###
+#######################
+
+def arrayInd_to_array2Ind(a_ind, num_cols, num_rows):
+    '''
+    Sort of deflattens an array.
+    '''
+    a_ind_col = a_ind % num_cols
+    a_ind_row = a_ind // num_cols
+    return a_ind_col, a_ind_row
+
+def get_rand_strats(lower_bound, upper_bound, num_strats, frac=.05):
+    a_strat_base, step = np.linspace(lower_bound, upper_bound, num_strats, retstep=True)
+    scale = frac * step
+    a_rand = np.random.uniform(low=-scale, high=+scale, size=len(a_strat_base))
+    a_strat_rand = a_strat_base + a_rand
+    return(a_strat_rand)
+
+
 #####################
 ### CALCULATE TAX ###
 #####################
 
 def circle_dist(a, b):
+    '''
+    Finds distance if 1==0.
+    '''
     return .5-abs(abs(a-b)-.5)
 
-def get_m_tax_and_m_dist(a_buyer_loc, a_seller_loc, gamma=GAMMA):
+def get_m_tax_and_m_dist(a_buyer_loc, a_seller_loc, gamma):
+    '''
+    Calculates tax matrix and distance matrix.
+    '''
     # Matrix with absolute dist
     m_dist = [[circle_dist(buyer_loc, seller_loc)
         for buyer_loc in a_buyer_loc] for seller_loc in a_seller_loc]
[…]

### 2019-05-10 code/model.py
added names to abstract

@@ -503,7 +503,7 @@ def parameter_combination(i):
 # Create combinations
     num_sellers     = [2]
     num_buyers      = [12]
-    gamma           = [3.]#np.round(np.linspace(0.0, .3, 11), 3)
+    gamma           = np.round(np.linspace(0.0, .3, 11), 3)
     scalar_tax      = [.05]
     mean_cost       = [100.]
     cost_ratio      = np.round(np.linspace(1.0, 2.0, 11), 3)
@@ -518,7 +518,7 @@ def parameter_combination(i):
 
 
 if __name__ == "__main__":
-    #i = int(sys.argv[1]) - 1
+    i = int(sys.argv[1]) - 1
     #for i in range(121):
-    parameter_combination(1) 
+    parameter_combination(i) 
 

### 2019-06-21 code/bar_plot3x2.py
a lot of changes were made in plotting, and I improved the discretization.

@@ -1,0 +1,169 @@
+import os
+import sys
+import pickle
+import numpy  as np
+import pandas as pd
+import seaborn as sb
+from matplotlib import pyplot as plt
+from pprint     import pprint as pp
+from sklearn.externals import joblib as jl
+from itertools  import product,combinations
+from plot_util import customaxis
+
+
+################
+### FUNCTION ###
+################
+
+# Circle of buyers and sellers
+############################################################
+def ax_circle_from_data(a_seller_pos, a_buyer_pos, m_quantity_bought, a_color,
+        ax = None):
+# Setup
+    if ax is None:
+        _, ax = plt.subplots()
+    num_sellers = len(a_seller_pos)
+# plot a grey circle 
+    r       = 1
+    angles  = np.linspace(0, 2*np.pi, 500)
+    xs      = r * np.sin(angles)
+    ys      = r * np.cos(angles)
+    ax.plot(xs, ys, color='grey', linestyle='--', zorder=1)
+# plot sellers
+    for i, s in enumerate(a_seller_pos):
+        xcoord = [ r * np.sin( 2*np.pi*s ) ]
+        ycoord = [ r * np.cos( 2*np.pi*s ) ]
+        ax.scatter(xcoord, ycoord, marker='o', facecolor='none',
+                color=a_color[i], s=400, zorder=3, label='Firm %d'%(i+1))
+# plot buyers
+# for each buyer, find index of his seller
+    seller_ind = np.argmax(m_quantity_bought, axis=0)
+    for s in range(num_sellers):
+        a_pos_subset = a_buyer_pos[seller_ind == s]
+        a_xcoord = [r * np.sin(2 * np.pi * a_pos_subset)]
+        a_ycoord = [r * np.cos(2 * np.pi * a_pos_subset)]
+        ax.scatter(a_xcoord, a_ycoord, marker='x', color=a_color[s], s=80, zorder=2,
+                label='Buyer who bought from Firm %d'%(s+1)) 
+    ax.set_xlim(-1.2*r, 1.2*r)
+    ax.set_ylim(-1.2*r, 1.5*r)
+    ax.legend(loc='center', ncol=2, frameon=False, fontsize=8, labelspacing=2)
+    ax.axes.get_xaxis().set_visible(False)
+    ax.axes.get_yaxis().set_visible(False)
+    ax.axis('equal')
+
+# Barplots price, cost, profit, and quantity
[…]

### 2019-06-21 code/bar_plots.py

@@ -49,6 +49,8 @@ def plot_1timestep_from_data(a_cost, gamma, endowment, num_sellers, num_buyers,
                 fontsize    =  12,
                 ha          = 'left',
                 va          = 'top' )
+# Colors
+    a_color = sb.color_palette("deep", (3 + num_sellers))
 
 # Circle of buyers and sellers
 ############################################################
@@ -60,21 +62,20 @@ def plot_1timestep_from_data(a_cost, gamma, endowment, num_sellers, num_buyers,
     xs      = r * np.sin(angles)  									
     ys      = r * np.cos(angles) 
     ax.plot(xs, ys, color='grey', linestyle='--', zorder=1)
-    colors  = sb.color_palette("deep",len(a_seller_pos))
 
     for i, s in enumerate(a_seller_pos):  						
         xcoord = [ r * np.sin( 2*np.pi*s ) ]
         ycoord = [ r * np.cos( 2*np.pi*s ) ]
-        ax.scatter(xcoord, ycoord, marker='o', color=colors[i], s=400, zorder=3,
-                label='Firm %d'%(i+1))
+        ax.scatter(xcoord, ycoord, marker='o', facecolor='none',
+                color=a_color[i], s=400, zorder=3, label='Firm %d'%(i+1))
 
 # for each buyer, find index of his seller
     seller_ind    = np.argmax(m_quantity_bought, axis=0)
-    for s in range(len(a_seller_pos)):
+    for s in range(num_sellers):
         a_pos_subset = a_buyer_pos[seller_ind == s]
         a_xcoord = [r * np.sin(2 * np.pi * a_pos_subset)]
         a_ycoord = [r * np.cos(2 * np.pi * a_pos_subset)]
-        ax.scatter(a_xcoord, a_ycoord, marker='x', color=colors[s], s=80, zorder=2,
+        ax.scatter(a_xcoord, a_ycoord, marker='x', color=a_color[s], s=80, zorder=2,
                 label='Buyer who bought from Firm %d'%(s+1)) 
     ax.set_xlim(-1.2*r, 1.2*r)
     ax.set_ylim(-1.2*r, 1.5*r)
@@ -88,23 +89,23 @@ def plot_1timestep_from_data(a_cost, gamma, endowment, num_sellers, num_buyers,
     a_xvalues = np.arange(1, num_sellers + 1)
     w = 0.2
     fontsize = 13
-    colors = sb.color_palette("deep",3)
 
     ax = price_axis
-    color = colors[0]
[…]

### 2019-06-21 code/time_plots.py

@@ -5,13 +5,14 @@ import numpy  as np
 import pandas as pd
 import seaborn as sb
 from matplotlib import pyplot as plt
+from matplotlib import ticker as tk
 from pprint     import pprint as pp
 from sklearn.externals import joblib as jl
 from itertools  import product,combinations
 from plot_util import customaxis
 
 
-fn = "turn_gamma=0.6.pickle"
+fn = "turn_gamma=0.0.pickle"
 # Run main function
 folder1 = '/home/nate/Documents/abmcournotmodel/code/output/data/'
 folder2 = '/cluster/home/slera//abmcournotmodel/code/output/data/'
@@ -73,6 +74,7 @@ width_scale		= 12
 height_scale    	= 4
 figsize 		= (width_scale*ncol,height_scale*nrow)
 a_marker = ['s', 'x', '*', 'o', 'D']
+a_color = sb.color_palette("deep", num_sellers+4)
 fontsize = 14
 
 # create the plot window
@@ -101,37 +103,70 @@ for (ax, annote) in zip(a_ax, a_annote[0:len(a_ax)]):
             ha          = 'left',
             va          = 'top' )
 
+# Circle of buyers and sellers
+############################################################
+ax = ax_circle
+
+# plot a grey circle 
+r       = 1
+angles  = np.linspace(0, 2*np.pi, 500)
+xs      = r * np.sin(angles)  									
+ys      = r * np.cos(angles) 
+ax.plot(xs, ys, color='grey', linestyle='--', zorder=1)
+
+for i, s in enumerate(a_seller_pos):  						
+    xcoord = [ r * np.sin( 2*np.pi*s ) ]
+    ycoord = [ r * np.cos( 2*np.pi*s ) ]
+    ax.scatter(xcoord, ycoord, marker='o', facecolor='none', color=a_color[i],
+            s=400, zorder=3, label='Firm %d'%(i+1))
+
+# for each buyer, find index of his seller
+seller_ind    = np.argmax(a_m_quantity_bought[0], axis=0)
+for s in range(len(a_seller_pos)):
+    a_pos_subset = a_buyer_pos[seller_ind == s]
+    a_xcoord = [r * np.sin(2 * np.pi * a_pos_subset)]
+    a_ycoord = [r * np.cos(2 * np.pi * a_pos_subset)]
+    ax.scatter(a_xcoord, a_ycoord, marker='x', color=a_color[s], s=80, zorder=2,
[…]

### 2019-06-21 code/turn_model.py

@@ -18,7 +18,7 @@ def get_settings_from_dic_ret(dic_ret):
     num_buyers = dic_ret['num_buyers']
     ret = { 'num_sellers' : dic_ret['num_sellers'],
             'num_buyers' : num_buyers,
-            'a_strat_quantity' : np.linspace(0, 100*num_buyers, 21),
+            'a_strat_quantity' : np.arange(0, 100*num_buyers, 40),
             'a_seller_loc' : dic_ret['a_seller_loc'],
             'a_buyer_loc' : dic_ret['a_buyer_loc'],
             'a_cost' : dic_ret['a_cost'],

### 2019-06-22 writing/Paper/main.tex
Added tex Document and changes to plots

\documentclass[11pt]{article}
\usepackage[a4paper,margin=2.8cm]{geometry}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[dvipsnames,usenames]{color}
\usepackage[colorlinks=true,linkcolor=NavyBlue,citecolor=NavyBlue,urlcolor=NavyBlue]{hyperref} % for hyperlinks

% macros 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\R}{\mathds {R}}
\newcommand{\red}[1]{\textcolor{WildStrawberry}{#1}} % for color for remarks
\newcommand{\green}[1]{\textcolor{Green}{#1}} % for color for remarks

\title{Fair, Stable Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}

\author{Nate Dwyer, Sandro Lera, and Alex `Sandy' Pentland}

\begin{document}

\maketitle
\setcounter{section}{0}

\section*{Extended Abstract}

Until not too long ago, people used to live in more self-contained villages,
with local markets where people buy different products.  Take clothing as an
example. Most villages had one or several clothing merchants competing for
customers.  There is some healthy competition among merchants within a village,
as people can flexibly switch according to prices and preferences. But
customers would rarely buy clothing from a faraway village, as the transaction
cost associated with visiting that village would be high,  and could not offset
a marginally better price or quality.  On the other hand, people living far
away from any village are disadvantaged as they always incur such high costs.
Similarly, if there is a specialized product that can only be produced in some
villages, it was harder to find customers across village borders,  making it
more difficult for new products and technologies to succeed.

From the industrial to the technological revolution, more efficient
distribution channels have emerged, enabling people to buy almost any product
in online stores.  Independent of a customer's physical location, orders can be
delivered to their door within a day.  More specialized products are now sold
globally, and people living far away from hubs benefit from the availability of
a wide range of products.  While such efficiency is beneficial for the economy
as a whole, it comes at the cost of potential monopolies.  Consider a merchant
that manages to sell a product for a few cents cheaper than its competitors. 
Given modern distribution channels, and ignoring potential differences in
quality, every buyer is now incentivized to buy from that one firm at the
cheaper price. One potential outcome is that the competitors follow along,
increase their efficiency, and a new equilibrium is reached.  However, in a
suboptimal scenario, that one firm leverages the temporarily increased revenue
to further outpace and potentially undercut its competitors.  In the short
term, feedback mechanisms kick in, and an initially minor gap in competitive
advantage, mixed with efficient distribution channels, manifests itself in a
monopoly situation.

We conclude that geographical constraints can lead to unfair and inefficient
conditions for the customers, whereas removal of those constraints can lead to
exploitative monopolies.

In this work, we introduce an individualized tax between buyers and firms based
on distance. Through tuning of this tax and targeted redistribution of tax
money to regions of low economic activity, we show that this model is able to
[put conclusions here, everything else right now is speculation.]

\section{Introduction}
Consider competing firms in a number of small towns. Each town wants to
encourage their local firm to succeed, but at the same time does not want for
its citizens to face monopoly prices. Hence, the towns all levy small,
percentage sales taxes on out of town goods. These taxes increase as the origin
of the good gets more distant.

In addition, the firms that initially do well tend to get better and better
over time and build up an advantage over other firms. This is especially true
with network based firms, where quality of the product is dwarfed by quantity
of the network.

With enough market power, a profit seeking firm will try to raise barriers to
entry to prevent competition. This stops firms that have new innovations from
surviving long enough to succeed in a market. The distance based tax introduced
in this paper allows start ups to overcome entrenched monopolies' unfair
advantages.

In this paper, we propose a new distance based tax, which we call an
idiosyncratic tax, in order to solve these
problems, then show that it works by modelling an economy that implements the
tax. In section 2 we give an overview of this economy. In section 3 we
formalize the model, and discuss how the firms compete on capacity and price.
In section 4 we expand the model by allowing for multiple timesteps, and having
firms decrease their costs based on previous profits as a form of investment.

\section{Economy}
We simulate an economy of buyers and firms in some environment with a distance
(e.g. a country, a network economy). Then we apply the idiosyncratic tax that
increases with distance of purchase and see how firms respond.

\subsection{Geography}
The geography of our model is one-dimensional with periodic boundaries, i.e.
a topological circle, of length $L$. Due to the periodic boundary conditions,
we measure physical distances with the metric $\min(|x-y|, L-|x-y|)$ for any
two points (`agents') $x$,$y$ on the circle. Without loss of generality, we set
$L=1$. Our model does not rely on the implemented geography, and any other,
potentially more realistic topology could be considered.

The left insets (subgraphs (a), (c), (e), (g), and (i)) of Figure
\pageref{fig:fig3x2SingleTimestep} are examples of such a geography.

\subsection{Buyers}
We randomly place buyers on the circle. Each buyer tries to buy as much product
as possible, while constrained by a demand curve that limits how much they can
buy at given prices.

\subsection{Firms}
The firms, like the buyers, are also randomly placed on the circle, and compete
non-cooperatively to maximize their profit. Each firm makes two choices, first
capacity (i.e. how much they produce), then price, in order to earn the most
profit. A firm chooses capacity before price because it is difficult to quickly
change capacity due to supply chain restraints, while it is easier to change a
price tag.

\subsection{Idiosyncratic Tax}
[talk about new product means d=1 for everyone]
The idiosyncratic tax that is introduced by this paper is dependent on 
discrete distance metric [need another term] $D$ between a buyer and a firm,
where the closest firm to a buyer is at distance $D=1$, the next closest at
$D=2$, and the $n$th closest at $D=n$. Consider a firm and two buyers, one
buyer near the firm, the other distant. The idiosyncratic tax means that the
nearer buyer can buy more cheaply from that firm than can the more distant one.
This incentivizes buyers to purchase from more local firms.

Crucially, this discrete distance metric is calculated for every type of
product individually. This means that a dentist and a bakery do not increase
each other's distance from their buyers. In addition, this means that if a firm
produces a new product, such as a new drug, it is considered at distance 1 from
all buyers, until a competitor emerges.

\section{Model Definition}
When firms choose capacity and price, they make their choices in order to
maximize profit. First, the firms compete on a capacity, by simultaneously
declaring how much of the product they plan to produce; next, they compete on
price to determine the firms' non-tax prices. This process, consisting of these
two subgames is called a Kreps-Scheinkman game. The major difference we
introduce to the classical Kreps-Scheinkman game is the idiosyncratic tax,
which significantly alters the pricing subgame.

\subsection{Capacity Game}
The first choice is how much capacity $\hat q_i$ each firm $i$ wishes to
install. The firm's desire to increase capacity is limited by two factors.
First, firm $i$ incurs a unit price of $c_i$ for every unit of product they
install, regardless of whether or not the product is sold. Second, because the
buyers have a limited demand, eventually the buyers will stop buying.

The capacity subgame acts much like a Cournot game.\footnote{A Cournot game is
where firms compete only on quantity, and sell all of the quantity at the
market clearing price.} The difference, in our case, is that instead of being
assigned a market clearing price and selling everything they produce, in our
model the firms compete on price in a second subgame where they choose a price.
Only after that do the buyers determine how much of each firms capacity is
sold.

\subsection{Pricing Game}
Each firm $i$, having chosen a capacity $\hat q_i$, now choose a price, $p_i$.
Consider two vending machines selling the same soda right beside one another,
with one machine selling soda at a cheaper price than the other. In this
subgame, buyers will use the cheaper machine first, but if the buyers demand
more soda than the machine's capacity, buyers switch to the more expensive
machine when the cheaper one runs out of soda. Competition on price in such a
manner is called an Edgeworth game. Edgeworth games are very difficult to find
an equilibrium in, as depending on demand and capacity, a variety of optimal
strategies can be employed.

By choosing a lower price, a firm can undercut competitors, ensuring that
buyers choose to buy from them instead of other firms. In addition, because
of the negatively sloped demand curves of buyers, a lower price increases the
amount of product purchased in total. But the capacity limitation on total
quantity sold by a firm means that a single firm usually can't sell to the
entire market, and it could be more profitable to just sell a few at a much
higher price.

\subsection{Idiosyncratic Tax}
An additional complication to the pricing game is the idiosyncratic tax, as it
causes buyers to have preferences for certain firms. The tax is designed to
promote buyers purchasing locally, by having no tax if a buyer purchases from
the nearest firm, and then increasing the tax in discrete steps as firms get
more and more distant. Since each buyer-seller pair has a different tax, the
tax can cause two buyers to perceive separate prices at the same firm.

For any buyer $b$ and firm $i$, we define a product-distance $D = D(b,i)$ such
that the firm $i$ that is physically closest to $b$ has distance $D(b,i)=1$,
the next closest has distance $D=2$, and the $n$th closest has distance $D=n$. 
Thus, if buyer $b$ buys from firm $i$, the total price, including transaction
cost (tax), is given by $p(b,i) = p_i \cdot (e(D(b,i)^\gamma -1) + 1)$ where
$\gamma$ is the scaling coefficient of the tax.

Implementing the distance based tax gives the buyers individualized preferences
over the firms. For example, imagine two firms $i$ and $j$, and let $p_i <
p_j$. Without any tax, every buyer prefers buying from $i$ versus buying from
$j$. But with the tax, this could change. Say that buyer $b$ is very close to
firm $j$, and very far from firm $i$, so that $D(b,i)^\gamma \gg
D(b,j)^\gamma$. Then buyer $b$ would prefer to buy from $j$ despite $j$'s price
being higher because $p_i\cdot D(b,i)^\gamma > p_j\cdot D(b,j)^\gamma$.

This gives rise to two interesting limit cases, one where $\gamma = 0$, and the
other where $\gamma = \infty$.  When $\gamma = 0$, no firms are taxed anywhere,
so the game simplifies into a pure Kreps-Scheinkman game. In contrast, when
$\gamma = \infty$, it becomes impossible for buyers to purchase from non local
firms, and so the firms all impose monopolistic prices.

\subsection{Buyer Behavior and Rationing}
After the firms have finished determining capacity and price, and the distance
based tax has been incorporated into the prices, the buyers conduct purchases
as follows.

Let the set of buyers be called $B$. Each buyer $b\in B$ buys a quantity $q_b =
\sum_{i\in S} q_{b,i}$, where $q_{b,i}$ is the amount buyer $b$ buys from the
firm $i$. The buyer's all have identical demand curves $p_\text{max} + q_b =
a$, where $a$ is the endowment they are given exogenously, and $p_\text{max}$
is the maximum price they pay (including tax). Each buyer tries to maximize
$q_b$ while keeping $P + Q \le a$. In other words, they buy from the cheapest
available firm until they hit the demand curve.

If a buyer perceives multiple firms as offering identical prices, they buy from
all such firms in identical amounts until either the buyer hits their demand
curve, or a seller runs out of capacity.

\subsection{Profit Function}
Finally, firm $i$, having chosen quantity $\hat q_i$ and price $p_i$, and
having sold the product to buyers, will earn a profit:

\begin{equation}
    \Pi_i = p_i\sum_{b\in B} q_{b,i} - c_i\hat q_i.
\end{equation}

Note that while the firm can choose both their capacity $\hat q_i$ and their
price $p_i$, their cost per unit $c_i$ is set exogenously. Also, each $q_{b,i}$
is chosen by the buyer $b$ so that they buy as much as possible while staying
under their demand curve $P+Q\leq a$; this is where taxes affect the firm's
profit.

If the firm sells all of their capacity, the equation simplifies to:
\begin{equation}
    \Pi_i = (p_i- c_i)\hat q_i,
\end{equation}
which is the profit per unit multiplied by quantity sold, which is the same as
capacity.

\section{Model Solution and Examples}

\subsection{Numeric Solution}
Because the buyers have individualized preferences and the pricing game does
not necessarily have a pure Nash equilibrium, it is difficult to determine a
generalized, theoretical Nash equilibrium to the model laid out is section 3.
Instead, we determine the Nash equilibrium numerically.

First we discretize the possible strategies the firms can take, so we only have
to consider a finite number of strategies.

We would like to determine what the Nash quantity is, but we do not currently
know what the payoff for particular combinations of strategies until we
determine price. So we need to start by determining the Nash prices for every
combination of quantities, which we do by using the Python library Gambit,
which can solve game theoretic questions. We use the price choices to determine
the payoffs of capacity choices. Finally, we use Gambit again to determine what
the Nash capacity is.

We work backwards. First we find the payoffs for all of the possible prices
given capacity. Then we use the Python library Gambit to determine the Nash
equilibrium price. Now if the firms make the same capacity choices, then they
will make

Besides the basic geometry of the model, in order to determine how much profit
a firm makes we need to know how much capacity every firm produces and what
prices they sell at. But this presents a problem, as firms must pick capacity
before choosing price, yet they need to know the price to calculate the profit.

, so we have to first determine the equilibrium price for
each outcome of the

So we need to determine the prices firms will choose for
every contingency of the capacity game.
prices will be chosen when they choose capacity. This makes it difficult for
them to optimize which capacity to choose. The solution to this is to work
backwards. The firms first find the equilibrium price choice for every
combination of capacity choices that might occur. Then they calculate the
payoffs for every outcome of the capacity game. Finally, we determine the Nash

Figure \pageref{fig:fig3x2SingleTimestep}, Row 1, has two firms with the same
cost per unit, and $\gamma=0$. To solve this, we first discretized the
capacities and prices firms could choose. Then for each combination of
capacities chosen by Firms 1 and 2, we found the payoffs for every price they
could choose, creating a payoff matrix. Specifically, given that Firm 1 chose
capacity $\hat q_1$ and Firm 2 chose $\hat q_2$, if the firms choose prices
$p_1$ and $p_2$, they will earn profits $\Pi_1$ and $\Pi_2$. After calculating
this for every combination of prices, we then find the Nash equilibrium of the
pricing game.

we found both firms Nash prices. We then used the knowledge of what the optimal
price was to calculate the

To do this, 
Next, we need to simulate buyers that try to
purchase goods on the

Next, since there are two choices, we work backwards to determine the Nash
equilibrium of the game.

set of capacity strategies $\{\hat q_1, \hat q_2, \cdots, \hat q_{|S|}\}$, we
determine the nash prices $\{p_1, p_2, \cdots, p_{|S|}\}$.  Thus we assemble
the game of

The firm makes two choices, first capacity, then price. To solve, we first
figure out the nash pricing strategy given

because it is equivalent
to an Edgeworth game
[elaborate more on edgeworth game in section above, say that this makes it a
mixed nash equilibria] game

\begin{figure}
  \includegraphics[width=\linewidth]{5x2plot.png}
  \caption{Shown above are five instances of the model running for different
  $\gamma$ and costs. In the first two rows, $\gamma=0$, with the one
  difference being that in Row 1, both Firm 1 and Firm 2 have the same cost,
  and in Row 2, Firm 1 has a 1\% lower cost than Firm 2. In Row 1, the firms
  sell the same amount of product and make the same amount of profit. But in
  Row 2, Firm 1 sells 33\% more quantity and makes 53\% more profit.
  In the rest of the plots, $\gamma = .6$. In Row 3 we can see a mirror of Row
  1, where both firms, faced with the same costs, produce the same quantity,
  and make the same profit. But in row 4, where we give Firm 1
  the same advantage we game them in the row 2, they sell the same amount, and
  only make 12\% more profit than Firm 2. To increase their market share,
  Firm 1 needs to reduce their costs to 80\% of Firm 2, as shown in row 5.
  Our idiosyncratic tax thus acts as a speed bump, preventing companies with
  slight advantages from acquiring overwhelming market dominance, while still
  ensuring that minor innovations are profitable, and that large innovations do
  cause market dominance.}
  \label{fig:fig3x2SingleTimestep}
\end{figure}

\section{Dynamics}
We run this model once for every timestep, then update the costs for the firms
between the timesteps. Every timestep we determine which firm has made the most
profit. For that firm, we reduce its cost per unit by 5\% in order to simulate
the company investing its excess profits in itself to become more profitable in
the long term.

[put picture here when done running].

\section{Special Case when $\gamma = 0$}
If $\gamma = 0$, then the tax rate $(D^\gamma - 1) = 0$, which turns the game
into a Kreps-Scheinkman game with firms experiencing different cost functions. 
Theoretically, when per-unit costs are sufficiently close [define sufficiently
close, need to examine judo economics thing for this], the theoretical
Nash ends up being the same as a Cournot game with the same demand curve
and costs [citation].

In our model, we can see that the price predicted by the Cournot model and our
model coincide for most costs. But once the cost get too disparate, the Cournot
model splits from our model. [need explanation for this, possible judo econ
related.] In addition the most

\begin{figure}
  \includegraphics[width=\linewidth]{CournotVsModel.png}
  \caption{A comparison between prices predicted by two models. In blue is the
  one predicted by this paper's numeric approximation of the Kreps-Scheinkman
  model and in orange is the one predicted by the Cournot model.}
  \label{fig:figCournotVsModel}
\end{figure}

\section{Special Case when $\gamma = \infty$}
When $\gamma = \infty$, no buyer can afford any positive price from a non local
firm. Because of this, all firms will charge monopoly prices.

\subsection{What $\gamma$ will cause monopolistic behavior?}
A firm will price at monopoly prices if it knows that it cannot be profitably
undercut, and, conversely, cannot profitably undercut its opponent. So the
question then becomes, at what $\gamma$ do we know that this will hold for all
firms?

We start by finding the maximum price that cannot be profitably undercut.
Consider a firm $i$ trying to determine if it can undercut a competitor. The
firm $i$ will want to make a profit, and thus must sell at a price $p_i > c_i$.
In addition, the least tax a non local buyer would incur purchasing from them
is $2^\gamma$. Thus firm $i$ cannot make a profit if it offers a price $p_i
\leq c_i 2^\gamma$, and if firm $j$ offers a price of $p_j=c_i2^\gamma$, firm
$i$ cannot undercut firm $j$. To a price that no firm can undercut, we find the
minimum value of $c_i$, which we call $c_\text{min}$, for all firms $i\in S$,
leaving us with the conclusion that the maximum price that cannot be profitably
undercut is:

\begin{equation}
  p_\text{max} = c_\text{min}2^\gamma.
\end{equation}

Now we just need to substitute $p_\text{max}$ for the largest monopolistic
price to ensure no firm can be undercut. In general, the monopolistic price for
a firm $i$ with a demand curve of $p_i = a-bq_i$ is $\frac{a+c_i}{2}$ [ref].
Thus the highest monopoly price is $\frac{a+c_\text{max}}{2}$, and we get the
following:
\begin{align}
  c_\text{min}2^\gamma &= p_\text{max}\\
  c_\text{min}2^\gamma &= \frac{a+c_\text{max}}{2}\\
  2^\gamma &= \frac{a+c_\text{max}}{2c_\text{min}}\\
  \gamma &= \frac{\ln(\frac{a+c_\text{max}}{2c_\text{min}})}{\ln(2)}\\
  \gamma &= \frac{\ln(a+c_\text{max}) - \ln(2) -\ln(c_\text{min})}{\ln(2)}
\end{align}

Thus when $\gamma$ satisfies (8), the firms all charge monopoly prices, and act
in the same way as they do when $gamma = \infty$.

\section{Nash Equilibrium of the game}
The analytic solution is unfortunately very difficult to compute for a number
of reasons. First, we must determine the prices firms will choose given their
choice of capacity. This is difficult to do as Edgeworth game does not
necessarily have a pure Nash solution, and it is beyond my abilities to
calculate what the mixed Nash is on a continuous game.

Fortunately, what our program does is calculate a numeric approximation of what
the Nash equilibrium is for our model. It does this by implementing our model
on a discrete set of strategies for both a firm's capacity and price, and then
solving these games using the program Gambit.

Interestingly, most of the time, the approximate Nash as calculated by the
program usually predicts that [blank here].

\section{Unequal tax model}
Consider a Cournot economy of $n$ firms where the $i$th firm is uniquely
subject to an ad valorem, or percentage, tax at rate $t$, with all other firms
assigned no tax. If there was no tax for firm $i$,  we could describe its
profit function using the equation $\Pi_i(q_i) = q_i(p-c_i)$, where $q_i$ is
the firm's quantity, $p$ the market clearing price, and $c_i$ the product's
unit cost.  The market clearing price is $p = a - bQ$, where $a$ is the
endowment, $b$ the slope of the demand curve, and $Q$ is the total quantity
produced by all firms. By $Q_{-i} = Q - q_i$ we denote the sum of all sold
quantities except $q$.

Since the firm is subject to a tax, it will have to offer a lower pre-tax
price to match the market clearing price; hence the pre-tax price is
$p_\text{pre-tax} = p/(1+t)$. Factoring this into the profit function gives:

\begin{subequations}
\begin{align}
    \Pi_i &= q_i \left(p_\text{pre-tax} - c\right)\\
          &= q_i \left(\frac{p}{1+t} - c\right)\\
          &= q_i \left(\frac{a - bQ}{1+t} - c\right)\\
          &= q_i \left(\frac{a - b(q_i + Q_{-i})}{1+t} - c\right).
\end{align}
\end{subequations}

Now, to find the best response function (BRF), we take the derivative and
set it to 0:
\begin{subequations}
\begin{align}
    \Pi_i &= q_i \left(\frac{a - b(q_i + Q_{-i})}{1+t} - c\right)\\
    \frac{\mathrm{d}\Pi_i}{\mathrm{d}q_i} &= \frac{a - b(2q_i + Q_{-i})}{1+t} -
    c\\
    0 &= \frac{a - b(2q_i + Q_{-i})}{1+t} - c\\
    0 &= a - b(2q_i + Q_{-i}) - c\left(1+t\right)\\
    2bq_i &= a - bQ_{-i} - c\left(1+t\right)\\
    q_i &= \frac{1}{2b}\left(a-bQ_{-i} - c\left(1+t\right)\right). \label{eq:q_i_unequal_tax_model}
\end{align}
\end{subequations}

We use the BRF's of all the firms to see if they intersect at a common point,
which would be the Nash equilibrium.  In \eqref{eq:q_i_unequal_tax_model},
we can consider the tax as part of the production cost when finding the Nash
quantities, then solve as we normally would a heterogeneous cost Cournot
oligopoly. In other words, taxation is an effective cost.

In a hetereogeneous Cournot economy, the Nash-equilibrium quantity $q_i$
of firm $i$ has cost $c_i$ is given by
\begin{equation}
q_i = \frac{1}{b (n+1)}(a + n(\bar c - c_i) - c_i)\text{,}
\end{equation}
where $n$ is the number of firms, $\bar c$ is the average cost, and $a$ and $b$
come from the demand curve $p = a-bQ$, where $Q$ is total quantity. \red{At
least in a footnote, provide a reference where you got that formula from.}

Interestingly, the BRF we get from a percentage tax is similar to the BRF we
would get if we had a specific tax, also known as a per unit tax.  A specific
or per unit tax is one that adds a flat extra cost per unit created,
effectively increasing the cost by a fixed amount. Say the specific tax was
$t_\text{specific}$. Then the profit function would look like:
\begin{equation}
\Pi = q (p-c-t_\text{specific})
\end{equation}
and the BRF would be:
\begin{equation}
q = \frac{1}{2}(a-q_\text{other} - c - t_\text{specific})
\end{equation}
which means that we could again just consider $c - t_\text{specific}$ as the
cost that the firm faces, and also solve as normal.

\section{Open Questions}

\begin{itemize}

    \item With this model, we want to demonstrate that initially small
        differences in quality do not lead to proportional feedback mechanisms
        that lead to an unequal output distribution So it might be questionable
        if the current Cournot model is the model of our interests, because it
        assumes all buyers set the same price.

\end{itemize}

\subsection{Summary}
The firms play two gamesjcompete first in a Cournot economy where they chose a
capacity, then in a Bertrand-Edgeworth economy where they choose the price.  A
sequential game without the taxes and variable costs is called the
Kreps-Scheinkman model.

\end{document}

### 2019-06-22 code/bar_plots.py

@@ -185,9 +185,10 @@ def plot_1timestep_from_dic(d_load, show=False):
 ##############
 
 fn = "turn_gamma=0.0.pickle"
+fn = "S=2_B=12_gamma=0.6_scalar_tax=0.05_mean_cost=100.0_cost_ratio=1.01_endow=120.0_randomize=False.pkl"
 folder1 = '/home/nate/Documents/abmcournotmodel/code/output/data/'
 folder2 = '/cluster/home/slera//abmcournotmodel/code/output/data/'
 folder  = folder1 if os.path.exists(folder1) else folder2
 d_load  = jl.load(folder + fn)
 
-plot_1timestep_from_a_dic(d_load, 0, show=True)
+plot_1timestep_from_dic(d_load, show=True)

### 2019-06-22 code/model.py

@@ -17,7 +17,8 @@ from pdb import set_trace
 
 
 #######################
-### SETUP FUNCTIONS ### #######################
+### SETUP FUNCTIONS ###
+#######################
 
 
 def get_a_cost_from_ratio(mean, ratio, num_sellers, is_arithmetic=True):
@@ -483,7 +484,7 @@ def main(num_sellers=2, num_buyers=6, gamma=0, scalar_tax=1., mean_cost=100, cos
     q_max, _ = theoretical_Cournot(num_sellers, num_buyers, max(a_cost),
             endowment)
     # Not the best estimate
-    a_strat_quantity = np.linspace(0, num_buyers*100, num_strats)
+    a_strat_quantity = np.arange(0, num_buyers*50, 40)
     d_write = make_dic_of_pure_nash(num_sellers, num_buyers, a_strat_quantity,
             a_seller_loc, a_buyer_loc, a_cost, gamma, scalar_tax, endowment,
             mean_cost, cost_ratio)
@@ -503,12 +504,12 @@ def parameter_combination(i):
     """
 # Create combinations
     num_sellers     = [2]
-    num_buyers      = [13]
-    gamma           = [0]#np.round(np.linspace(0.0, .3, 11), 3)
+    num_buyers      = [12]
+    gamma           = [0.0]#np.round(np.linspace(0.0, .3, 11), 3)
     scalar_tax      = [.05]
-    mean_cost       = [60.]
-    cost_ratio      = [5]#np.round(np.linspace(1.0, 2.0, 11), 3)
-    endowment       = [200.]
+    mean_cost       = [100]
+    cost_ratio      = [1.0]#np.round(np.linspace(1.0, 2.0, 11), 3)
+    endowment       = [120.]
     randomize       = [False]
     combs           = product(num_sellers, num_buyers, gamma, scalar_tax, mean_cost, cost_ratio, endowment, randomize)
     comb            = list(combs)[i]

### 2019-06-22 code/multiple_bar_plots.py

@@ -10,6 +10,7 @@ from sklearn.externals import joblib as jl
 from itertools  import product,combinations
 from plot_util import customaxis
 
+fontsize = 15
 
 ################
 ### FUNCTION ###
@@ -18,10 +19,11 @@ from plot_util import customaxis
 # Circle of buyers and sellers
 ############################################################
 def ax_circle_from_data(a_seller_pos, a_buyer_pos, m_quantity_bought, a_color,
-        ax = None):
+        gamma, ax = None):
 # Setup
     if ax is None:
         _, ax = plt.subplots()
+    ax.set_title(label='Gamma = {}'.format(gamma))
     num_sellers = len(a_seller_pos)
 # plot a grey circle 
     r       = 1
@@ -42,11 +44,12 @@ def ax_circle_from_data(a_seller_pos, a_buyer_pos, m_quantity_bought, a_color,
         a_pos_subset = a_buyer_pos[seller_ind == s]
         a_xcoord = [r * np.sin(2 * np.pi * a_pos_subset)]
         a_ycoord = [r * np.cos(2 * np.pi * a_pos_subset)]
-        ax.scatter(a_xcoord, a_ycoord, marker='x', color=a_color[s], s=80, zorder=2,
-                label='Buyer who bought from Firm %d'%(s+1)) 
+        ax.scatter(a_xcoord, a_ycoord, marker='x', color=a_color[s], s=80,
+                zorder=2, label='Buyer who bought from Firm %d'%(s+1)) 
     ax.set_xlim(-1.2*r, 1.2*r)
     ax.set_ylim(-1.2*r, 1.5*r)
-    ax.legend(loc='center', ncol=2, frameon=False, fontsize=8, labelspacing=2)
+    ax.legend(loc='center', ncol=2, frameon=False, fontsize=2*fontsize/3,
+            labelspacing=2)
     ax.axes.get_xaxis().set_visible(False)
     ax.axes.get_yaxis().set_visible(False)
     ax.axis('equal')
@@ -62,7 +65,6 @@ def ax_bars_from_data(a_price, a_cost, a_quantity_sold, a_profit, a_color,
     a_color_alt = sb.color_palette("deep", num_sellers)
     a_xvalues = np.arange(1, num_sellers + 1)
     w = 0.2
-    fontsize = 13
 # plot the price for each buyer 
     color = a_color[0]
[…]

### 2019-06-22 code/time_plots.py

@@ -12,7 +12,7 @@ from itertools  import product,combinations
 from plot_util import customaxis
 
 
-fn = "turn_gamma=0.0.pickle"
+fn = "turn_gamma=0.6.pickle"
 # Run main function
 folder1 = '/home/nate/Documents/abmcournotmodel/code/output/data/'
 folder2 = '/cluster/home/slera//abmcournotmodel/code/output/data/'
@@ -31,19 +31,19 @@ bug_check = True
 
 # Data from d_load
 ##########################################################
-gamma      		= d_load['gamma'][0]
-endowment  		= d_load['endowment'][0]
-num_sellers     	= d_load['num_sellers'][0]
-num_buyers 		= d_load['num_buyers'][0]
-a_buyer_pos             = d_load['a_buyer_loc'][0]
-a_seller_pos            = d_load['a_seller_loc'][0]
-m_tax                   = d_load['m_tax'][0]
-a_m_quantity_bought     = d_load['m_quantity_bought']
-pd_quantity             = pd.DataFrame(d_load['a_quantity_nash'])
-pd_quantity_sold        = pd.DataFrame(d_load['a_quantity_sold'])
-pd_price         	= pd.DataFrame(d_load['a_price_nash'])
-pd_cost       		= pd.DataFrame(d_load['a_cost'])
-pd_profit 		= pd.DataFrame(d_load['a_profit'])
+gamma               = d_load['gamma'][0]
+endowment           = d_load['endowment'][0]
+num_sellers         = d_load['num_sellers'][0]
+num_buyers          = d_load['num_buyers'][0]
+a_buyer_pos         = d_load['a_buyer_loc'][0]
+a_seller_pos        = d_load['a_seller_loc'][0]
+m_tax               = d_load['m_tax'][0]
+a_m_quantity_bought = d_load['m_quantity_bought']
+pd_quantity         = pd.DataFrame(d_load['a_quantity_nash'])
+pd_quantity_sold    = pd.DataFrame(d_load['a_quantity_sold'])
+pd_price            = pd.DataFrame(d_load['a_price_nash'])
+pd_cost             = pd.DataFrame(d_load['a_cost'])
+pd_profit           = pd.DataFrame(d_load['a_profit'])
 print(pd_cost)
 
 # Data from calculations
@@ -110,11 +110,11 @@ ax = ax_circle
 # plot a grey circle 
 r       = 1
[…]

### 2019-06-22 writing/Paper/main.tex
took care of figure caption

@@
 \usepackage[colorlinks=true,linkcolor=NavyBlue,citecolor=NavyBlue,urlcolor=NavyBlue]{hyperref} % for hyperlinks 
+\usepackage{floatpag} % remove page number for figure that covers entire page
 
@@
 
-\begin{figure}
+\begin{figure}[[p!htb] % p stands for 'entire page', '!htb' is to insert as close to code as possible
+	\floatpagestyle{empty} % remove page number
+	\centering
+	\vspace{-2cm} % shift upwards to get more space for caption
   \includegraphics[width=\linewidth]{5x2plot.png}
-  \caption{Shown above are five instances of the model running for different
+  \caption{\small{Shown above are five instances of the model running for different
   $\gamma$ and costs. In the first two rows, $\gamma=0$, with the one
@@
   ensuring that minor innovations are profitable, and that large innovations do
-  cause market dominance.}
+  cause market dominance.}}
   \label{fig:fig3x2SingleTimestep}

### 2019-06-23 writing/Paper/main.tex
latest version of paper

@@
 \usepackage[colorlinks=true,linkcolor=NavyBlue,citecolor=NavyBlue,urlcolor=NavyBlue]{hyperref} % for hyperlinks 
-\usepackage{floatpag} % remove page number for figure that covers entire page
+\usepackage{floatpag}
 
@@
 formalize the model, and discuss how the firms compete on capacity and price.
-In section 4 we expand the model by allowing for multiple timesteps, and having
-firms decrease their costs based on previous profits as a form of investment.
+In section 4, we discuss results of running the model. In section 5 we expand
+the model by allowing for multiple timesteps, and having firms decrease their
+costs based on previous profits as a form of investment.
+%[change as we add sections]
 
@@
 We simulate an economy of buyers and firms in some environment with a distance
-(e.g. a country, a network economy). Then we apply the idiosyncratic tax that
-increases with distance of purchase and see how firms respond.
+metric (e.g. a country, a network economy), then see how firms respond when we
+apply the idiosyncratic tax.
 
 \subsection{Geography}
-The geography of our model is one-dimensional with periodic boundaries, i.e.
-a topological circle, of length $L$. Due to the periodic boundary conditions,
+The geography of our model is one-dimensional with periodic boundaries (i.e.
+a topological circle) of length $L$. Due to the periodic boundary conditions,
 we measure physical distances with the metric $\min(|x-y|, L-|x-y|)$ for any
@@
 
-The left insets (subgraphs (a), (c), (e), (g), and (i)) of Figure
-\pageref{fig:fig3x2SingleTimestep} are examples of such a geography.
+The left insets of Figure \pageref{fig:fig3x2SingleTimestep} are examples of
+such a geography.
 
@@
 We randomly place buyers on the circle. Each buyer tries to buy as much product
-as possible, while constrained by a demand curve that limits how much they can
-buy at given prices.
+as possible, but is constrained by a negatively sloped demand curve which
+lowers the amount of product they can buy the more expensive the product gets.
 
@@
 The firms, like the buyers, are also randomly placed on the circle, and compete
-non-cooperatively to maximize their profit. Each firm makes two choices, first
-capacity (i.e. how much they produce), then price, in order to earn the most
-profit. A firm chooses capacity before price because it is difficult to quickly
-change capacity due to supply chain restraints, while it is easier to change a
-price tag.
+non-cooperatively to maximize their profit. In this competition, also known as
+a game, each firm makes two choices, first capacity (i.e. how much they
+produce), then price. A firm chooses capacity before price because it is
+difficult to quickly change capacity due to supply chain restraints, while it
+is easier to change a price tag.
 
 \subsection{Idiosyncratic Tax}
-[talk about new product means d=1 for everyone]
-The idiosyncratic tax that is introduced by this paper is dependent on 
-discrete distance metric [need another term] $D$ between a buyer and a firm,
-where the closest firm to a buyer is at distance $D=1$, the next closest at
-$D=2$, and the $n$th closest at $D=n$. Consider a firm and two buyers, one
-buyer near the firm, the other distant. The idiosyncratic tax means that the
-nearer buyer can buy more cheaply from that firm than can the more distant one.
-This incentivizes buyers to purchase from more local firms.
+The idiosyncratic tax that is introduced by this paper is dependent on a
+distance measuere $D$, or ordinal distance, that gives a discrete distance
+between every pair of buyers and firms. $D$ is defined such that the closest
+firm to a buyer is at ordinal distance $D=1$, the next closest at $D=2$, and
+the $n$th closest at $D=n$. Consider a firm and two buyers, one buyer near the
+firm, the other distant. The idiosyncratic tax means that the nearer buyer can
+buy more cheaply from that firm than can the more distant one. This
+incentivizes buyers to purchase from more local firms.
 
-Crucially, this discrete distance metric is calculated for every type of
-product individually. This means that a dentist and a bakery do not increase
-each other's distance from their buyers. In addition, this means that if a firm
-produces a new product, such as a new drug, it is considered at distance 1 from
-all buyers, until a competitor emerges.
+Crucially, this ordinal distance is calculated for every individual type of
+product. This means that a dentist and a bakery do not increase each other's
+distance from their buyers. In addition, if a firm produces a new product, such
+as a drug for a previously incurable disease, it is considered at distance 1
+from all buyers, at least until a competitor emerges.
 
@@
 When firms choose capacity and price, they make their choices in order to
-maximize profit. First, the firms compete on a capacity, by simultaneously
+maximize profit. First, the firms compete on capacity, by simultaneously
 declaring how much of the product they plan to produce; next, they compete on
 price to determine the firms' non-tax prices. This process, consisting of these
-two subgames is called a Kreps-Scheinkman game. The major difference we
+two subgames, is called a Kreps-Scheinkman game. The major difference we
 introduce to the classical Kreps-Scheinkman game is the idiosyncratic tax,
@@
 where firms compete only on quantity, and sell all of the quantity at the
-market clearing price.} The difference, in our case, is that instead of being
-assigned a market clearing price and selling everything they produce, in our
-model the firms compete on price in a second subgame where they choose a price.
-Only after that do the buyers determine how much of each firms capacity is
-sold.
+market clearing price.} The difference is that instead of being assigned a
+market clearing price and selling everything they produce, in our model the
+firms compete on price in a second subgame where they choose a price. Only
+after that do the buyers determine how much of each firms capacity is sold.
 
 \subsection{Pricing Game}
-Each firm $i$, having chosen a capacity $\hat q_i$, now choose a price, $p_i$.
-Consider two vending machines selling the same soda right beside one another,
+Each firm $i$, having chosen a capacity $\hat q_i$, now chooses a price, $p_i$.
+Consider two vending machines right beside one another selling the same soda,
 with one machine selling soda at a cheaper price than the other. In this
 subgame, buyers will use the cheaper machine first, but if the buyers demand
-more soda than the machine's capacity, buyers switch to the more expensive
-machine when the cheaper one runs out of soda. Competition on price in such a
-manner is called an Edgeworth game. Edgeworth games are very difficult to find
-an equilibrium in, as depending on demand and capacity, a variety of optimal
-strategies can be employed.
+more soda than that machine's capacity, buyers will switch to the more
+expensive machine when the cheaper one runs out of soda. Competition on price
+in such a manner is called an Edgeworth game. Edgeworth games are very
+difficult to find an equilibrium in, as depending on demand and capacity, a
+variety of strategies can be employed.
 
 By choosing a lower price, a firm can undercut competitors, ensuring that
-buyers choose to buy from them instead of other firms. In addition, because
-of the negatively sloped demand curves of buyers, a lower price increases the
-amount of product purchased in total. But the capacity limitation on total
+buyers choose to buy from them instead of other firms. Since the amount a buyer
+purchases increases as the product gets less expensive, a lower price increases
+the amount of product purchased in total. But the capacity limitation on total
 quantity sold by a firm means that a single firm usually can't sell to the
-entire market, and it could be more profitable to just sell a few at a much
-higher price.
+entire market, and it could be more profitable to just sell a low quantity at a much higher price.
 
 \subsection{Idiosyncratic Tax}
-An additional complication to the pricing game is the idiosyncratic tax, as it
-causes buyers to have preferences for certain firms. The tax is designed to
-promote buyers purchasing locally, by having no tax if a buyer purchases from
-the nearest firm, and then increasing the tax in discrete steps as firms get
-more and more distant. Since each buyer-seller pair has a different tax, the
-tax can cause two buyers to perceive separate prices at the same firm.
+The idiosyncratic tax is designed to promote buyers purchasing locally by
+imposing no tax if a buyer purchases from the nearest firm, and then increasing
+the tax in discrete steps as firms get more and more ordinally distant. Since
+each buyer-seller pair can have a different tax, the tax can cause two buyers
+to perceive separate prices at the same firm.
 
-For any buyer $b$ and firm $i$, we define a product-distance $D = D(b,i)$ such
-that the firm $i$ that is physically closest to $b$ has distance $D(b,i)=1$,
-the next closest has distance $D=2$, and the $n$th closest has distance $D=n$. 
-Thus, if buyer $b$ buys from firm $i$, the total price, including transaction
-cost (tax), is given by $p(b,i) = p_i \cdot (e(D(b,i)^\gamma -1) + 1)$ where
-$\gamma$ is the scaling coefficient of the tax.
+For any buyer $b$ and firm $i$, we define the ordinal distance $D = D(b,i)$
+such that the firm $i$ that is physically closest to $b$ has distance
+$D(b,i)=1$, the next closest has distance $D=2$, and the $n$th closest has
+distance $D=n$.  Thus, if buyer $b$ buys from firm $i$, the total price,
+including tax, is given by $p(b,i) = p_i + p_i \cdot r(D(b,i)^\gamma -1)$
+where $\gamma$ is the coefficient governing how quickly the tax increases, and
+$r$ is a simple scaling coefficient.
 
-Implementing the distance based tax gives the buyers individualized preferences
+Implementing this tax gives the buyers individualized preferences
 over the firms. For example, imagine two firms $i$ and $j$, and let $p_i <
@@
 $j$. But with the tax, this could change. Say that buyer $b$ is very close to
-firm $j$, and very far from firm $i$, so that $D(b,i)^\gamma \gg
-D(b,j)^\gamma$. Then buyer $b$ would prefer to buy from $j$ despite $j$'s price
-being higher because $p_i\cdot D(b,i)^\gamma > p_j\cdot D(b,j)^\gamma$.
+firm $j$, and very far from firm $i$, which would mean that $D(b,i) \gg
+D(b,j)$. Then buyer $b$ would prefer to buy from $j$ despite $j$'s price
+being higher because $p_i + p_i\cdot r(D(b,i)^\gamma - 1) > p_j + p_j\cdot
+r(D(b,j)^\gamma -1)$.
 
@@
 \subsection{Buyer Behavior and Rationing}
-After the firms have finished determining capacity and price, and the distance
-based tax has been incorporated into the prices, the buyers conduct purchases
-as follows.
+After the firms have finished determining capacity and price, and the
+idiosyncratic tax has been incorporated into the prices, the buyers conduct
+purchases as follows.
 
@@
 
-If the firm sells all of their capacity, the equation simplifies to:
+If the firm sells all of their capacity, then $q_i = \hat q_i$, and the profit
+equation simplifies to:
 \begin{equation}
@@
 \end{equation}
-which is the profit per unit multiplied by quantity sold, which is the same as
-capacity.
+which is the net profit per unit multiplied by quantity sold.
 
-\section{Model Solution and Examples}
+\subsection{Numerical Approximation}
+Because the buyers have individualized preferences and the pricing game does
+not necessarily have a `best' strategy, it is difficult to determine a
+generalized, theoretical solution to the model laid out above. Instead, we
+numerically determine the Nash equilibrium.\footnote{A Nash equilibrium
+for a game is a set of choices, one for each player, such that upon seeing the
+other firm's choices, could increase their payoff by changing strategies. In
+our model, the players are firms, the payoff is profit, and the choices are
+either capacity or price, depending on the subgame.}
 
-\subsection{Numeric Solution}
-Because the buyers have individualized preferences and the pricing game does
-not necessarily have a pure Nash equilibrium, it is difficult to determine a
-generalized, theoretical Nash equilibrium to the model laid out is section 3.
-Instead, we determine the Nash equilibrium numerically.
+To find the capacities and prices that the firms will choose, we begin by
+discretizing the capacity and pricing choices so we only have a finite number
+of possible combinations. Then, for every outcome of the capacity game, we find
+the Nash equilibrium of the pricing game using the Python library Gambit. Then,
+using the equilibrium prices, we calculate the profits for every outcome of the
+capacity game. We finally use this information to find the Nash equilibrium of
+the capacity game, again using Gambit.
 
-First we discretize the possible strategies the firms can take, so we only have
-to consider a finite number of strategies.
+\section{Examples}
+Figure \ref{fig:fig3x2SingleTimestep} contains the output of five instances
+of finding the numerical solution for different $\gamma$ and costs. In the
+first two rows $\gamma=0$, with the one difference being that in Row 1, both
+Firm 1 and Firm 2 have the same cost, and in Row 2, Firm 1 has a 1\% lower cost
+than Firm 2. In Row 1, the firms sell the same amount of product and make the
+same amount of profit. But in Row 2, Firm 1 sells 33\% more quantity and makes
+53\% more profit. As a side note, since when $\gamma = 0$ there is no tax on
+distance, we can see on the left insets of these rows that buyers do not
+necessarily buy from the closest firm.
 
-We would like to determine what the Nash quantity is, but we do not currently
-know what the payoff for particular combinations of strategies until we
-determine price. So we need to start by determining the Nash prices for every
-combination of quantities, which we do by using the Python library Gambit,
-which can solve game theoretic questions. We use the price choices to determine
-the payoffs of capacity choices. Finally, we use Gambit again to determine what
-the Nash capacity is.
+In the Rows 3, 4, and 5, we let $\gamma = .5$ instead. In Row 3 we can see a
+mirror of Row 1, where both firms, faced with the same costs, produce the same
+quantity, and make the same profit. But in row 4, where we give Firm 1 the same
+advantage we game them in the row 2, they sell the same amount, and only make
+12\% more profit than Firm 2. To increase their market share, Firm 1 needs to
+reduce their costs to 80\% of Firm 2, as shown in row 5.
 
-We work backwards. First we find the payoffs for all of the possible prices
-given capacity. Then we use the Python library Gambit to determine the Nash
-equilibrium price. Now if the firms make the same capacity choices, then they
-will make
-
-Besides the basic geometry of the model, in order to determine how much profit
-a firm makes we need to know how much capacity every firm produces and what
-prices they sell at. But this presents a problem, as firms must pick capacity
-before choosing price, yet they need to know the price to calculate the profit.
-
-, so we have to first determine the equilibrium price for
-each outcome of the
-
-So we need to determine the prices firms will choose for
-every contingency of the capacity game.
-prices will be chosen when they choose capacity. This makes it difficult for
-them to optimize which capacity to choose. The solution to this is to work
-backwards. The firms first find the equilibrium price choice for every
-combination of capacity choices that might occur. Then they calculate the
-payoffs for every outcome of the capacity game. Finally, we determine the Nash
-
-Figure \pageref{fig:fig3x2SingleTimestep}, Row 1, has two firms with the same
-cost per unit, and $\gamma=0$. To solve this, we first discretized the
-capacities and prices firms could choose. Then for each combination of
-capacities chosen by Firms 1 and 2, we found the payoffs for every price they
-could choose, creating a payoff matrix. Specifically, given that Firm 1 chose
-capacity $\hat q_1$ and Firm 2 chose $\hat q_2$, if the firms choose prices
-$p_1$ and $p_2$, they will earn profits $\Pi_1$ and $\Pi_2$. After calculating
-this for every combination of prices, we then find the Nash equilibrium of the
-pricing game.
-
-we found both firms Nash prices. We then used the knowledge of what the optimal
-price was to calculate the
-
-To do this, 
-Next, we need to simulate buyers that try to
-purchase goods on the
-
-Next, since there are two choices, we work backwards to determine the Nash
-equilibrium of the game.
-
-set of capacity strategies $\{\hat q_1, \hat q_2, \cdots, \hat q_{|S|}\}$, we
-determine the nash prices $\{p_1, p_2, \cdots, p_{|S|}\}$.  Thus we assemble
-the game of
-
-The firm makes two choices, first capacity, then price. To solve, we first
-figure out the nash pricing strategy given
-
-because it is equivalent
-to an Edgeworth game
-[elaborate more on edgeworth game in section above, say that this makes it a
-mixed nash equilibria] game
+The idiosyncratic tax thus acts as a dampener, preventing companies with
+slight advantages from acquiring overwhelming market dominance, while still
+ensuring that minor innovations are profitable. But, if one firm is
+significantly better, as in Row 5, then that firm will still dominate the
+market.
 
@@
   \includegraphics[width=\linewidth]{5x2plot.png}
-  \caption{\small{Shown above are five instances of the model running for different
-  $\gamma$ and costs. In the first two rows, $\gamma=0$, with the one
-  difference being that in Row 1, both Firm 1 and Firm 2 have the same cost,
-  and in Row 2, Firm 1 has a 1\% lower cost than Firm 2. In Row 1, the firms
-  sell the same amount of product and make the same amount of profit. But in
-  Row 2, Firm 1 sells 33\% more quantity and makes 53\% more profit.
-  In the rest of the plots, $\gamma = .6$. In Row 3 we can see a mirror of Row
-  1, where both firms, faced with the same costs, produce the same quantity,
-  and make the same profit. But in row 4, where we give Firm 1
-  the same advantage we game them in the row 2, they sell the same amount, and
-  only make 12\% more profit than Firm 2. To increase their market share,
-  Firm 1 needs to reduce their costs to 80\% of Firm 2, as shown in row 5.
-  Our idiosyncratic tax thus acts as a speed bump, preventing companies with
-  slight advantages from acquiring overwhelming market dominance, while still
-  ensuring that minor innovations are profitable, and that large innovations do
-  cause market dominance.}}
+  \caption{\small{Above are the model's results for a variety of
+  conditions. The Rows 1 and 2 have $\gamma=0$, while Rows 3, 4, and 5 have
+  $\gamma = .5$. In Rows 1 and 3, the firms have an equal cost per unit, sell
+  equal quantity, and make equal profit. In Row 2, where $\gamma=0$, a 1\%
+  difference in cost means Firm 1 has a 10\% greater market share, and a 53\%
+  larger profit.
+  In Row 4, where $\gamma=.5$, Firm 1's 1\% difference in cost now results in
+  an equal market share, but they still profit 12\% more. To get a larger
+  market share, as in Row 5, Firm 1 must have a 20\% lower cost per unit. This
+  means that $\gamma$ acts as a dampener on monopolization by increasing the
+  amount of innovation needed to gain market power while still encouraging
+  innovation. %[Check numbers after new gamma]
+  }}
   \label{fig:fig3x2SingleTimestep}
@@
 
-[put picture here when done running].
-
-\section{Special Case when $\gamma = 0$}
-If $\gamma = 0$, then the tax rate $(D^\gamma - 1) = 0$, which turns the game
-into a Kreps-Scheinkman game with firms experiencing different cost functions. 
-Theoretically, when per-unit costs are sufficiently close [define sufficiently
-close, need to examine judo economics thing for this], the theoretical
-Nash ends up being the same as a Cournot game with the same demand curve
-and costs [citation].
-
-In our model, we can see that the price predicted by the Cournot model and our
-model coincide for most costs. But once the cost get too disparate, the Cournot
-model splits from our model. [need explanation for this, possible judo econ
-related.] In addition the most
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{CournotVsModel.png}
-  \caption{A comparison between prices predicted by two models. In blue is the
-  one predicted by this paper's numeric approximation of the Kreps-Scheinkman
-  model and in orange is the one predicted by the Cournot model.}
-  \label{fig:figCournotVsModel}
-\end{figure}
-
-\section{Special Case when $\gamma = \infty$}
-When $\gamma = \infty$, no buyer can afford any positive price from a non local
-firm. Because of this, all firms will charge monopoly prices.
-
-\subsection{What $\gamma$ will cause monopolistic behavior?}
-A firm will price at monopoly prices if it knows that it cannot be profitably
-undercut, and, conversely, cannot profitably undercut its opponent. So the
-question then becomes, at what $\gamma$ do we know that this will hold for all
-firms?
-
-We start by finding the maximum price that cannot be profitably undercut.
-Consider a firm $i$ trying to determine if it can undercut a competitor. The
-firm $i$ will want to make a profit, and thus must sell at a price $p_i > c_i$.
-In addition, the least tax a non local buyer would incur purchasing from them
-is $2^\gamma$. Thus firm $i$ cannot make a profit if it offers a price $p_i
-\leq c_i 2^\gamma$, and if firm $j$ offers a price of $p_j=c_i2^\gamma$, firm
-$i$ cannot undercut firm $j$. To a price that no firm can undercut, we find the
-minimum value of $c_i$, which we call $c_\text{min}$, for all firms $i\in S$,
-leaving us with the conclusion that the maximum price that cannot be profitably
-undercut is:
-
-\begin{equation}
-  p_\text{max} = c_\text{min}2^\gamma.
-\end{equation}
-
-Now we just need to substitute $p_\text{max}$ for the largest monopolistic
-price to ensure no firm can be undercut. In general, the monopolistic price for
-a firm $i$ with a demand curve of $p_i = a-bq_i$ is $\frac{a+c_i}{2}$ [ref].
-Thus the highest monopoly price is $\frac{a+c_\text{max}}{2}$, and we get the
-following:
-\begin{align}
-  c_\text{min}2^\gamma &= p_\text{max}\\
-  c_\text{min}2^\gamma &= \frac{a+c_\text{max}}{2}\\
-  2^\gamma &= \frac{a+c_\text{max}}{2c_\text{min}}\\
-  \gamma &= \frac{\ln(\frac{a+c_\text{max}}{2c_\text{min}})}{\ln(2)}\\
-  \gamma &= \frac{\ln(a+c_\text{max}) - \ln(2) -\ln(c_\text{min})}{\ln(2)}
-\end{align}
-
-Thus when $\gamma$ satisfies (8), the firms all charge monopoly prices, and act
-in the same way as they do when $gamma = \infty$.
-
-\section{Nash Equilibrium of the game}
-The analytic solution is unfortunately very difficult to compute for a number
-of reasons. First, we must determine the prices firms will choose given their
-choice of capacity. This is difficult to do as Edgeworth game does not
-necessarily have a pure Nash solution, and it is beyond my abilities to
-calculate what the mixed Nash is on a continuous game.
-
-Fortunately, what our program does is calculate a numeric approximation of what
-the Nash equilibrium is for our model. It does this by implementing our model
-on a discrete set of strategies for both a firm's capacity and price, and then
-solving these games using the program Gambit.
-
-Interestingly, most of the time, the approximate Nash as calculated by the
-program usually predicts that [blank here].
-
-\section{Unequal tax model}
-Consider a Cournot economy of $n$ firms where the $i$th firm is uniquely
-subject to an ad valorem, or percentage, tax at rate $t$, with all other firms
-assigned no tax. If there was no tax for firm $i$,  we could describe its
-profit function using the equation $\Pi_i(q_i) = q_i(p-c_i)$, where $q_i$ is
-the firm's quantity, $p$ the market clearing price, and $c_i$ the product's
-unit cost.  The market clearing price is $p = a - bQ$, where $a$ is the
-endowment, $b$ the slope of the demand curve, and $Q$ is the total quantity
-produced by all firms. By $Q_{-i} = Q - q_i$ we denote the sum of all sold
-quantities except $q$.
-
-Since the firm is subject to a tax, it will have to offer a lower pre-tax
-price to match the market clearing price; hence the pre-tax price is
-$p_\text{pre-tax} = p/(1+t)$. Factoring this into the profit function gives:
-
-\begin{subequations}
-\begin{align}
-    \Pi_i &= q_i \left(p_\text{pre-tax} - c\right)\\
-          &= q_i \left(\frac{p}{1+t} - c\right)\\
-          &= q_i \left(\frac{a - bQ}{1+t} - c\right)\\
-          &= q_i \left(\frac{a - b(q_i + Q_{-i})}{1+t} - c\right).
-\end{align}
-\end{subequations}
-
-Now, to find the best response function (BRF), we take the derivative and
-set it to 0:
-\begin{subequations}
-\begin{align}
-    \Pi_i &= q_i \left(\frac{a - b(q_i + Q_{-i})}{1+t} - c\right)\\
-    \frac{\mathrm{d}\Pi_i}{\mathrm{d}q_i} &= \frac{a - b(2q_i + Q_{-i})}{1+t} -
-    c\\
-    0 &= \frac{a - b(2q_i + Q_{-i})}{1+t} - c\\
-    0 &= a - b(2q_i + Q_{-i}) - c\left(1+t\right)\\
-    2bq_i &= a - bQ_{-i} - c\left(1+t\right)\\
-    q_i &= \frac{1}{2b}\left(a-bQ_{-i} - c\left(1+t\right)\right). \label{eq:q_i_unequal_tax_model}
-\end{align}
-\end{subequations}
-
-We use the BRF's of all the firms to see if they intersect at a common point,
-which would be the Nash equilibrium.  In \eqref{eq:q_i_unequal_tax_model},
-we can consider the tax as part of the production cost when finding the Nash
-quantities, then solve as we normally would a heterogeneous cost Cournot
-oligopoly. In other words, taxation is an effective cost.
-
-In a hetereogeneous Cournot economy, the Nash-equilibrium quantity $q_i$
-of firm $i$ has cost $c_i$ is given by
-\begin{equation}
-q_i = \frac{1}{b (n+1)}(a + n(\bar c - c_i) - c_i)\text{,}
-\end{equation}
-where $n$ is the number of firms, $\bar c$ is the average cost, and $a$ and $b$
-come from the demand curve $p = a-bQ$, where $Q$ is total quantity. \red{At
-least in a footnote, provide a reference where you got that formula from.}
-
-Interestingly, the BRF we get from a percentage tax is similar to the BRF we
-would get if we had a specific tax, also known as a per unit tax.  A specific
-or per unit tax is one that adds a flat extra cost per unit created,
-effectively increasing the cost by a fixed amount. Say the specific tax was
-$t_\text{specific}$. Then the profit function would look like:
-\begin{equation}
-\Pi = q (p-c-t_\text{specific})
-\end{equation}
-and the BRF would be:
-\begin{equation}
-q = \frac{1}{2}(a-q_\text{other} - c - t_\text{specific})
-\end{equation}
-which means that we could again just consider $c - t_\text{specific}$ as the
-cost that the firm faces, and also solve as normal.
-
-\section{Open Questions}
-
-\begin{itemize}
-
-    \item With this model, we want to demonstrate that initially small
-        differences in quality do not lead to proportional feedback mechanisms
-        that lead to an unequal output distribution So it might be questionable
-        if the current Cournot model is the model of our interests, because it
-        assumes all buyers set the same price.
-
-\end{itemize}
-
-\subsection{Summary}
-The firms play two gamesjcompete first in a Cournot economy where they chose a
-capacity, then in a Bertrand-Edgeworth economy where they choose the price.  A
-sequential game without the taxes and variable costs is called the
-Kreps-Scheinkman model.
-
 \end{document}

### 2019-06-24 code/model.py
updated turn_model.py

@@ -468,6 +468,7 @@ def main(num_sellers=2, num_buyers=6, gamma=0, scalar_tax=1., mean_cost=100, cos
     #assert num_buyers%num_sellers == 0, "number of sellers does not divide number of buyers"
 # setup buyer and seller locations
     if randomize:
+        np.random.seed(17)
         a_seller_loc = np.random.uniform(low=0, high=1, size=num_sellers)
         a_buyer_loc  = np.random.uniform(low=0, high=1, size=num_buyers)
     else:
@@ -478,6 +479,7 @@ def main(num_sellers=2, num_buyers=6, gamma=0, scalar_tax=1., mean_cost=100, cos
     dist = 40 # deviation from cournot that we search for
 # Determine a_cost
     a_cost = get_a_cost_from_ratio(mean_cost, cost_ratio, num_sellers)
+    #a_cost = np.array([99., 100])
 # need to fix theoretical Cournot.
     q_min, _ = theoretical_Cournot(1, num_buyers/float(num_sellers),
             min(a_cost), endowment)
@@ -505,12 +507,12 @@ def parameter_combination(i):
 # Create combinations
     num_sellers     = [2]
     num_buyers      = [12]
-    gamma           = [0.0]#np.round(np.linspace(0.0, .3, 11), 3)
+    gamma           = [1.0]#np.round(np.linspace(0.0, .3, 11), 3)
     scalar_tax      = [.05]
     mean_cost       = [100]
     cost_ratio      = [1.0]#np.round(np.linspace(1.0, 2.0, 11), 3)
     endowment       = [120.]
-    randomize       = [False]
+    randomize       = [True]
     combs           = product(num_sellers, num_buyers, gamma, scalar_tax, mean_cost, cost_ratio, endowment, randomize)
     comb            = list(combs)[i]
     num_sellers, num_buyers, gamma, scalar_tax, mean_cost, cost_ratio, endowment, randomize = comb

### 2019-06-24 code/multiple_bar_plots.py

@@ -19,11 +19,11 @@ fontsize = 15
 # Circle of buyers and sellers
 ############################################################
 def ax_circle_from_data(a_seller_pos, a_buyer_pos, m_quantity_bought, a_color,
-        gamma, ax = None):
+        gamma, a_cost, ax = None):
 # Setup
     if ax is None:
         _, ax = plt.subplots()
-    ax.set_title(label='Gamma = {}'.format(gamma))
+    ax.set_title(label='gamma = {}, Firm 1\'s cost is {}% lower.'.format(gamma, a_cost[1]-a_cost[0]))
     num_sellers = len(a_seller_pos)
 # plot a grey circle 
     r       = 1
@@ -72,7 +72,6 @@ def ax_bars_from_data(a_price, a_cost, a_quantity_sold, a_profit, a_color,
     ax.set_xlabel('')
     ax.set_xticks(a_xvalues)
     ax.set_xticklabels(['Firm %d'%i for i in a_xvalues])
-    ax.set_xlim([0,5])
     [t.set_color(i) for (i,t) in zip(a_color_alt[0:num_sellers], ax.xaxis.get_ticklabels())]
     customaxis(ax = ax, position = 'left', color = color, label = 'Prices',
             scale = 'linear', size = fontsize, full_nrs = False, location = 0.0)
@@ -95,6 +94,7 @@ def ax_bars_from_data(a_price, a_cost, a_quantity_sold, a_profit, a_color,
     axt2.autoscale(tight=True)
     customaxis(ax = axt2, position = 'right', color = color, label = 'Profit',
             scale = 'linear', size= fontsize, full_nrs = False, location = 1.12)
+    ax.set_xlim([min(a_xvalues)-1.5*w, max(a_xvalues)+1.5*w])
 
 def draw_ax2_from_a_dic(d_load, i, ax_circle, ax_bar):
 # get data
@@ -140,7 +140,7 @@ def draw_ax2_from_a_dic(d_load, i, ax_circle, ax_bar):
 # Plots
     a_color = sb.color_palette("deep", (3 + num_sellers))
     ax_circle_from_data(a_seller_pos, a_buyer_pos, m_quantity_bought,
-            a_color=a_color, gamma=gamma, ax=ax_circle)
[…]

### 2019-06-24 code/turn_model.py

@@ -6,9 +6,9 @@ import pandas as pd
 import numpy as np
 
 def new_a_cost(a_cost, a_profit):
-    ind = np.argmax(a_profit)
-    ret = list(a_cost)
-    ret[ind] = .95*a_cost[ind]
+    a_profit_ratio = a_profit/np.sum(a_profit)
+    a_cost_decrease_ratio = 1 - .05*a_profit_ratio
+    ret = a_cost_decrease*a_cost
     return ret
 
 def get_settings_from_dic_ret(dic_ret):
@@ -85,17 +85,17 @@ def process(d_settings, num_loops):
 
 if __name__ == "__main__":
     i = int(sys.argv[1]) - 1
-    gamma = i*3./100.
+    gamma = i/10.
     num_sellers = 2
     num_buyers = 13
     d_settings = { 'num_sellers' : num_sellers,
             'num_buyers' : num_buyers,
-            'a_strat_quantity' : np.linspace(0, 800, 21),
+            'a_strat_quantity' : np.linspace(0, num_buyers*100, 21),
             'a_seller_loc' : np.linspace(start=0, stop=1, num=num_sellers, endpoint=False),
             'a_buyer_loc'  : np.linspace(start=0, stop=.999, num=num_buyers,  endpoint=False),
             'a_cost' : [100, 100],
             'gamma' : gamma,
-            'scalar_tax' : 1,
+            'scalar_tax' : .05,
             'endowment' : 200,
             'mean_cost' : 100,
             'cost_ratio' : 1} 

### 2019-06-24 writing/Paper/main.tex
Writing imporovements

@@
 \usepackage{floatpag}
+\usepackage{hyperref}
+\usepackage[backend=biber,style=authoryear]{biblatex}
+\bibliography{refs}
 
@@
 
+\green{If we don't add the start up stuff, delete this.}
 With enough market power, a profit seeking firm will try to raise barriers to
@@
 
-In this paper, we propose a new distance based tax, which we call an
-idiosyncratic tax, in order to solve these
-problems, then show that it works by modelling an economy that implements the
-tax. In section 2 we give an overview of this economy. In section 3 we
-formalize the model, and discuss how the firms compete on capacity and price.
-In section 4, we discuss results of running the model. In section 5 we expand
-the model by allowing for multiple timesteps, and having firms decrease their
-costs based on previous profits as a form of investment.
+In this paper, we propose an idiosyncratic tax based on distance in order to
+solve these problems, then show that it works by modelling an economy that
+implements the tax. In section 2 we give an overview of this economy. In
+section 3 we formalize the model, and discuss how the firms compete on capacity
+and price. In section 4, we discuss results of running the model. In section 5
+we expand the model by allowing for multiple timesteps, and having firms
+decrease their costs based on previous profits as a form of investment.
 %[change as we add sections]
@@
 We simulate an economy of buyers and firms in some environment with a distance
-metric (e.g. a country, a network economy), then see how firms respond when we
-apply the idiosyncratic tax.
+metric (e.g. a country, a network economy), then observe how firms respond when
+we apply the idiosyncratic tax.
 
@@
 
-The left insets of Figure \pageref{fig:fig3x2SingleTimestep} are examples of
+The left insets of Figure \ref{fig:fig3x2SingleTimestep} are examples of
 such a geography.
@@
 The idiosyncratic tax that is introduced by this paper is dependent on a
-distance measuere $D$, or ordinal distance, that gives a discrete distance
-between every pair of buyers and firms. $D$ is defined such that the closest
-firm to a buyer is at ordinal distance $D=1$, the next closest at $D=2$, and
-the $n$th closest at $D=n$. Consider a firm and two buyers, one buyer near the
-firm, the other distant. The idiosyncratic tax means that the nearer buyer can
-buy more cheaply from that firm than can the more distant one. This
-incentivizes buyers to purchase from more local firms.
+distance measure $D$, or ordinal distance, that gives a discrete distance
+between every pair of buyers and firms. We define the ordinal distance $D$ be
+defined such that the closest firm to a buyer is at ordinal distance $D=1$, the
+next closest at $D=2$, and the $n$th closest at $D=n$. Consider a subset of a
+larger economy consisting of a firm and two buyers, one buyer near the firm,
+the other distant. \green{right here I am trying to express show that because
+of the tax, two buyer's can perceive different prices at the same firm.} The
+idiosyncratic tax means that the nearer buyer can buy more cheaply from that
+firm than can the more distant one. This incentivizes buyers to purchase from
+more local firms.
 
@@
 price to determine the firms' non-tax prices. This process, consisting of these
-two subgames, is called a Kreps-Scheinkman game. The major difference we
-introduce to the classical Kreps-Scheinkman game is the idiosyncratic tax,
-which significantly alters the pricing subgame.
+two subgames, is called a Kreps-Scheinkman game \cite{kreps1983quantity}.
+The major difference we introduce to the classical Kreps-Scheinkman game is the
+idiosyncratic tax, which significantly alters the pricing subgame.
 
@@
 market clearing price and selling everything they produce, in our model the
-firms compete on price in a second subgame where they choose a price. Only
-after that do the buyers determine how much of each firms capacity is sold.
+firms compete on price in a second subgame where they choose a price. This
+subgame is necessary because the idiosyncratic tax can provide incentive for
+firms to charge different prices. For example, a firm with low costs trying to
+sell to non-local buyers would need to price undercut those customer's local
+firm.
 
@@
 expensive machine when the cheaper one runs out of soda. Competition on price
-in such a manner is called an Edgeworth game. Edgeworth games are very
-difficult to find an equilibrium in, as depending on demand and capacity, a
-variety of strategies can be employed.
+in such a manner is called an Edgeworth game.
 
@@
 quantity sold by a firm means that a single firm usually can't sell to the
-entire market, and it could be more profitable to just sell a low quantity at a much higher price.
+entire market, and it could be more profitable to just sell a low quantity at a
+much higher price.
 
@@
 is the maximum price they pay (including tax). Each buyer tries to maximize
-$q_b$ while keeping $P + Q \le a$. In other words, they buy from the cheapest
-available firm until they hit the demand curve.
+$q_b$ while keeping $p_\text{max} + q_b \le a$. In other words, they buy from
+the cheapest available firm until they hit the demand curve and stop buying, or
+the firm runs out of capacity and the buyer begins buying from the next
+cheapest, repeating the process.
 
@@
 Finally, firm $i$, having chosen quantity $\hat q_i$ and price $p_i$, and
-having sold the product to buyers, will earn a profit:
+having sold some or all of their capacity to buyers, will earn a profit:
 
@@
 
-Note that while the firm can choose both their capacity $\hat q_i$ and their
-price $p_i$, their cost per unit $c_i$ is set exogenously. Also, each $q_{b,i}$
-is chosen by the buyer $b$ so that they buy as much as possible while staying
-under their demand curve $P+Q\leq a$; this is where taxes affect the firm's
-profit.
+Also, each $q_{b,i}$ is chosen by the buyer $b$ so that they buy as much as
+possible while staying under their demand curve $P+Q\leq a$; this is where
+taxes affect the firm's profit.
 
@@
 Because the buyers have individualized preferences and the pricing game does
-not necessarily have a `best' strategy, it is difficult to determine a
+not necessarily have a `best' price choice, it is difficult to determine a
 generalized, theoretical solution to the model laid out above. Instead, we
@@
 of possible combinations. Then, for every outcome of the capacity game, we find
-the Nash equilibrium of the pricing game using the Python library Gambit. Then,
-using the equilibrium prices, we calculate the profits for every outcome of the
-capacity game. We finally use this information to find the Nash equilibrium of
-the capacity game, again using Gambit.
+the Nash equilibrium of the pricing game using the Python library Gambit
+\cite{gambitPython}. Then, using the equilibrium prices, we calculate the
+profits for every outcome of the capacity game. We finally use this information
+to find the Nash equilibrium of the capacity game.
 
 \section{Examples}
-Figure \ref{fig:fig3x2SingleTimestep} contains the output of five instances
-of finding the numerical solution for different $\gamma$ and costs. In the
-first two rows $\gamma=0$, with the one difference being that in Row 1, both
-Firm 1 and Firm 2 have the same cost, and in Row 2, Firm 1 has a 1\% lower cost
-than Firm 2. In Row 1, the firms sell the same amount of product and make the
-same amount of profit. But in Row 2, Firm 1 sells 33\% more quantity and makes
-53\% more profit. As a side note, since when $\gamma = 0$ there is no tax on
-distance, we can see on the left insets of these rows that buyers do not
-necessarily buy from the closest firm.
+In Figure \ref{fig:fig3x2SingleTimestep} we can see the idiosyncratic tax
+dampen Firm 1's attempts to become a monopoly power. In Rows 1 and 2, there is
+no tax as $\gamma = 0$. While Firm 1 and 2 have an equal cost per unit, no firm
+can become a monopoly. But if we reduce Firm 1's cost per unit by $1\%$, they
+sell 14\% more than their competition, and earn 33\% more profit, which is out
+of proportion to Firm 1's actual accomplishment, and can lead to
+anti-competitive behavior by Firm 1.
 
-In the Rows 3, 4, and 5, we let $\gamma = .5$ instead. In Row 3 we can see a
+In contrast, in Rows 3, 4, and 5, we let $\gamma = 1$. In Row 3 we can see a
 mirror of Row 1, where both firms, faced with the same costs, produce the same
@@
 advantage we game them in the row 2, they sell the same amount, and only make
-12\% more profit than Firm 2. To increase their market share, Firm 1 needs to
-reduce their costs to 80\% of Firm 2, as shown in row 5.
+12\% more profit than Firm 2, which implies that our tax protects Firm 2 from
+small decrease in Firm 1's cost per unit. To increase their market share, Firm
+1 needs to reduce their costs to 80\% of Firm 2, as shown in row 5.
 
-The idiosyncratic tax thus acts as a dampener, preventing companies with
-slight advantages from acquiring overwhelming market dominance, while still
-ensuring that minor innovations are profitable. But, if one firm is
-significantly better, as in Row 5, then that firm will still dominate the
-market.
+The idiosyncratic tax thus dampens monopolistic tendencies of firms with slight
+competitive advantages, while still ensuring that minor innovations are
+profitable. But, if one firm is significantly better, as in Row 5, then that
+firm will still dominate the market.
 
@@
   \caption{\small{Above are the model's results for a variety of
-  conditions. The Rows 1 and 2 have $\gamma=0$, while Rows 3, 4, and 5 have
-  $\gamma = .5$. In Rows 1 and 3, the firms have an equal cost per unit, sell
+  conditions. The Rows 1 and 2 have $\gamma=0.0$, while Rows 3, 4, and 5 have
+  $\gamma = 0.5$. In Rows 1 and 3, the firms have an equal cost per unit, sell
   equal quantity, and make equal profit. In Row 2, where $\gamma=0$, a 1\%
-  difference in cost means Firm 1 has a 10\% greater market share, and a 53\%
+  difference in cost implies Firm 1 sells 14\% more quantity, and earns a 33\%
   larger profit.
   In Row 4, where $\gamma=.5$, Firm 1's 1\% difference in cost now results in
-  an equal market share, but they still profit 12\% more. To get a larger
+  an equal market share, but they still profit 11\% more. To get a larger
   market share, as in Row 5, Firm 1 must have a 20\% lower cost per unit. This
-  means that $\gamma$ acts as a dampener on monopolization by increasing the
-  amount of innovation needed to gain market power while still encouraging
-  innovation. %[Check numbers after new gamma]
+  implies that $\gamma$ dampens a firm's ability to gain market power from
+  small innovations, without significantly discouraging innovation. 
+  %[Check numbers after new gamma]
   }}
@@
 We run this model once for every timestep, then update the costs for the firms
-between the timesteps. Every timestep we determine which firm has made the most
-profit. For that firm, we reduce its cost per unit by 5\% in order to simulate
-the company investing its excess profits in itself to become more profitable in
-the long term.
+between the timesteps. Every timestep we split a 5\% decrease in costs between
+the firms according to the fraction of total profit the Firm makes. For
+example, if Firm 1 earned a profit of 80, and Firm 2 earned a profit of 20,
+then Firm 1's per unit cost would decrease by 4\%, and Firm 1's by 1\%.
 
+\newpage
+\printbibliography
 \end{document}

### 2019-06-24 code/model.py
Can now run time_plots.py from terminal

@@ -478,8 +478,12 @@ def main(num_sellers=2, num_buyers=6, gamma=0, scalar_tax=1., mean_cost=100, cos
     num_strats = 21 # number of quantity-strategies
     dist = 40 # deviation from cournot that we search for
 # Determine a_cost
+    if cost_ratio == 1.25:
+        mean_cost = 90
     a_cost = get_a_cost_from_ratio(mean_cost, cost_ratio, num_sellers)
-    #a_cost = np.array([99., 100])
+    if cost_ratio == 1.01:
+        a_cost = np.array([90., 100])
+    a_cost = np.array([90., 100])
 # need to fix theoretical Cournot.
     q_min, _ = theoretical_Cournot(1, num_buyers/float(num_sellers),
             min(a_cost), endowment)
@@ -507,10 +511,10 @@ def parameter_combination(i):
 # Create combinations
     num_sellers     = [2]
     num_buyers      = [12]
-    gamma           = [1.0]#np.round(np.linspace(0.0, .3, 11), 3)
-    scalar_tax      = [.05]
-    mean_cost       = [100]
-    cost_ratio      = [1.0]#np.round(np.linspace(1.0, 2.0, 11), 3)
+    gamma           = [0, .5]#np.round(np.linspace(0.0, .3, 11), 3)
+    scalar_tax      = [1.0]
+    mean_cost       = [95]
+    cost_ratio      = [1.0, 1.01, 1.1]#np.round(np.linspace(1.0, 2.0, 11), 3)
     endowment       = [120.]
     randomize       = [True]
     combs           = product(num_sellers, num_buyers, gamma, scalar_tax, mean_cost, cost_ratio, endowment, randomize)
@@ -522,7 +526,7 @@ def parameter_combination(i):
 
 
 if __name__ == "__main__":
-    i = 0
+    i = 7
     #i = int(sys.argv[1]) - 1
     #for i in range(121):
     parameter_combination(i) 

### 2019-06-24 code/turn_model.py
some updates for many functions, but not everything

@@ -8,7 +8,8 @@ import numpy as np
 def new_a_cost(a_cost, a_profit):
     a_profit_ratio = a_profit/np.sum(a_profit)
     a_cost_decrease_ratio = 1 - .05*a_profit_ratio
-    ret = a_cost_decrease*a_cost
+    ret = a_cost_decrease_ratio*a_cost
+    print(ret)
     return ret
 
 def get_settings_from_dic_ret(dic_ret):
@@ -18,7 +19,7 @@ def get_settings_from_dic_ret(dic_ret):
     num_buyers = dic_ret['num_buyers']
     ret = { 'num_sellers' : dic_ret['num_sellers'],
             'num_buyers' : num_buyers,
-            'a_strat_quantity' : np.arange(0, 100*num_buyers, 40),
+            'a_strat_quantity' : np.arange(0, 100*num_buyers, 21),
             'a_seller_loc' : dic_ret['a_seller_loc'],
             'a_buyer_loc' : dic_ret['a_buyer_loc'],
             'a_cost' : dic_ret['a_cost'],
@@ -80,23 +81,28 @@ def process(d_settings, num_loops):
     folder1 = '/home/nate/Documents/abmcournotmodel/code/output/data/'
     folder2 = '/cluster/home/slera//abmcournotmodel/code/output/data/'
     folder  = folder1 if os.path.exists(folder1) else folder2
-    fn = folder + 'turn_gamma=' + str(round(d_settings['gamma'],3)) + '.pickle'
+    fn = folder + 'alt_adv_fast_turn_gamma={}_scalar_tax={}_endow={}.pickle'.format(round(d_settings['gamma'],3), d_settings['scalar_tax'], d_settings['endowment'])
     jl.dump(d_turns, fn)
 
 if __name__ == "__main__":
     i = int(sys.argv[1]) - 1
     gamma = i/10.
+    scalar_tax = 1.0
+    endowment = 200
     num_sellers = 2
-    num_buyers = 13
+    num_buyers = 12
+    np.random.seed(17)
+    a_seller_loc = np.random.uniform(low=0, high=1, size=num_sellers)
+    a_seller_loc = np.random.uniform(low=0, high=1, size=num_sellers)
     d_settings = { 'num_sellers' : num_sellers,
             'num_buyers' : num_buyers,
             'a_strat_quantity' : np.linspace(0, num_buyers*100, 21),
             'a_seller_loc' : np.linspace(start=0, stop=1, num=num_sellers, endpoint=False),
[…]

### 2019-06-24 writing/Paper/main.tex
significantly revised the report.

@@
-\documentclass[11pt]{article}
-\usepackage[a4paper,margin=2.8cm]{geometry}
+% document settings
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[final,3p,times,authoryear,12pt]{elsarticle}
+
 \usepackage{amsfonts}
@@
 \usepackage{hyperref}
-\usepackage[backend=biber,style=authoryear]{biblatex}
-\bibliography{refs}
+\usepackage[shortlabels]{enumitem}
 
@@
 
+% remove abstracf (for now)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\makeatletter
+\long\def\MaketitleBox{%
+  \resetTitleCounters
+  \def\baselinestretch{1}%
+  \begin{center}%
+   \def\baselinestretch{1}%
+    \Large\@title\par\vskip18pt
+    \normalsize\elsauthors\par\vskip10pt
+    \footnotesize\itshape\elsaddress\par\vskip36pt
+%    \hrule\vskip12pt
+%    \ifvoid\absbox\else\unvbox\absbox\par\vskip10pt\fi
+%    \ifvoid\keybox\else\unvbox\keybox\par\vskip10pt\fi
+%    \hrule\vskip12pt
+    \end{center}%
+  }
+\makeatother
+
+% title, authors and affiliations
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\journal{~}
+\begin{document}
+\begin{frontmatter}
+
 \title{Fair, Stable Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}
 
-\author{Nate Dwyer, Sandro Lera, and Alex `Sandy' Pentland}
+\author[add1]{Nate Dwyer}
+\ead{nate9799@gmail.com}
 
-\begin{document}
+\author[add1]{Sandro Claudio Lera}
+\ead{slera@mit.edu}
 
-\maketitle
-\setcounter{section}{0}
+\author[add1]{Alex `Sandy' Pentland}
+\ead{sandy@media.mit.edu}
 
-\section*{Extended Abstract}
+\address[add1]{\scriptsize The Media Lab, Massachusetts Institute of Technology, 77 Massachusetts Avenue, 02139 Cambridge, Massachusetts, USA}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{abstract} 
+A new, firm-buyer specific idiosyncratic tax is introduced.
+\end{abstract}
+
+\end{frontmatter}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 term, feedback mechanisms kick in, and an initially minor gap in competitive
-advantage, mixed with efficient distribution channels, manifests itself in a
-monopoly situation.
+advantage, mixed with efficient distribution channels, manifests itself in a suboptimal monopoly.
 
-We conclude that geographical constraints can lead to unfair and inefficient
-conditions for the customers, whereas removal of those constraints can lead to
-exploitative monopolies.
+In this article, we show that such monopolies can be prevented by introducing an idiosyncratic buyer-seller transaction cost.
+This tax leverages the benefits of modern distribution channels, making sure that no buyer remains disadvantaged. 
+At the same time, innovative products can spread globally, whereas less specialised products remain local. 
+This is achieved through the following taxation mechanism: 
+Consider a set of $|F|$ firms, all offering the same product, and a set of $|B|$ potential buyers (customers). 
+For any buyer $b \in C$ and firm $f \in F$, we define the ordinal distance $D = D(b,f)$ such that the firm $f$ that is physically closest to $b$ has distance $D(b,f)=1$, the next closest has distance $D=2$, and the $n$-th closest has distance $D=n$.
+The tax when customer $b$ buys from the $n$-th closest firm is then proportional to $D^\gamma$, for some exponent $\gamma > 0$. 
+If we were to set $\gamma = 0$, everybody can buy from every firm for the same amount of tax. 
+If we were to set $\gamma=\infty$, a seller can only buy from its closest firm.
+A gamma in-between those two extremes represents a trade-off: 
+Close-by products are taxed less than far away products. 
+However, because the distance is ordinal, absolute distances do not matter. 
+No matter whether the next closest firm is $100$ meters or $100$ kilometres, the taxation is the same. 
+In particular, if there is only one firm offering the product, everybody buys for the same tax (since $D=1$ for every buyer), enabling innovations to spread globally.
 
-In this work, we introduce an individualized tax between buyers and firms based
-on distance. Through tuning of this tax and targeted redistribution of tax
-money to regions of low economic activity, we show that this model is able to
-[put conclusions here, everything else right now is speculation.]
+Through tuning of $\gamma$ and targeted redistribution of tax money to regions of low economic activity, we show that this model is able to fuel a self-consistent economy, 
+with fair competition, where innovations can spread freely, but without the chance of monopolies emerging through disproportional feedback mechanisms. 
+In summary, we present a model that avoids the winner-take-all monopoly tendency and associated negative externalities of today's internet enabled business through a low cost tax based on a topological constraint.
 
-\section{Introduction}
-Consider competing firms in a number of small towns. Each town wants to
-encourage their local firm to succeed, but at the same time does not want for
-its citizens to face monopoly prices. Hence, the towns all levy small,
-percentage sales taxes on out of town goods. These taxes increase as the origin
-of the good gets more distant.
+\section{Model Set-Up}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-In addition, the firms that initially do well tend to get better and better
-over time and build up an advantage over other firms. This is especially true
-with network based firms, where quality of the product is dwarfed by quantity
-of the network.
-
-\green{If we don't add the start up stuff, delete this.}
-With enough market power, a profit seeking firm will try to raise barriers to
-entry to prevent competition. This stops firms that have new innovations from
-surviving long enough to succeed in a market. The distance based tax introduced
-in this paper allows start ups to overcome entrenched monopolies' unfair
-advantages.
-
-In this paper, we propose an idiosyncratic tax based on distance in order to
-solve these problems, then show that it works by modelling an economy that
-implements the tax. In section 2 we give an overview of this economy. In
-section 3 we formalize the model, and discuss how the firms compete on capacity
-and price. In section 4, we discuss results of running the model. In section 5
-we expand the model by allowing for multiple timesteps, and having firms
-decrease their costs based on previous profits as a form of investment.
-%[change as we add sections]
-
-\section{Economy}
-We simulate an economy of buyers and firms in some environment with a distance
-metric (e.g. a country, a network economy), then observe how firms respond when
-we apply the idiosyncratic tax.
+We simulate an economy of firms and customers in some environment with a distance metric (e.g. a country) and study how firms respond to the idiosyncratic tax.
+In this section, we outline the model semi-quantitatively. 
+Game-theoretical details are then elaborated in section \ref{sec:game_theory} and concrete applications are described in the subsequent sections. 
+Section \ref{sec:conclusions} summarises the results and suggests future directions.
 
 \subsection{Geography}
-The geography of our model is one-dimensional with periodic boundaries (i.e.
-a topological circle) of length $L$. Due to the periodic boundary conditions,
-we measure physical distances with the metric $\min(|x-y|, L-|x-y|)$ for any
-two points (`agents') $x$,$y$ on the circle. Without loss of generality, we set
-$L=1$. Our model does not rely on the implemented geography, and any other,
-potentially more realistic topology could be considered.
+The geography of our model is one-dimensional with periodic boundaries (i.e. a topological circle) of length $L$. 
+Due to the periodic boundary conditions, we measure physical distances with the metric $\min(|b-f|, L-|b-f|)$ for any two points $b$,$f$ (i.e. buyers and firms) on the circle. 
+Without loss of generality, we set $L=1$. 
+The left-hand-side plots of Figure \ref{fig:fig3x2SingleTimestep} are examples of this `abstract geography'.
+Our results not rely on the implemented geography, and any other, potentially more realistic topology could be considered.
+However, as we outline above, a simple ring-topology is sufficient for practical purposes, and could be implemented on digital market places such as Amazon.
 
-The left insets of Figure \ref{fig:fig3x2SingleTimestep} are examples of
-such a geography.
+\subsection{Product}
+In a first approach, we consider an economy of only one unique product. 
+We assume that all firms produce that same product, but at potentially different production costs. 
+Extensions to more products are essentially straight forward and discussed in the outlook section below.
 
 \subsection{Buyers}
-We randomly place buyers on the circle. Each buyer tries to buy as much product
-as possible, but is constrained by a negatively sloped demand curve which
-lowers the amount of product they can buy the more expensive the product gets.
+Buyers are placed on the circle uniformly at random. 
+Each buyer tries to buy as much product as possible, but is constrained by a negatively sloped demand curve which lowers the amount of product they can buy the more expensive the product gets.
 
 \subsection{Firms}
-The firms, like the buyers, are also randomly placed on the circle, and compete
-non-cooperatively to maximize their profit. In this competition, also known as
-a game, each firm makes two choices, first capacity (i.e. how much they
-produce), then price. A firm chooses capacity before price because it is
-difficult to quickly change capacity due to supply chain restraints, while it
-is easier to change a price tag.
+The firms, like the buyers, are also randomly placed on the circle, and compete non-cooperatively to maximize their profit. 
+In this competition, also known as a `game' in the context of gam theory, each firm makes two choices, first capacity (i.e. how much they produce), then price. 
+A firm chooses capacity before price because it is difficult to adapt capacity due to supply chain restraints, while it is easier to change a price tag.
+
+For the remainder of this article, the location of buyers and sellers is held fixed. 
+This can be relaxed later on, assuming that their location changes on time-scales slower than numerous transactions with clients.
 
 \subsection{Idiosyncratic Tax}
-The idiosyncratic tax that is introduced by this paper is dependent on a
-distance measure $D$, or ordinal distance, that gives a discrete distance
-between every pair of buyers and firms. We define the ordinal distance $D$ be
-defined such that the closest firm to a buyer is at ordinal distance $D=1$, the
-next closest at $D=2$, and the $n$th closest at $D=n$. Consider a subset of a
-larger economy consisting of a firm and two buyers, one buyer near the firm,
-the other distant. \green{right here I am trying to express show that because
-of the tax, two buyer's can perceive different prices at the same firm.} The
-idiosyncratic tax means that the nearer buyer can buy more cheaply from that
-firm than can the more distant one. This incentivizes buyers to purchase from
-more local firms.
+The idiosyncratic tax that is introduced by this paper is dependent on a distance measure $D$, or ordinal distance, that gives a discrete distance between every pair of buyers and firms. 
+We define the ordinal distance $D$ be defined such that the closest firm to a buyer is at ordinal distance $D=1$, the next closest at $D=2$, and the $n$th closest at $D=n$. 
+If buyer $b$ wants to buy a product from its $n$-th closest firms, a tax proportional to $n^\gamma$ for some $\gamma \geqslant 0$ is raised. 
+This incentivizes buyers to purchase from more local firms, unless a remote firm offers th same product for a considerably lower price, that offsets the tax.
 
-Crucially, this ordinal distance is calculated for every individual type of
-product. This means that a dentist and a bakery do not increase each other's
-distance from their buyers. In addition, if a firm produces a new product, such
-as a drug for a previously incurable disease, it is considered at distance 1
-from all buyers, at least until a competitor emerges.
+Crucially, this ordinal distance is calculated for every individual type of product. 
+So for instance a car manufacturer and a bakery do not increase each other's distance from their buyers.
+Thus, if a firm produces a new product, such as a drug for a previously incurable disease, it is considered at distance $D=1$ from all buyers, at least until a competitor emerges.
+This way, new technologies and true innovation can spread freely, whereas more basic products remain more localised.
 
-\section{Model Definition}
-When firms choose capacity and price, they make their choices in order to
-maximize profit. First, the firms compete on capacity, by simultaneously
-declaring how much of the product they plan to produce; next, they compete on
-price to determine the firms' non-tax prices. This process, consisting of these
-two subgames, is called a Kreps-Scheinkman game \cite{kreps1983quantity}.
-The major difference we introduce to the classical Kreps-Scheinkman game is the
-idiosyncratic tax, which significantly alters the pricing subgame.
+\section{Equilibrium Capacities \& Prices}
+\label{sec:game_theory} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this section, we explain how firms set their production quantities and prices based on game theoretically equilibria. 
+The reader only interested in qualitative results may skip this section, and continue reading in section \ref{sec:static_game}.
+
+When firms choose capacity and price, they make their choices in order to maximize profit. 
+First, the firms compete on capacity, by simultaneously declaring how much of the product they plan to produce; next, they compete on price to determine the firms' non-tax prices. 
+This process, consisting of these two sub-games, is similar to the games studied by \cite{kreps1983quantity}.
+From a game-theoretical perspective, the major difference is the idiosyncratic tax, which significantly alters the pricing sub-game.
+
+The exact quantity and price offered by each firm are determined as the Nash equilibrium of this two-stage game. 
+The firm's strategy-space is thus given by the number of quantity that they produce and the prices that they can offer.
 
 \subsection{Capacity Game}
-The first choice is how much capacity $\hat q_i$ each firm $i$ wishes to
-install. The firm's desire to increase capacity is limited by two factors.
-First, firm $i$ incurs a unit price of $c_i$ for every unit of product they
-install, regardless of whether or not the product is sold. Second, because the
-buyers have a limited demand, eventually the buyers will stop buying.
+The first choice is how much capacity $\hat q_f$ each firm $f$ wishes to produce.
+The firm's desire to increase capacity is limited by two factors.
+First, firm $f$ incurs a unit price of $c_f$ for every unit of product they
+install, regardless of whether or not the product is sold. 
+Second, buyers have limited demand.
 
-The capacity subgame acts much like a Cournot game.\footnote{A Cournot game is
-where firms compete only on quantity, and sell all of the quantity at the
-market clearing price.} The difference is that instead of being assigned a
+The capacity sub-game acts much like a Cournot game.
+\footnote{
+A Cournot game is where firms compete only on quantity, and sell all of the quantity at the market clearing price.
+} 
+The difference is that instead of being assigned a
 market clearing price and selling everything they produce, in our model the
-firms compete on price in a second subgame where they choose a price. This
-subgame is necessary because the idiosyncratic tax can provide incentive for
+firms compete on price in a second sub-game where they choose a price. This
+sub-game is necessary because the idiosyncratic tax can provide incentive for
 firms to charge different prices. For example, a firm with low costs trying to
-sell to non-local buyers would need to price undercut those customer's local
-firm.
+sell to non-local buyers would need to undercut firms that ar more local to those potential customers. 
+Depending on the tax, this may or may not increase profits.
 
 \subsection{Pricing Game}
-Each firm $i$, having chosen a capacity $\hat q_i$, now chooses a price, $p_i$.
-Consider two vending machines right beside one another selling the same soda,
-with one machine selling soda at a cheaper price than the other. In this
-subgame, buyers will use the cheaper machine first, but if the buyers demand
-more soda than that machine's capacity, buyers will switch to the more
-expensive machine when the cheaper one runs out of soda. Competition on price
-in such a manner is called an Edgeworth game.
 
-By choosing a lower price, a firm can undercut competitors, ensuring that
-buyers choose to buy from them instead of other firms. Since the amount a buyer
-purchases increases as the product gets less expensive, a lower price increases
-the amount of product purchased in total. But the capacity limitation on total
-quantity sold by a firm means that a single firm usually can't sell to the
-entire market, and it could be more profitable to just sell a low quantity at a
-much higher price.
+Each firm $f$, having chosen a capacity $\hat q_f$, now chooses a price, $p_f$.
+
+By choosing a lower price, a firm can undercut competitors. 
+Since the amount a buyer purchases increases as the product gets less expensive, a lower price increases the amount of product purchased in total.
+
+Note that usually, it is not optimal for a firm to offer products so cheaply that it can sell to the entire market. 
+It tends to be more profitable to sell a lower quantity locally at a higher price.
 
@@
 
-For any buyer $b$ and firm $i$, we define the ordinal distance $D = D(b,i)$
-such that the firm $i$ that is physically closest to $b$ has distance
-$D(b,i)=1$, the next closest has distance $D=2$, and the $n$th closest has
-distance $D=n$.  Thus, if buyer $b$ buys from firm $i$, the total price,
-including tax, is given by $p(b,i) = p_i + p_i \cdot r(D(b,i)^\gamma -1)$
+For any buyer $b$ and firm $f$, we define the ordinal distance $D = D(b,f)$
+such that the firm $f$ that is physically closest to $b$ has distance
+$D(b,f)=1$, the next closest has distance $D=2$, and the $n$th closest has
+distance $D=n$.  Thus, if buyer $b$ buys from firm $f$, the total price,
+including tax, is given by 
+\begin{equation}
+	p(b,f) = p_f + p_f ~ r~ \left( D(b,f)^\gamma - 1 \right)
+\end{equation}
 where $\gamma$ is the coefficient governing how quickly the tax increases, and
-$r$ is a simple scaling coefficient.
+$r$ is a simple scaling coefficient (set to $5\%$ in the remainder of this report).
 
-Implementing this tax gives the buyers individualized preferences
-over the firms. For example, imagine two firms $i$ and $j$, and let $p_i <
-p_j$. Without any tax, every buyer prefers buying from $i$ versus buying from
-$j$. But with the tax, this could change. Say that buyer $b$ is very close to
-firm $j$, and very far from firm $i$, which would mean that $D(b,i) \gg
-D(b,j)$. Then buyer $b$ would prefer to buy from $j$ despite $j$'s price
-being higher because $p_i + p_i\cdot r(D(b,i)^\gamma - 1) > p_j + p_j\cdot
-r(D(b,j)^\gamma -1)$.
+Implementing this tax gives the buyers individualized preferences over the firms. 
+For example, imagine two firms $f$ and $g$, and let $p_f <p_g$. 
+Without any tax, every buyer prefers buying from $f$ versus buying from $g$. 
+But with the tax, this could change. 
+Say that buyer $b$ is very close to firm $g$, and very far from firm $f$ (in the sense that there is many other firms in-between). 
+This implies $D(b,f) \gg D(b,g)$ and hence $p(b,f) > p(b,g)$, such that $b$ busy from $g$. 
+Quantitative examples are provided in section \ref{sec:static_game}.
 
-This gives rise to two interesting limit cases, one where $\gamma = 0$, and the
-other where $\gamma = \infty$. When $\gamma = 0$, no firms are taxed anywhere,
-so the game simplifies into a pure Kreps-Scheinkman game. In contrast, when
-$\gamma = \infty$, it becomes impossible for buyers to purchase from non local
-firms, and so the firms all impose monopolistic prices.
+There are two limit cases: $\gamma=0$ and $\gamma=\infty$. 
+When $\gamma = 0$, no firms are taxed anywhere, so the game simplifies into a pure \cite{kreps1983quantity} game.
+In contrast, when $\gamma = \infty$, it becomes impossible for buyers to purchase from non local firms, and so the firms all impose monopolistic prices.
 
-\subsection{Buyer Behavior and Rationing}
-After the firms have finished determining capacity and price, and the
-idiosyncratic tax has been incorporated into the prices, the buyers conduct
-purchases as follows.
+\subsection{Buyer Allocation}
 
-Let the set of buyers be called $B$. Each buyer $b\in B$ buys a quantity $q_b =
-\sum_{i\in S} q_{b,i}$, where $q_{b,i}$ is the amount buyer $b$ buys from the
-firm $i$. The buyer's all have identical demand curves $p_\text{max} + q_b =
-a$, where $a$ is the endowment they are given exogenously, and $p_\text{max}$
-is the maximum price they pay (including tax). Each buyer tries to maximize
-$q_b$ while keeping $p_\text{max} + q_b \le a$. In other words, they buy from
-the cheapest available firm until they hit the demand curve and stop buying, or
-the firm runs out of capacity and the buyer begins buying from the next
-cheapest, repeating the process.
+Consider two vending machines right beside one another selling the same soda, with one machine selling soda at a cheaper price than the other. 
+Customers will buy from the cheaper machine first until it runs out, and will then switch to the more expensive machine until their demand is satisfied. 
+This generic type of consumer behaviour is implemented in our two-step game as well: 
+Buyer's start buying from the cheapest buyer first (incl. taxes), then move on to the second cheapest, and so forth. 
+Throughout the game, we assume global information, i.e. buyers are perfectly aware of all prices. 
+This is good approximation of reality when considering digital market places such as Amazon.
+
+More formally, let the set of buyers be called $B$. 
+Each buyer $b\in B$ buys a quantity $q_b =\sum_{f\in F} q_{b,f}$, where $q_{b,f}$ is the amount buyer $b$ buys from the firm $f$. 
+The buyer's all have identical demand curves $p_\text{max} + q_b = a$, where $a$ is the endowment, and $p_\text{max}$is the maximum price they are willing to pay (including tax). 
+Each buyer tries to maximize $q_b$ while keeping $p_\text{max} + q_b \le a$. 
+In other words, they buy from the cheapest available firm until they hit the demand curve and stop buying, or the firm runs out of capacity and the buyer begins buying from the next cheapest, repeating the process.
 
@@
 curve, or a seller runs out of capacity. 
+This assumption is known as rationing.
 
 \subsection{Profit Function}
-Finally, firm $i$, having chosen quantity $\hat q_i$ and price $p_i$, and
-having sold some or all of their capacity to buyers, will earn a profit:
+After having produced $\hat q_f$ units sold at price $p_f$, firm $f$'s profit is given by 
+\begin{equation}
+    \Pi_f = p_f \sum_{b\in B} q_{b,f} - c_f\hat q_f.
+\end{equation}
+Also, each $q_{b,f}$ is chosen by the buyer $b$ so that they buy as much as possible while staying under their demand curve $P+Q\leq a$; 
+this is where taxes affect the firm's profit.
 
+If the firm sells all of their capacity, then $q_f = \hat q_f$, and the profit equation simplifies to:
 \begin{equation}
-    \Pi_i = p_i\sum_{b\in B} q_{b,i} - c_i\hat q_i.
-\end{equation}
-
-Also, each $q_{b,i}$ is chosen by the buyer $b$ so that they buy as much as
-possible while staying under their demand curve $P+Q\leq a$; this is where
-taxes affect the firm's profit.
-
-If the firm sells all of their capacity, then $q_i = \hat q_i$, and the profit
-equation simplifies to:
-\begin{equation}
-    \Pi_i = (p_i- c_i)\hat q_i,
+    \Pi_f = (p_f- c_f) \hat q_f,
 \end{equation}
@@
 
-\subsection{Numerical Approximation}
-Because the buyers have individualized preferences and the pricing game does
-not necessarily have a `best' price choice, it is difficult to determine a
-generalized, theoretical solution to the model laid out above. Instead, we
-numerically determine the Nash equilibrium.\footnote{A Nash equilibrium
-for a game is a set of choices, one for each player, such that upon seeing the
-other firm's choices, could increase their payoff by changing strategies. In
-our model, the players are firms, the payoff is profit, and the choices are
-either capacity or price, depending on the subgame.}
+\subsection{Numerical Solution of Nash Equilibria}
 
-To find the capacities and prices that the firms will choose, we begin by
-discretizing the capacity and pricing choices so we only have a finite number
-of possible combinations. Then, for every outcome of the capacity game, we find
-the Nash equilibrium of the pricing game using the Python library Gambit
-\cite{gambitPython}. Then, using the equilibrium prices, we calculate the
-profits for every outcome of the capacity game. We finally use this information
-to find the Nash equilibrium of the capacity game.
+The firms determine their capacity and price such that they are in a Nash equilibrium. 
+Because of the idiosyncratic structure of the game, which depends on the exact location of buyers and sellers, 
+it is not possible to determine the Nash equilibrium analytically, for general cases. 
+Instead, we use the Gambit library developed by  \cite{gambitPython} to find the Nash equilibrium numerically. 
+To this end, the strategy space of capacities and prices are discretised into a sufficiently fine grid. 
+Then, the quantity-price two-step game is solved in reverse order: 
+For every choice of quantity, the equilibrium price is determined.
+Then, the equilibrium quantity is determined. 
+Example solutions are provided in the next section.
 
-\section{Examples}
-In Figure \ref{fig:fig3x2SingleTimestep} we can see the idiosyncratic tax
-dampen Firm 1's attempts to become a monopoly power. In Rows 1 and 2, there is
-no tax as $\gamma = 0$. While Firm 1 and 2 have an equal cost per unit, no firm
-can become a monopoly. But if we reduce Firm 1's cost per unit by $1\%$, they
-sell 14\% more than their competition, and earn 33\% more profit, which is out
-of proportion to Firm 1's actual accomplishment, and can lead to
-anti-competitive behavior by Firm 1.
-
-In contrast, in Rows 3, 4, and 5, we let $\gamma = 1$. In Row 3 we can see a
-mirror of Row 1, where both firms, faced with the same costs, produce the same
-quantity, and make the same profit. But in row 4, where we give Firm 1 the same
-advantage we game them in the row 2, they sell the same amount, and only make
-12\% more profit than Firm 2, which implies that our tax protects Firm 2 from
-small decrease in Firm 1's cost per unit. To increase their market share, Firm
-1 needs to reduce their costs to 80\% of Firm 2, as shown in row 5.
-
-The idiosyncratic tax thus dampens monopolistic tendencies of firms with slight
-competitive advantages, while still ensuring that minor innovations are
-profitable. But, if one firm is significantly better, as in Row 5, then that
-firm will still dominate the market.
+\section{Towards a More Balanced Economy}
+\label{sec:static_game}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   \vspace{-2cm} % shift upwards to get more space for caption
-  \includegraphics[width=\linewidth]{5x2plot.png}
-  \caption{\small{Above are the model's results for a variety of
-  conditions. The Rows 1 and 2 have $\gamma=0.0$, while Rows 3, 4, and 5 have
-  $\gamma = 0.5$. In Rows 1 and 3, the firms have an equal cost per unit, sell
-  equal quantity, and make equal profit. In Row 2, where $\gamma=0$, a 1\%
-  difference in cost implies Firm 1 sells 14\% more quantity, and earns a 33\%
-  larger profit.
-  In Row 4, where $\gamma=.5$, Firm 1's 1\% difference in cost now results in
-  an equal market share, but they still profit 11\% more. To get a larger
-  market share, as in Row 5, Firm 1 must have a 20\% lower cost per unit. This
-  implies that $\gamma$ dampens a firm's ability to gain market power from
-  small innovations, without significantly discouraging innovation. 
-  %[Check numbers after new gamma]
+  \includegraphics[width=\linewidth]{static_game.png}
+  \caption{\small{
+  		The balancing effect of the distance-based tax is demonstrated. 
+		The first two rows depict an economy where the is no distance-based tax. 
+		If costs are equal, the profits are equal as well. 
+		But if costs are marginally different, the game-theoretical equilibrium profit are disproportionally large. 
+		The mitigating effect of a distance-based tax is considered in rows 3-5. 
+		If costs are equal (row 3) or marginally different (row 4), then profits are only marginally different. 
+		But if costs are significantly different (row 5), so are the equilibrium profits. 
+		An interpretation in an economic context is provided in the text of subsection \ref{sec:static_game}. 
 		 }}
-  \label{fig:fig3x2SingleTimestep}
+  \label{fig:static_game}
 \end{figure}
 
-\section{Dynamics}
-We run this model once for every timestep, then update the costs for the firms
-between the timesteps. Every timestep we split a 5\% decrease in costs between
-the firms according to the fraction of total profit the Firm makes. For
-example, if Firm 1 earned a profit of 80, and Firm 2 earned a profit of 20,
-then Firm 1's per unit cost would decrease by 4\%, and Firm 1's by 1\%.
+\subsection{A Static Economy} 
+\label{sec:static_economy}
 
-\newpage
-\printbibliography
+We are now demonstrating the social benefits of this taxation policy by considering an economy with a single product, only two firms and twelve buyers. 
+Firms and buyers are randomly distributed on the unit circle, but we have chosen a setting where each firm has six closest buyers (i.e. $D=1$, and the respective other six buyers have $D=2$). 
+This arrangement is shown in the left plots of Figure \ref{fig:static_game}, and purposefully kept the same for all five examples that we now show.
+
+First, we consider the case where no idiosyncratic, distance-based tax is applied ($\gamma=0$). 
+In case where the production cost of both firms is equal ($c_1=c_2 = 100$), we see in the top right plot of figure \ref{fig:static_game} that both firms produce and sell equally, as is to expect by symmetry.
+In the second row of Figure \ref{fig:static_game}, we then consider the case where firm $1$'s production cost is merely $1\%$ less than firm $2$'s cost ($c_1=100, c_2=99$). 
+However, the resulting profit, as dictated by the Nash equilibrium quantity and price, is a whopping $33\%$ larger for firm $1\%$ than for firm $2$. 
+This highlights the destabilising long-term effect that an economy of global trade with (converging towards) zero transportation cost may experience. 
+While a cost difference of only $1\%$ is hardly considered a major competitive advantage, the resulting difference in revenue is.
+
+A different scenario is shown in rows $3$ and $4$ of Figure \ref{fig:static_game}, where the distance-tax applies ($\gamma = 1/2$).
+In row 3, we witness again a symmetric outcome, as $c_1 = c_2 = 100$. 
+In row 4, we assume again that firm $1$'s production costs are just $1\%$ below firm $2$'s. 
+Here, however, the resulting difference in profit is reduced to $11\%$ (and could be reduced further if we were to increase $\gamma$  above $1/2$). 
+This shows clearly the balancing effect that the taxation based distance has.
+
+Row 5 finally shows the profit asymmetry obtained in a $\gamma=1/2$ economy where firm $1$'s production cost is $20\%$ lower than firm $2$'s. 
+The equilibrium profit functions determine that firm $1$ makes \red{(@Nate: add number)}-times more profit than firm $2$.
+
+This demonstrates the subtle but important difference induced by our distance-based tax:
+A minor difference in production cost, associated with an essentially negligible, random difference in one firm's competitiveness, is dampened to a balanced difference in profits. 
+On the other hand, a major difference in production cost, associated with major difference in one firm's competitiveness, is rewarded accordingly by significantly increased profits.
+
+\subsection{A Dynamic Economy}
+
+In the previous subsection, we have demonstrated how a distance-tax-free $\gamma=0$ economy disproportionally rewards essentially random, minor differences in firm competitiveness. 
+But even more concerningly, the problem does not stay static: 
+This disproportional revenue can be used to further invest in aggressive marketing, thereby increasing the difference between the two firms even more. 
+This may ultimately run a firm out of business, although it was initially effectively competitive as the other firms.
+
+We highlight this mechanism more quantitatively by running the following simple game:
+The same economy as in subsection \ref{sec:static_economy} is considered (2 firms, 12 buyers, 6 closest buyers each). 
+However, instead of just offering one static set of quantities and prices, here we consider multiple business cycles (e.g. quarters, or years). 
+Firm $1$ starts with an initial production cost that is only $1\%$ below that of firm $2$'s. 
+But then, each of the two firms use their profit to effectively subsidise their costs, allowing them to offer lower prices during the next round. 
+The outcome of this experiment is depicted in figure \ref{fig:dynamic_game},
+
+\section{Conclusions \& Outlook}
+\label{sec:conclusions}
+
+\red{
+mention
+- multiple products
+- fixed location
+- implementation on digital market place
+- vision
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{References}
+\bibliographystyle{apa}
+\bibliography{bibliography.bib}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2019-06-25 code/turn_model.py
Multiple fixes to turn_model.py

@@ -75,19 +75,20 @@ def dic_from_a_dic(a_dic):
     ret = dict(zip(a_key, a_a_value))
     return ret
 
-def process(d_settings, num_loops):
+def process(d_settings, num_loops, price_diff):
     a_d_turns = loop(d_settings, num_loops)
     d_turns = dic_from_a_dic(a_d_turns)
     folder1 = '/home/nate/Documents/abmcournotmodel/code/output/data/'
     folder2 = '/cluster/home/slera//abmcournotmodel/code/output/data/'
     folder  = folder1 if os.path.exists(folder1) else folder2
-    fn = folder + 'alt_adv_fast_turn_gamma={}_scalar_tax={}_endow={}.pickle'.format(round(d_settings['gamma'],3), d_settings['scalar_tax'], d_settings['endowment'])
+    fn = folder + 'alt_fast_adv={}_turn_gamma={}_scalar_tax={}_endow={}.pickle'.format(price_diff, round(d_settings['gamma'],3), d_settings['scalar_tax'], d_settings['endowment'])
     jl.dump(d_turns, fn)
 
 if __name__ == "__main__":
     i = int(sys.argv[1]) - 1
     gamma = i/10.
     scalar_tax = 1.0
+    price_diff = 10
     endowment = 200
     num_sellers = 2
     num_buyers = 12
@@ -99,11 +100,11 @@ if __name__ == "__main__":
             'a_strat_quantity' : np.linspace(0, num_buyers*100, 21),
             'a_seller_loc' : np.linspace(start=0, stop=1, num=num_sellers, endpoint=False),
             'a_buyer_loc'  : np.linspace(start=0, stop=.999, num=num_buyers,  endpoint=False),
-            'a_cost' : np.array([99, 100]),
+            'a_cost' : np.array([100.-price_diff, 100.]),
             'gamma' : gamma,
             'scalar_tax' : scalar_tax,
             'endowment' : endowment,
             'mean_cost' : 100,
             'cost_ratio' : 1} 
-    process(d_settings, 20)
+    process(d_settings, 20, price_diff)
 

### 2019-06-25 writing/Paper/main.tex

@@
 		But if costs are significantly different (row 5), so are the equilibrium profits. 
-		An interpretation in an economic context is provided in the text of subsection \ref{sec:static_game}. 
+		An interpretation in an economic context is provided in the text of subsection \ref{sec:static_economy}. 
 		 }}
@@
 
-In the previous subsection, we have demonstrated how a distance-tax-free $\gamma=0$ economy disproportionally rewards essentially random, minor differences in firm competitiveness. 
+In the previous subsection, we have demonstrated how a distance-tax-free economy disproportionally rewards essentially random, minor differences in firm competitiveness. 
 But even more concerningly, the problem does not stay static: 
 This disproportional revenue can be used to further invest in aggressive marketing, thereby increasing the difference between the two firms even more. 
-This may ultimately run a firm out of business, although it was initially effectively competitive as the other firms.
+This may ultimately run a firm out of business, although it was initially as competitive as the other firms.
 

### 2019-06-25 code/turn_model.py
added print(fn) to turn_model.py so I can quickly scan lsf files for info.

@@ -81,15 +81,16 @@ def process(d_settings, num_loops, price_diff):
     folder1 = '/home/nate/Documents/abmcournotmodel/code/output/data/'
     folder2 = '/cluster/home/slera//abmcournotmodel/code/output/data/'
     folder  = folder1 if os.path.exists(folder1) else folder2
-    fn = folder + 'alt_fast_adv={}_turn_gamma={}_scalar_tax={}_endow={}.pickle'.format(price_diff, round(d_settings['gamma'],3), d_settings['scalar_tax'], d_settings['endowment'])
+    fn = folder + 'turn_fast_adv={}_gamma={}_scalar_tax={}_endow={}.pickle'.format(price_diff, round(d_settings['gamma'],3), d_settings['scalar_tax'], d_settings['endowment'])
+    print(fn)
     jl.dump(d_turns, fn)
 
 if __name__ == "__main__":
     i = int(sys.argv[1]) - 1
     gamma = i/10.
     scalar_tax = 1.0
-    price_diff = 10
-    endowment = 200
+    price_diff = 1
+    endowment = 120
     num_sellers = 2
     num_buyers = 12
     np.random.seed(17)

### 2019-06-25 writing/Paper/main.tex
Put in edits to paper

@@
 with local markets where people buy different products.  Take clothing as an
-example. Most villages had one or several clothing merchants competing for
+example. Most villages had one or more clothing merchants competing for
 customers.  There is some healthy competition among merchants within a village,
-as people can flexibly switch according to prices and preferences. But
-customers would rarely buy clothing from a faraway village, as the transaction
-cost associated with visiting that village would be high,  and could not offset
-a marginally better price or quality.  On the other hand, people living far
-away from any village are disadvantaged as they always incur such high costs.
+as people can flexibly switch according to prices and preferences. But customers
+would rarely buy clothing from a faraway village, as the transaction cost
+associated with visiting that village would be high,  and could not offset a
+marginally better price or quality.  On the other hand, people living far away
+from any village were disadvantaged as they would always incur such high costs.
 Similarly, if there is a specialized product that can only be produced in some
-villages, it was harder to find customers across village borders,  making it
-more difficult for new products and technologies to succeed.
+villages, it was harder to find customers across village borders, making it more
+difficult for new products and technologies to succeed.
 
-From the industrial to the technological revolution, more efficient
-distribution channels have emerged, enabling people to buy almost any product
-in online stores.  Independent of a customer's physical location, orders can be
-delivered to their door within a day.  More specialized products are now sold
-globally, and people living far away from hubs benefit from the availability of
-a wide range of products.  While such efficiency is beneficial for the economy
-as a whole, it comes at the cost of potential monopolies.  Consider a merchant
-that manages to sell a product for a few cents cheaper than its competitors. 
-Given modern distribution channels, and ignoring potential differences in
-quality, every buyer is now incentivized to buy from that one firm at the
-cheaper price. One potential outcome is that the competitors follow along,
-increase their efficiency, and a new equilibrium is reached.  However, in a
-suboptimal scenario, that one firm leverages the temporarily increased revenue
-to further outpace and potentially undercut its competitors.  In the short
-term, feedback mechanisms kick in, and an initially minor gap in competitive
-advantage, mixed with efficient distribution channels, manifests itself in a suboptimal monopoly.
+From the industrial to the technological revolution, more efficient distribution
+channels have emerged, enabling people to buy almost any product in online
+stores. Now, orders can be delivered to their door within a day independent of a
+customer's physical location  More specialized products are now sold globally,
+and even people living far away from cities benefit from the availability of a
+wide range of products. While such efficiency is beneficial for the economy as a
+whole, it comes at the cost of potential monopolies.  Consider a merchant that
+manages to sell a product for a few cents cheaper than its competitors.  Given
+modern distribution channels, and ignoring potential differences in quality,
+every buyer is now incentivized to buy from that one firm offering the cheaper
+price. One potential outcome is that the competitors follow along, increase
+their efficiency, and a new equilibrium is reached.  However, in a suboptimal
+scenario, that one firm leverages the temporarily increased revenue to further
+outpace and potentially undercut its competitors.  In the short term, feedback
+mechanisms kick in, and an initially minor gap in competitive advantage, mixed
+with efficient distribution channels, manifests itself in a suboptimal monopoly.
 
@@
 This tax leverages the benefits of modern distribution channels, making sure that no buyer remains disadvantaged. 
-At the same time, innovative products can spread globally, whereas less specialised products remain local. 
+At the same time, innovative products can spread globally, whereas less specialized products remain local. 
 This is achieved through the following taxation mechanism: 
 Consider a set of $|F|$ firms, all offering the same product, and a set of $|B|$ potential buyers (customers). 
-For any buyer $b \in C$ and firm $f \in F$, we define the ordinal distance $D = D(b,f)$ such that the firm $f$ that is physically closest to $b$ has distance $D(b,f)=1$, the next closest has distance $D=2$, and the $n$-th closest has distance $D=n$.
+For any buyer $b \in B$ and firm $f \in F$, we define the ordinal distance $D = D(b,f)$ such that the firm $f$ that is physically closest to $b$ has distance $D(b,f)=1$, the next closest has distance $D=2$, and the $n$-th closest has distance $D=n$.
 The tax when customer $b$ buys from the $n$-th closest firm is then proportional to $D^\gamma$, for some exponent $\gamma > 0$. 
-If we were to set $\gamma = 0$, everybody can buy from every firm for the same amount of tax. 
+If we were to set $\gamma = 0$, everybody can buy from every firm at single tax rate. 
 If we were to set $\gamma=\infty$, a seller can only buy from its closest firm.
@@
 with fair competition, where innovations can spread freely, but without the chance of monopolies emerging through disproportional feedback mechanisms. 
-In summary, we present a model that avoids the winner-take-all monopoly tendency and associated negative externalities of today's internet enabled business through a low cost tax based on a topological constraint.
+In summary, we present a model that avoids the winner-take-all monopoly tendency and associated negative externalities of today's Internet enabled business through a tax based on a topological constraint \green{the tax is not always small, and definitely not in our examples}.
 
@@
 
-We simulate an economy of firms and customers in some environment with a distance metric (e.g. a country) and study how firms respond to the idiosyncratic tax.
+We simulate an economy of firms and customers in some environment with a distance metric (e.g. a country using road distance) and study how firms respond to the idiosyncratic tax.
 In this section, we outline the model semi-quantitatively. 
@@
 Without loss of generality, we set $L=1$. 
-The left-hand-side plots of Figure \ref{fig:fig3x2SingleTimestep} are examples of this `abstract geography'.
+The left-hand-side plots of Figure \ref{fig:static_game} are examples of this `abstract geography'.
 Our results not rely on the implemented geography, and any other, potentially more realistic topology could be considered.
@@
 \subsection{Product}
-In a first approach, we consider an economy of only one unique product. 
+In a first approach, we consider an economy of only one product. 
 We assume that all firms produce that same product, but at potentially different production costs. 
@@
 The firms, like the buyers, are also randomly placed on the circle, and compete non-cooperatively to maximize their profit. 
-In this competition, also known as a `game' in the context of gam theory, each firm makes two choices, first capacity (i.e. how much they produce), then price. 
+In this competition, also known as a `game' in the context of game theory, each firm makes two choices, first capacity (i.e. how much they produce), then price. 
 A firm chooses capacity before price because it is difficult to adapt capacity due to supply chain restraints, while it is easier to change a price tag.
@@
 If buyer $b$ wants to buy a product from its $n$-th closest firms, a tax proportional to $n^\gamma$ for some $\gamma \geqslant 0$ is raised. 
-This incentivizes buyers to purchase from more local firms, unless a remote firm offers th same product for a considerably lower price, that offsets the tax.
+This incentivizes buyers to purchase from more local firms, unless a remote firm offers the same product for a considerably lower price, offsetting the tax.
 
 Crucially, this ordinal distance is calculated for every individual type of product. 
-So for instance a car manufacturer and a bakery do not increase each other's distance from their buyers.
+For instance, a car manufacturer and a bakery do not increase each other's distance from their buyers.
 Thus, if a firm produces a new product, such as a drug for a previously incurable disease, it is considered at distance $D=1$ from all buyers, at least until a competitor emerges.
-This way, new technologies and true innovation can spread freely, whereas more basic products remain more localised.
+This way, new technologies and true innovation can spread freely, whereas more basic products remain more localized.
 
@@
 
-In this section, we explain how firms set their production quantities and prices based on game theoretically equilibria. 
-The reader only interested in qualitative results may skip this section, and continue reading in section \ref{sec:static_game}.
+In this section, we explain how firms set their production quantities and prices based on game theoretic equilibria. 
+The reader only interested in qualitative results may skip this section and continue reading in section \ref{sec:static_game}.
 
@@
 
-The capacity sub-game acts much like a Cournot game.
-\footnote{
-A Cournot game is where firms compete only on quantity, and sell all of the quantity at the market clearing price.
-} 
-The difference is that instead of being assigned a
+%put the '\footnote' right next to the period to avoid weird spacing between footnote and end of sentence
+The capacity sub-game acts much like a Cournot game.\footnote{
+A Cournot game is where firms compete only on quantity, and sell all of the quantity at the market clearing price.} 
+The difference is that instead of firms being assigned a
 market clearing price and selling everything they produce, in our model the
@@
 firms to charge different prices. For example, a firm with low costs trying to
-sell to non-local buyers would need to undercut firms that ar more local to those potential customers. 
+sell to non-local buyers would need to undercut firms that are more local to those potential customers. 
 Depending on the tax, this may or may not increase profits.
@@
 Note that usually, it is not optimal for a firm to offer products so cheaply that it can sell to the entire market. 
-It tends to be more profitable to sell a lower quantity locally at a higher price.
+It tends to be more profitable to sell a lower quantity locally at a higher price.\green{I don't know if I would go this far here.}
 
@@
 
+\green{This is the third time we define ordinal distance. We should cut at least
+one}
 For any buyer $b$ and firm $f$, we define the ordinal distance $D = D(b,f)$
@@
 where $\gamma$ is the coefficient governing how quickly the tax increases, and
-$r$ is a simple scaling coefficient (set to $5\%$ in the remainder of this report).
+$r$ is a simple scaling coefficient (set to $100\%$ in the remainder of this
+report\green{in teh bar plots, $r=1$}).
 
@@
 This generic type of consumer behaviour is implemented in our two-step game as well: 
-Buyer's start buying from the cheapest buyer first (incl. taxes), then move on to the second cheapest, and so forth. 
+buyer's start buying from the cheapest buyer first (incl. taxes), then move on to the second cheapest, and so forth. 
 Throughout the game, we assume global information, i.e. buyers are perfectly aware of all prices. 
@@
 Each buyer $b\in B$ buys a quantity $q_b =\sum_{f\in F} q_{b,f}$, where $q_{b,f}$ is the amount buyer $b$ buys from the firm $f$. 
-The buyer's all have identical demand curves $p_\text{max} + q_b = a$, where $a$ is the endowment, and $p_\text{max}$is the maximum price they are willing to pay (including tax). 
+The buyers all have identical demand curves $p_\text{max} + q_b = a$, where $a$ is the endowment, and $p_\text{max}$ is the maximum price they buy product at (including tax). 
 Each buyer tries to maximize $q_b$ while keeping $p_\text{max} + q_b \le a$. 
@@
 \begin{equation}
-    \Pi_f = p_f \sum_{b\in B} q_{b,f} - c_f\hat q_f.
+    \Pi_f = p_f \sum_{b\in B} q_{b,f} - c_f\hat q_f,
 \end{equation} 
-Also, each $q_{b,f}$ is chosen by the buyer $b$ so that they buy as much as possible while staying under their demand curve $P+Q\leq a$; 
-this is where taxes affect the firm's profit.
+where  $p_f \sum_{b\in B} q_{b,f}$ is the firm's revenue, and $ c_f\hat q_f$ is the firm's total cost.
+Taxes affect the firm's profit by altering buyer's preferences, hence changing $q_{b,f}$.
 
@@
 
-The firms determine their capacity and price such that they are in a Nash equilibrium. 
+The firms choose their capacity and price such that they are in a Nash equilibrium. 
 Because of the idiosyncratic structure of the game, which depends on the exact location of buyers and sellers, 
@@
 A different scenario is shown in rows $3$ and $4$ of Figure \ref{fig:static_game}, where the distance-tax applies ($\gamma = 1/2$).
-In row 3, we witness again a symmetric outcome, as $c_1 = c_2 = 100$. 
+In row 3, we again witness a symmetric outcome, as $c_1 = c_2 = 100$. 
 In row 4, we assume again that firm $1$'s production costs are just $1\%$ below firm $2$'s. 
@@
 This demonstrates the subtle but important difference induced by our distance-based tax:
-A minor difference in production cost, associated with an essentially negligible, random difference in one firm's competitiveness, is dampened to a balanced difference in profits. 
+a minor difference in production cost, associated with an essentially negligible, random difference in one firm's competitiveness, is dampened to a balanced difference in profits. 
 On the other hand, a major difference in production cost, associated with major difference in one firm's competitiveness, is rewarded accordingly by significantly increased profits.
@@
 This disproportional revenue can be used to further invest in aggressive marketing, thereby increasing the difference between the two firms even more. 
-This may ultimately run a firm out of business, although it was initially as competitive as the other firms.
+This may ultimately run a firm out of business, despite initially being as competitive as the other firms.
 

### 2019-06-25 PlotData.py
another gitignore update for some reason.

@@ -1,0 +1,98 @@
+import numpy as np
+import pandas as pd
+from sklearn.externals import joblib as jl
+import pickle
+from matplotlib import pyplot as plt
+import seaborn as sns
+
+# CONSTANTS 
+NUM_BUYERS = 100
+STARTUP_COST = 1
+COST_PER_TIMESTEP = 3
+GAMMA = 1 + (3.5/16)
+WEALTH_TAX = .0
+RATE_NEW_SELLER = .0
+PLOT_TITLE = 'Gamma = {0:.2f}, Buyers = {1:}, Cost = {2:}, Tax = {3:2f}, Rate = {4:2f}'.format(GAMMA,
+        NUM_BUYERS, COST_PER_TIMESTEP, WEALTH_TAX, RATE_NEW_SELLER)
+
+file_path = "C:/Users/CAREBEARSTARE3_USER/Documents/MITInternship/ModelWithSandro/Pickle/"
+FILE_NAME_FORMATER = file_path + 'gamma{0:.2f}_buyers{1:}_cost{2:}_tax{3:.2f}_rate{4:2f}.pickle'
+file_name_read = FILE_NAME_FORMATER.format(GAMMA, NUM_BUYERS, COST_PER_TIMESTEP, WEALTH_TAX, RATE_NEW_SELLER)
+print(file_name_read)
+
+d_load = jl.load(file_name_read)
+
+df_price = d_load['price']
+df_profit = d_load['profit']
+df_wealth = d_load['wealth']
+a_num_sellers = df_price.notna().sum(axis=1)
+df_num_sales_by_seller = d_load['num_sales_by_seller']
+df_num_sales_by_seller.fillna(0, inplace=True)
+df_num_sales_by_dist = d_load['num_sales_by_dist']
+df_num_closest_buyer = d_load['num_closest_buyer']
+df_num_closest_buyer.fillna(0, inplace=True)
+print(df_num_closest_buyer)
+
+MAX_TIMESTEP = len(a_num_sellers)-1
+
+print(type(a_num_sellers))
+
+############################################
+# set figure size
+############################################
+nrow            = 7 
+ncol            = 1
+width_scale     = 15
+height_scale    = 6
+figsize         = ( width_scale*ncol, height_scale*nrow )
+
+############################################
+# create the figure
+############################################
+fig = plt.figure(figsize=figsize)
+fig.suptitle(PLOT_TITLE)
+fig.subplots_adjust(wspace=0.4, hspace=.4)
+
+############################################
[…]

### 2019-06-25 code/time_plots.py

@@ -14,19 +14,15 @@ from multiple_bar_plots import ax_circle_from_data
 
 
 def write_time_plot_from_file(fn):
-# Run main function
-
-
-##############
-### SCRIPT ###
-##############
 
 ########
 # DATA #
 ########
-
+    d_load  = jl.load(folder + fn)
 # Data from d_load
 ##########################################################
+    scalar_tax          = d_load['scalar_tax'][0]
+    print(scalar_tax)
     gamma               = d_load['gamma'][0]
     endowment           = d_load['endowment'][0]
     num_sellers         = d_load['num_sellers'][0]
@@ -38,7 +34,7 @@ def write_time_plot_from_file(fn):
     pd_quantity         = pd.DataFrame(d_load['a_quantity_nash'])
     pd_quantity_sold    = pd.DataFrame(d_load['a_quantity_sold'])
     pd_price            = pd.DataFrame(d_load['a_price_nash'])
-    pd_cost             = pd.DataFrame(d_load['a_cost'])
+    pd_cost             = pd.DataFrame(np.array(d_load['a_cost']))
     pd_profit           = pd.DataFrame(d_load['a_profit'])
     print(pd_cost)
 
@@ -201,12 +197,12 @@ def write_time_plot_from_file(fn):
             num_sellers, num_buyers)
     out_folder = './output/plots/'
     if not os.path.exists(out_folder): os.makedirs(out_folder)
-    plt.savefig(out_folder + fn + '.pdf', bbox_inches='tight')
+    plt.savefig(out_folder + fn + '.png', bbox_inches='tight')
 
 # write figure to the screen (must go after file creation or doesn't write
 # correctly) 
 ############################################################
-    plt.show()
+    #plt.show()
 
 ##############
 ### SCRIPT ###
@@ -214,9 +210,9 @@ def write_time_plot_from_file(fn):
 
 if __name__ == "__main__":
     fn = str(sys.argv[1])
+    a_fn = np.array([['alt_adv_fast_turn_gamma={}.{}_scalar_tax=1.0_endow=200.pickle'.format(i, j) for i in range(2)] for j in range(10)]).flatten()
     folder1 = '/home/nate/Documents/abmcournotmodel/code/output/data/'
     folder2 = '/cluster/home/slera//abmcournotmodel/code/output/data/'
-    folder  = folder1 if os.path.exists(folder1) else folder2
[…]

### 2019-06-25 writing/Paper/main.tex
minor changes in document

@@
 The tax when customer $b$ buys from the $n$-th closest firm is then proportional to $D^\gamma$, for some exponent $\gamma > 0$. 
-If we were to set $\gamma = 0$, everybody can buy from every firm at single tax rate. 
+If we were to set $\gamma = 0$, everybody can buy from every firm at the same tax rate. 
 If we were to set $\gamma=\infty$, a seller can only buy from its closest firm.
@@
 with fair competition, where innovations can spread freely, but without the chance of monopolies emerging through disproportional feedback mechanisms. 
-In summary, we present a model that avoids the winner-take-all monopoly tendency and associated negative externalities of today's Internet enabled business through a tax based on a topological constraint \green{the tax is not always small, and definitely not in our examples}.
+In summary, we present a model that avoids the winner-take-all monopoly tendency and associated negative externalities of today's Internet enabled business through a discretised, distance-based tax.
 

### 2019-06-25 code/multiple_bar_plots.py
Fixed titles

@@ -23,7 +23,7 @@ def ax_circle_from_data(a_seller_pos, a_buyer_pos, m_quantity_bought, a_color,
 # Setup
     if ax is None:
         _, ax = plt.subplots()
-    ax.set_title(label='$\gamma$ = {}, Firm 1\'s cost is {}% lower.'.format(gamma, a_cost[1]-a_cost[0]))
+    ax.set_title(label='$\gamma$ = {}'.format(gamma))
     num_sellers = len(a_seller_pos)
 # plot a grey circle 
     r       = 1
@@ -66,6 +66,7 @@ def ax_bars_from_data(a_price, a_cost, a_quantity_sold, a_profit, a_color,
     a_xvalues = np.arange(1, num_sellers + 1)
     w = 0.2
 # plot the price for each buyer 
+    ax.set_title('Firm 1\'s cost is {}\% of firm 2\'s and makes {}\% more profit'.format(a_cost[0], int(round(a_profit[0]/a_profit[1] -1, 2)*100)))
     color = a_color[0]
     ax.bar(a_xvalues-w, a_price, width=.8*w, color=color,   alpha=1.0, align='center')
     ax.bar(a_xvalues-w, a_cost,  width=.8*w, color='black', alpha=0.2, align='center')

### 2019-07-23 code/model.py
changed some things, especially with model.py's taxation.

@@ -38,30 +38,10 @@ def get_a_cost_from_a_ratio(mean, a_ratio):
     ret = ret * mean / avg_ratio
     return ret
 
-def get_a_strat_quantity(lower_bound, upper_bound, num_strats,
-        is_randomized=False, is_shifted = False):
-    if is_randomized:
-        return get_rand_strats(lower_bound, upper_bound, num_strats, frac=.05)
-    shift = 0.
-    if is_shifted:
-        jump = (upper_bound - lower_bound)/(num_strats - 1)
-        shift = float(jump)/6
-    return np.linspace(lower_bound, upper_bound, num_strats) + shift
-    
 def get_a_strat_from_center(n, center, jump, shift = 0):
     dist = float(n * jump)/2
     ret = np.linspace(center - dist, center + dist, n) + shift
     return(ret)
-
-def get_rand_strats(lower_bound, upper_bound, num_strats, frac=.05):
-    '''
-    Slightly randomizes an array.
-    '''
-    a_strat_base, step = np.linspace(lower_bound, upper_bound, num_strats, retstep=True)
-    scale = frac * step
-    a_rand = np.random.uniform(low=-scale, high=+scale, size=len(a_strat_base))
-    a_strat_rand = a_strat_base + a_rand
-    return(a_strat_rand)
 
 
 #####################
@@ -74,7 +54,20 @@ def circle_dist(a, b):
     '''
     return .5-abs(abs(a-b)-.5)
 
-def get_m_tax(a_buyer_loc, a_seller_loc, gamma, scalar_tax):
+def get_m_tax_dist(a_buyer_loc, a_seller_loc, gamma, scalar_tax):
+    '''
+    Calculates tax matrix and distance matrix.
+    '''
+    # Matrix with absolute dist
+    m_dist = [[circle_dist(buyer_loc, seller_loc)
+        for buyer_loc in a_buyer_loc] for seller_loc in a_seller_loc]
+    # Matrix with rel dist with list of prices. '+ 1' because min dist is 1.
+    # Lot of potential speed up here, only need to do exponent once.
+    m_tax = scalar_tax * np.array(m_dist**gamma) + 1.
+    print(m_tax)
+    return m_tax
+
+def get_m_tax_ordinal(a_buyer_loc, a_seller_loc, gamma, scalar_tax):
     '''
     Calculates tax matrix and distance matrix.
     '''
[…]

### 2019-07-23 code/multiple_bar_plots.py

@@ -45,7 +45,7 @@ def ax_circle_from_data(a_seller_pos, a_buyer_pos, m_quantity_bought, a_color,
         a_xcoord = [r * np.sin(2 * np.pi * a_pos_subset)]
         a_ycoord = [r * np.cos(2 * np.pi * a_pos_subset)]
         ax.scatter(a_xcoord, a_ycoord, marker='x', color=a_color[s], s=80,
-                zorder=2, label='Buyer who bought from Firm %d'%(s+1)) 
+                zorder=2, label='Buyer closest to from Firm %d'%(s+1)) 
     ax.set_xlim(-1.2*r, 1.2*r)
     ax.set_ylim(-1.2*r, 1.5*r)
     ax.legend(loc='center', ncol=2, frameon=False, fontsize=2*fontsize/3,
@@ -166,7 +166,7 @@ def draw_grid_of_timesteps(a_fn, a_index, folder=''):
     a_ax = a_ax_circle + a_ax_bar
     a_ax[::2] = a_ax_circle
     a_ax[1::2] = a_ax_bar
-    a_annote = ['Row {}'.format(i) for i in np.arange(1, len(a_fn) + 1)]
+    #a_annote = ['Row {}'.format(i) for i in np.arange(1, len(a_fn) + 1)]
     for (ax, annote) in zip(a_ax_circle, a_annote):
         ax.annotate(annote,
                 xy          =  (-0.17, 0.5),
@@ -180,7 +180,7 @@ def draw_grid_of_timesteps(a_fn, a_index, folder=''):
     return fig
 
 def write_plot(fig):
-    fn_out = '5x2plot'
+    fn_out = '1x2plot1'
     out_folder = './output/plots/'
     if not os.path.exists(out_folder): os.makedirs(out_folder)
     plt.savefig(out_folder + fn_out + '.png', bbox_inches='tight')
@@ -191,14 +191,15 @@ def write_plot(fig):
 ##############
 
 if __name__ == "__main__":
-    a_fn = ["S=2_B=12_gamma=0.0_scalar_tax=0.05_mean_cost=100_cost_ratio=1.0_endow=120.0_randomize=True.pkl",
-            "S=2_B=12_gamma=0.0_scalar_tax=0.05_mean_cost=100_cost_ratio=1.01_endow=120.0_randomize=True.pkl",
[…]

### 2019-07-23 code/time_plots.py

@@ -4,109 +4,20 @@ import pickle
 import numpy  as np
 import pandas as pd
 import seaborn as sb
+import glob
 from matplotlib import pyplot as plt
 from matplotlib import ticker as tk
 from pprint     import pprint as pp
 from sklearn.externals import joblib as jl
 from itertools  import product,combinations
 from plot_util import customaxis
-from multiple_bar_plots import ax_circle_from_data
 
-
-def write_time_plot_from_file(fn):
-
-########
-# DATA #
-########
-    d_load  = jl.load(folder + fn)
-# Data from d_load
-##########################################################
-    scalar_tax          = d_load['scalar_tax'][0]
-    print(scalar_tax)
-    gamma               = d_load['gamma'][0]
-    endowment           = d_load['endowment'][0]
-    num_sellers         = d_load['num_sellers'][0]
-    num_buyers          = d_load['num_buyers'][0]
-    a_buyer_pos         = d_load['a_buyer_loc'][0]
-    a_seller_pos        = d_load['a_seller_loc'][0]
-    m_tax               = d_load['m_tax'][0]
-    a_m_quantity_bought = d_load['m_quantity_bought']
-    pd_quantity         = pd.DataFrame(d_load['a_quantity_nash'])
-    pd_quantity_sold    = pd.DataFrame(d_load['a_quantity_sold'])
-    pd_price            = pd.DataFrame(d_load['a_price_nash'])
-    pd_cost             = pd.DataFrame(np.array(d_load['a_cost']))
-    pd_profit           = pd.DataFrame(d_load['a_profit'])
-    print(pd_cost)
-
-# Data from calculations
-##########################################################
-    pd_num_buyers_per_seller = pd.DataFrame([np.count_nonzero(m_quant, axis=1) for
-        m_quant in a_m_quantity_bought])
-    pd_quantity_unsold      = pd_quantity - pd_quantity_sold
-# Cournot price at Nash quantity (A + n\bar c)/(n+1)
-    pd_cournot              = (endowment + pd_cost.sum(1))/(num_sellers+1)
-
-    num_timesteps           = len(d_load['a_cost']) - 1
-#check for if the stuff ended early
-    if np.isnan(d_load['a_profit'][num_timesteps][0]):
-        num_timesteps = num_timesteps - 1
-
-########
-# PLOT #
-########
-
-    sb.set_style("darkgrid")
-
-# set figure size
[…]

### 2019-07-23 code/turn_model.py

@@ -5,12 +5,29 @@ import model
 import pandas as pd
 import numpy as np
 
+def new_m_tax(m_tax):
+    ret = .9 * (m_tax - 1) + 1
+    return ret
+
 def new_a_cost(a_cost, a_profit):
     a_profit_ratio = a_profit/np.sum(a_profit)
     a_cost_decrease_ratio = 1 - .05*a_profit_ratio
     ret = a_cost_decrease_ratio*a_cost
     print(ret)
     return ret
+
+def a_func_executor(a_func, a_a_key, dic):
+    '''
+    Ensure subfunctions do not do in-place weirdness. NO SIDEEFFECTS PLEASE!
+    '''
+    a_key_ret = []
+    a_data_ret = []
+    for func, a_key in zip(a_func, a_a_key):
+        d_tmp = {key : dic[key] for key in a_key}
+        a_key_ret.append(a_key[0])
+        a_data_ret.append(func(**d_tmp))
+    return a_key_ret, a_data_ret
+
 
 def get_settings_from_dic_ret(dic_ret):
     '''
@@ -24,33 +41,39 @@ def get_settings_from_dic_ret(dic_ret):
             'a_buyer_loc' : dic_ret['a_buyer_loc'],
             'a_cost' : dic_ret['a_cost'],
             'gamma' : dic_ret['gamma'],
-            'scalar_tax' : 1,
+            'scalar_tax' : dic_ret['scalar_tax'],
             'endowment' : dic_ret['endowment'],
             'mean_cost' : dic_ret['mean_cost'],
-            'cost_ratio' : dic_ret['cost_ratio']} 
+            'cost_ratio' : dic_ret['cost_ratio'],
+            'm_tax' : dic_ret['m_tax']} 
     return ret
 
-def turn_dic_from_dic(dic):
+def turn_dic_from_dic(dic, a_func, a_a_keys):
     '''
     Computes a single turn
     '''
-    a_cost = dic['a_cost']
-    a_profit = dic['a_profit']
     a_cost = new_a_cost(a_cost, a_profit)
+    m_tax_new = new_m_tax(m_tax)
+    a_key, a_data = a_func_executor(a_func, a_a_keys, dic)
     d_settings = get_settings_from_dic_ret(dic)
+    for key, data in zip(a_key, a_data):
+        d_settings[key] = data
     d_settings['a_cost'] = a_cost
+    d_settings['m_tax'] = m_tax_new
[…]

### 2019-07-24 code/model.py
more fixes

@@ -200,7 +200,7 @@ def find_payoff_of_mixed_strategy(game, a_nash):
         prob = 1
 # Check how enumerate works
         for strat_ind, player_ind in enumerate(profile):
-https://forums.spacebattles.com/threads/a-better-class-of-criminal-dc-si.394632            prob_player = a_nash[player_ind]
+            prob_player = a_nash[player_ind]
             if prob_player = 0:
                 prob = 0
                 break
@@ -489,12 +489,11 @@ def main(num_sellers=2, num_buyers=6, gamma=0, scalar_tax=1., mean_cost=100, cos
     num_strats = 21 # number of quantity-strategies
     dist = 40 # deviation from cournot that we search for
 # Determine a_cost
-    if cost_ratio == 1.25:
-        mean_cost = 90
     a_cost = get_a_cost_from_ratio(mean_cost, cost_ratio, num_sellers)
     if cost_ratio == 1.01:
-        a_cost = np.array([90., 100])
-    a_cost = np.array([90., 100])
+        a_cost = np.array([99., 100.])
+    if cost_ratio == 1.0:
+        a_cost = np.array([100., 100.])
 # need to fix theoretical Cournot.
     q_min, _ = theoretical_Cournot(1, num_buyers/float(num_sellers),
             min(a_cost), endowment)
@@ -503,6 +502,7 @@ def main(num_sellers=2, num_buyers=6, gamma=0, scalar_tax=1., mean_cost=100, cos
     # Not the best estimate
     a_strat_quantity = np.arange(0, num_buyers*50, 40)
 # Calculate m_tax
+    ordinal = False
     if ordinal:
         m_tax = get_m_tax_ordinal(a_buyer_loc, a_seller_loc, gamma, scalar_tax)
     else:
@@ -527,10 +527,10 @@ def parameter_combination(i):
 # Create combinations
     num_sellers     = [2]
     num_buyers      = [12]
-    gamma           = [0, .5]#np.round(np.linspace(0.0, .3, 11), 3)
-    scalar_tax      = [1.0]
-    mean_cost       = [95]
-    cost_ratio      = [1.0, 1.01, 1.1]#np.round(np.linspace(1.0, 2.0, 11), 3)
+    gamma           = [1.]#np.round(np.linspace(0.0, .3, 11), 3)
+    scalar_tax      = np.round(np.linspace(0.0, 1.0, 11), 3)
+    mean_cost       = [100]
[…]

### 2019-07-25 code/cluster_execution.sh
more fixes

@@ -1,4 +1,4 @@
 
 module load new gcc/4.8.2 python/2.7.14
 
-bsub -n 6 -W 24:00 -R "rusage[mem=6000]" -J "Cournot[1-16]" "python -W ignore model.py \$LSB_JOBINDEX "
+bsub -n 6 -W 24:00 -R "rusage[mem=6000]" -J "Cournot[1-22]" "python -W ignore model.py \$LSB_JOBINDEX "

### 2019-07-25 code/model.py

@@ -63,7 +63,7 @@ def get_m_tax_dist(a_buyer_loc, a_seller_loc, gamma, scalar_tax):
         for buyer_loc in a_buyer_loc] for seller_loc in a_seller_loc]
     # Matrix with rel dist with list of prices. '+ 1' because min dist is 1.
     # Lot of potential speed up here, only need to do exponent once.
-    m_tax = scalar_tax * np.array(m_dist**gamma) + 1.
+    m_tax = scalar_tax * (np.array(m_dist)**gamma) + 1.
     print(m_tax)
     return m_tax
 
@@ -77,7 +77,7 @@ def get_m_tax_ordinal(a_buyer_loc, a_seller_loc, gamma, scalar_tax):
     # Matrix with rel dist with list of prices. '+ 1' because min dist is 1.
     m_rel_dist = np.argsort(m_dist, axis=0) + 1.
     # Lot of potential speed up here, only need to do exponent once.
-    m_tax = scalar_tax * (np.array(m_rel_dist**gamma) - 1.) + 1.
+    m_tax = scalar_tax * (np.array(m_rel_dist)**gamma - 1.) + 1.
     print(m_tax)
     return m_tax
 
@@ -201,11 +201,11 @@ def find_payoff_of_mixed_strategy(game, a_nash):
 # Check how enumerate works
         for strat_ind, player_ind in enumerate(profile):
             prob_player = a_nash[player_ind]
-            if prob_player = 0:
+            if prob_player == 0:
                 prob = 0
                 break
             prob = prob * prob_seller
-        if prob = 0:
+        if prob == 0:
             continue
         for seller_ind in range(num_players):
             a_payoff[player_ind] = prob * game[profile][player_ind]
@@ -506,7 +506,7 @@ def main(num_sellers=2, num_buyers=6, gamma=0, scalar_tax=1., mean_cost=100, cos
     if ordinal:
         m_tax = get_m_tax_ordinal(a_buyer_loc, a_seller_loc, gamma, scalar_tax)
     else:
-        m_tax = get_m_tax_dist(a_buyer_loc, a_seller_loc, scalar_tax)
+        m_tax = get_m_tax_dist(a_buyer_loc, a_seller_loc, gamma, scalar_tax)
     d_write = make_dic_of_pure_nash(num_sellers, num_buyers, a_strat_quantity,
[…]

### 2019-07-25 writing/shortNote/shortnote.tex
Added shortnote.tex

% document settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[final,5p,times,twocolumn,11pt]{elsarticle}

% standard packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{empheq} 
\usepackage{comment}
\usepackage{enumerate}
\usepackage{setspace}
\usepackage[inline,shortlabels]{enumitem}

% other packages 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{balance} 					% to balance the last columns 
\usepackage[usenames,dvipsnames]{color} 	% to get color with fancy colornames
\usepackage{floatpag} 					% remove page number for figure that covers entire page
\usepackage{bbm}						% for indicator function with \mathbbm{1}
\usepackage[normalem]{ulem} 				% for tables
\useunder{\uline}{\ul}{} 					% for tables

% some settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\numberwithin{equation}{section} % numerates equations according to sections	
\linespread{1.2} 		           % space between lines

 % bibilography settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\biboptions{sort&compress} % cite as [1,2,3] and not [3,1,2] etc.

% bug fix in elsearticle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\def\@author#1{\g@addto@macro\elsauthors{\normalsize%
    \def\baselinestretch{1}%
    \upshape\authorsep#1\unskip\textsuperscript{%
      \ifx\@fnmark\@empty\else\unskip\sep\@fnmark\let\sep=,\fi
      \ifx\@corref\@empty\else\unskip\sep\@corref\let\sep=,\fi
      }%
    \def\authorsep{\unskip,\space}%
    \global\let\@fnmark\@empty
    \global\let\@corref\@empty  %% Added
    \global\let\sep\@empty}%
    \@eadauthor={#1}
}
\makeatother

% This removes the Preprint `submitted to "Journal_name"' footnote.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty 
 \let\@evenhead\@empty
 \def\@oddfoot{}%
 \let\@evenfoot\@oddfoot}
 \makeatother

 % specify the colors of links
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[table,xcdraw,svgnames]{xcolor}
\usepackage[colorlinks]{hyperref}
\AtBeginDocument{%
  \hypersetup{
    citecolor=SteelBlue,
    linkcolor=SteelBlue,   
    urlcolor=SteelBlue}
   }

  % shortcuts & makros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\red}[1]{\textcolor{WildStrawberry}{#1}} 					%  red text
\newcommand{\pd}[2]{ \frac{\partial #1}{\partial #2}} 						% first partial derivative
\newcommand{\pdt}[2]{\frac{\partial^2 #1}{\partial #2^2}} 					% second partial derivative 
\newcommand{\td}[2]{ \frac{\mathrm{d} #1}{\mathrm{d} #2}}				 % first total derivative
\newcommand{\tdt}[2]{ \frac{\mathrm{d}^2 #1}{\mathrm{d} #2^2}}			 % second total derivative
\newcommand{\nt}[3]{\int \limits_{#1}^{#2} \mathrm{d}#3~} 				% integral with boundaries
\newcommand{\dd}{\mathrm{d}} 									% differential d
\newcommand{\ord}[1]{\mathcal{O} \left( #1 \right)} 						% Landau
\newcommand{\mw}[1]{\left< #1 \right>} 								% mean value
\newcommand{\expt}[2]{\mathbb{E}_{#2} \left[ #1 \right]}					% expectation value
\newcommand{\exptn}[3]{\mathbb{E}_{#2}^{(#3)} \left[ #1 \right]}			% n-th order expectation value
\newcommand{\exptc}[3]{\mathbb{E}_{#2} \left[ #1 ~ \left|  #3 \right. \right]} 	% conditional expectation value

% title, authors and affiliations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\journal{~}
\begin{document}
\begin{frontmatter}

\title{Why a digital tax may be the only sustainable solution}

\author[add1]{Nate Dwyer}
\ead{nate9799@gmail.com}

\author[add1]{Sandro Claudio Lera}
\ead{slera@mit.edu}

\author[add1]{Alex `Sandy' Pentland}
\ead{sandy@media.mit.edu}

\address[add1]{\scriptsize Massachusetts Institute of Technology, 77 Massachusetts Avenue, 02139 Cambridge, Massachusetts, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{frontmatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
Over time, new innovations have drastically lowered the cost of transactions.
This has had many positive effects, including increasing trade and wealth while
reducing inequities between cities and rural areas. Unfortunately,
as the transaction costs get very close to 0, monopolization and centralization
of firms becomes more likely and more profitable. This holds especially true
with technology companies, who have very low transaction costs, and are easy to
scale up. Recently, France imposed a  digital tax of 3\% [details here]. The
new French tax could serve as part of a strategy to prevent firms becoming
monopoly powers.

To see what impact extremely low transaction costs could have, we developed a
model that puts a cost on transactions proportional to the distance between a
buyer-seller pair. In this model, sellers can choose different prices and
different capacities, which allows us to model sellers modifying prices and
capacities to compensate for differing transaction costs. For example, a seller
trying to grab a larger market share might lower their prices, while a seller
close to a lot of buyers might want to produce more than a seller that is only
near a few.

\section{Model Definition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Our model of buyers and sellers takes place on some world with a distance
metric (e.g. a country using road distance) and studies how sellers respond to
reductions in distance based transaction costs.

To model distance based transaction costs, we need a concept of distance.  In
the real world, we could use physical distance, but in our model, we place the
buyers and sellers on a circle of circumference 1 and use the arc distance.
We then use that distance as the basis for the transaction cost, treating it as
if it were a percentage tax. More specifically, the transaction cost $t$ for
buyer $b$ to buy from seller $s$ is $p_s * \lambda d(b, s)$, where $p_s$ is the
price $s$ offers, $d(b, s)$ is the distance between buyer $b$ and seller $s$,
and $\lambda$ is a scaling factor. Lowering $\lambda$ is how we model
decreasing transaction costs.

Each buyer has an individual demand curve that is negatively sloped, meaning
that the more expensive the product, the less the buyer purchases. Buyers also
always buy the from the cheapest available seller.

To separate fit sellers from unfit sellers, we use assign sellers differing
cost-per-unit values, with more competitive sellers having lower cost-per-unit
values than less competitive sellers.

@Sandro: Should I even include the math parts?

On the circle, the sellers will play a two step game (known as a
Kreps-Schienkman game) where each seller $s$ will first determine and announce
their capacity $\hat q_s$ (the maximum amount of product they can sell), then
determine and announce their price $p_s$. They choose their capacity and price
trying to maximize their profit $$\Pi = p_sq_s - c_s\hat q_s,$$ where $q_s$ is
the quantity the seller actually sells, and $c_s$ is the cost-per-unit.

\section{Results}
We can see in Figure [blank] that as $\lambda$ gets closer to 0, the more fit
company is able to sell to more buyers, and eventually become a dominant
market force. [add actual numbers here.] This is despite only a 1\% lower
cost-per-unit.

When $\lambda$ is present but not too large, we have healthy competition
without seeing competitors being run out of business.

\section{Iterating the Model}
This difference becomes even more apparent when we iterate the model and
include a feedback mechanism. In such a game, a small initial advantage could
lead to rapid monopolization when there is no friction in the market, such as
transaction costs. However, in a market with some, small transaction costs, the
two firms can stay competitive and neither firm will become the monopoly power.

\section{Conclusion}

At MIT, we are currently developing a new form of taxation that leverages
benefits of digital market place with this mechanism. We hope to still capture
all of the benefits of low transaction costs, including increased trade and
fairness, while at the same time reducing the ability and incentive for sellers
with transaction costs close to 0.

\end{document}

### 2019-07-27 writing/shortNote/shortnote.tex
Changed short note text.

@@
 
+\section{Side Notes}
+Since we are now using a physical distance instead of an ordinal distance, when $\lambda$ is high, the transaction cost can be more important than the cost-per-unit in determining profit and relative fitness of firms.
+
+In addition, our model may not be an accurate descriptor of how a tech company works, as it would seem more accurate for tech companies to have a very low or no per-unit-costs, instead having high fixed costs.
+
 \end{document}

### 2019-07-27 code/multiple_bar_plots.py

@@ -23,7 +23,6 @@ def ax_circle_from_data(a_seller_pos, a_buyer_pos, m_quantity_bought, a_color,
 # Setup
     if ax is None:
         _, ax = plt.subplots()
-    ax.set_title(label='$\gamma$ = {}'.format(gamma))
     num_sellers = len(a_seller_pos)
 # plot a grey circle 
     r       = 1
@@ -167,6 +166,7 @@ def draw_grid_of_timesteps(a_fn, a_index, folder=''):
     a_ax[::2] = a_ax_circle
     a_ax[1::2] = a_ax_bar
     #a_annote = ['Row {}'.format(i) for i in np.arange(1, len(a_fn) + 1)]
+    '''
     for (ax, annote) in zip(a_ax_circle, a_annote):
         ax.annotate(annote,
                 xy          =  (-0.17, 0.5),
@@ -174,35 +174,31 @@ def draw_grid_of_timesteps(a_fn, a_index, folder=''):
                 fontsize    =  fontsize,
                 ha          = 'left',
                 va          = 'top' )
+    '''
     [draw_ax2_from_a_dic(d_load, index, ax_circle, ax_bar) for
             (d_load,index,ax_circle,ax_bar) in zip(a_d_load, a_index,
                 a_ax_circle, a_ax_bar)]
     return fig
 
-def write_plot(fig):
-    fn_out = '1x2plot1'
+def write_plot(fig, fn):
     out_folder = './output/plots/'
     if not os.path.exists(out_folder): os.makedirs(out_folder)
-    plt.savefig(out_folder + fn_out + '.png', bbox_inches='tight')
-    plt.show()
+    plt.savefig(out_folder + fn + '.png', bbox_inches='tight')
 
 ##############
 ### SCRIPT ###
 ##############
 
 if __name__ == "__main__":
-    a_fn = ["S=2_B=12_gamma=0.0_scalar_tax=0.05_mean_cost=100_cost_ratio=1.0_endow=120.0_randomize=True.pkl"]
-            #"S=2_B=12_gamma=0.0_scalar_tax=0.05_mean_cost=100_cost_ratio=1.01_endow=120.0_randomize=True.pkl",
-            #"S=2_B=12_gamma=0.5_scalar_tax=1.0_mean_cost=100_cost_ratio=1.0_endow=120.0_randomize=True.pkl",
[…]

### 2019-07-28 writing/shortNote/main.tex
New shortnote, with pictures. Please read whatsapp.

--- 2019-07-27 writing/shortNote/shortnote.tex
@@
 
-Each buyer has an individual demand curve that is negatively sloped, meaning
-that the more expensive the product, the less the buyer purchases. Buyers also
-always buy the from the cheapest available seller.
+Each buyer has an individual, linear demand curve that is negatively sloped,
+meaning that the more expensive the product, the less the buyer purchases.
+Buyers also always buy the from the cheapest available seller.
 
@@
 \section{Results}
-We can see in Figure [blank] that as $\lambda$ gets closer to 0, the more fit
-company is able to sell to more buyers, and eventually become a dominant
-market force. [add actual numbers here.] This is despite only a 1\% lower
-cost-per-unit.
+We can see in Figure \ref{fig:no_tax}, where $\lambda=0$ and there is no
+transaction cost, that Firm 1 is able to make 33\% more profit despite only a
+1\% lower cost-per-unit. But in Figure \ref{fig:no_tax}, where there is a
+significant transaction cost of $\lambda = .4$, the difference in profits
+is much closer, with Firm 1 only earning 8\% more than firm 2, with the same
+1\% difference in costs. This decrease in monopolization comes at a great cost
+though, as both firm's profit in the first scenario is significantly higher
+than in the second.
 
-When $\lambda$ is present but not too large, we have healthy competition
-without seeing competitors being run out of business.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=\textwidth/2]{no_tax.png}
+	\caption{The trade-offs of the transaction costs are demonstrated.
+		This figure depicts an economy where the is no distance-based tax.
+In the economy, the profits of both firms are high, but one firm has 33\% larger profits because of a slight advantage in having 1\% cheaper unit costs.}
+	\label{fig:no_tax}
+\end{figure}
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=\textwidth/2]{lambda=4Over10.png}
+	\caption{
+		In contrast to Figure \ref{fig:no_tax}, this figure depicts an economy with a significant transaction cost.
+The profits for both firms are significantly lower, but also are much closer, with Firm 1 earning 8\% more profit, as opposed to 33\% in the previous figure.}
+	\label{fig:lambda=.4}
+\end{figure}
 
@@
 benefits of digital market place with this mechanism. We hope to still capture
-all of the benefits of low transaction costs, including increased trade and
-fairness, while at the same time reducing the ability and incentive for sellers
-with transaction costs close to 0.
+all of the benefits of low transaction costs, including increased trade,
+profit, and  fairness, while at the same time reducing the ability and
+incentive for sellers to monopolize.
 

### 2019-08-03 writing/main paper/main.tex
added first version of the short note. Still needs some proof reading, which I will do tomorrow.

--- 2019-06-25 writing/Paper/main.tex
@@
 Note that usually, it is not optimal for a firm to offer products so cheaply that it can sell to the entire market. 
-It tends to be more profitable to sell a lower quantity locally at a higher price.\green{I don't know if I would go this far here.}
+It tends to be more profitable to sell a lower quantity locally at a higher price.
 
@@
 
-\green{This is the third time we define ordinal distance. We should cut at least
-one}
 For any buyer $b$ and firm $f$, we define the ordinal distance $D = D(b,f)$
@@
 $r$ is a simple scaling coefficient (set to $100\%$ in the remainder of this
-report\green{in teh bar plots, $r=1$}).
+report).
 
@@
 Row 5 finally shows the profit asymmetry obtained in a $\gamma=1/2$ economy where firm $1$'s production cost is $20\%$ lower than firm $2$'s. 
-The equilibrium profit functions determine that firm $1$ makes \red{(@Nate: add number)}-times more profit than firm $2$.
+The equilibrium profit functions determine that firm $1$ makes 6.7 times more profit than firm $2$.
 
@@
 \subsection{A Dynamic Economy} 
+\label{sec:dynamic}
 
-In the previous subsection, we have demonstrated how a distance-tax-free economy disproportionally rewards essentially random, minor differences in firm competitiveness. 
+In the previous subsection, we have demonstrated how a no-transportation-cost economy disproportionally rewards essentially random, minor differences in firm competitiveness. 
 But even more concerningly, the problem does not stay static: 
-This disproportional revenue can be used to further invest in aggressive marketing, thereby increasing the difference between the two firms even more. 
+This disproportional revenue can be used to further under-cut prices, invest in aggressive marketing etc. 
+This increases the difference between the two firms even more. 
 This may ultimately run a firm out of business, despite initially being as competitive as the other firms.
@@
 Firm $1$ starts with an initial production cost that is only $1\%$ below that of firm $2$'s. 
-But then, each of the two firms use their profit to effectively subsidise their costs, allowing them to offer lower prices during the next round. 
-The outcome of this experiment is depicted in figure \ref{fig:dynamic_game},
+But then, each of the two firms use their profit to effectively subsidise their costs, proportional to the revenue they have received. 
+This allows them to offer lower prices during the next round. 
+The outcome of this experiment is depicted in Figure \ref{fig:dynamic_game} both with tax $(\gamma > 0)$ and without tax $(\gamma=0)$. 
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=\textwidth]{dynamic_game}
+	\caption{	The left (right) column depicts a situation of repeated business cycles (`games'), without (with) a distance based idiosyncratic tax, $\gamma=0$ ($\gamma > 0$). 
+			Initially, firm $1$ is able to produce only $1\%$ cheaper than firm $2$. 
+			After each round, the firms use their revenue to subsidies their own prices (or alternatively: reinvest into higher production efficiency, etc.). 
+			We witness in the left column that this essentially drives firm $2$ out of business, as it is is forced to decrease prices as low as firm $1$, in order to stay competitive. 
+			Consequently,  firm $2$'s  profit decreases, until it would ultimately run out of business.
+			If only a minimal distance-based tax is raised $(\gamma=0.1)$, such a scenario can be prevented: 
+			Both firms are able to decrease their prices and remain competitive. 
+			The dashed line in the lower left plot depicts the analytically calculable `Cournot price', i.e. the Nash-equilibrium price in a zero-tax-model.
+			As we can see: the lines almost perfectly match, thus showing that our numerical results are consistent. 
+			}
+	\label{fig:dynamic_game}
+\end{figure}
+We witness that despite an initially marginal difference where firm $1$ is producing the products for only $1\%$ less than firm $2$, if we set $\gamma=0$. 
+Firm $2$ ultimately runs out of business, as it is forced to compete with firm $1$. 
+If $\gamma > 0$, both firms remain competitive. 
+A detailed description of the outcome is found in the figure caption.
+
+Although not shown here, we can deduce from row 5 in Figure \ref{fig:static_game} that even for $\gamma = 1/2$, firm $2$ is ran out of business, if the difference in cost is initially large, as anticipated.
+The only way firm $2$ can survive unconditionally of its competitiveness, is if $\gamma$ is set to effectively infinite. 
+With basic calculus, we can calculate analytically an upper bound $\overline{\gamma}$ at which all firms are selling in effective monopolies (derivation will be shown in an Appendix of a next report).
 
@@
 
-\red{
-mention
-- multiple products
-- fixed location
-- implementation on digital market place
-- vision
-}
+In this report, we have shown that problematic disproportional revenue is generated as our economy converges to a zero-transportation-cost limit. 
+This is essentially rooted in the fact that initially minor (and essentially random) imbalances in product quality reward massively more the marginally cheaper/better product, 
+as no rational agent has any incentive to deviate.
+
+We have then introduced an idiosyncratic buyer-seller distance-based tax, that avoids such disproportional revenue in case the differences in production cost are minor, 
+but at the same time continues to reward competitiveness in the sense of significantly cheaper production costs.
+
+The current state of the paper serves as proof of concept, 
+A lot of work has been devoted to determine the Nash equilibria correctly. 
+Now that everything is set up, we can move forward quickly.
+
+In particular, the following points should still be addressed: 
+\red{@Sandy: please tell us what you think we should focus on}
+
+For now, the tax revenue has not been used. 
+We should implement a targeted redirection of the tax money. 
+We have to be careful that we do not thereby distort the game-theoretical equilibria. 
+So for instance, if we give back the tax revenue directly to the most effected firms (either the richest or the poorest), it essentially distorts their incentives. 
+Funding of new start-ups, or an equal redistribution to customers comes to mind. 
+\red{@Sandy: any practical suggestions?}
+
+A value for $\gamma$ striking an optimal balance between competition and firm protection has to be set. 
+A value too low leads to reward of essentially random, minor production advantages. 
+A value too large dampens competition by protecting firms too much. 
+We will have to find a balance, ideally one that is defined algorithmically and adjusts itself automatically. 
+We can implement one $\gamma$ per product, and continue to consider a single-product economy. 
+Ideally, we can couple it to the tax revenue, once that has been defined.
+
+The requirement that firms and buyers are placed uniformly at random appears unnecessarily restrictive. 
+If we want to impose such a mechanism e.g, on a digital market place such as Amazon, one should give buyers and sellers at least the illusion of having a choice. 
+We can use our simulations to show that the model still holds, if buyers and sellers can chose their location on the circle freely, as long as change happens on time-scales much slower than multiple transactions.
+
+Ultimately, we want to run more realistic simulations of real market places, such as Amazon.
 

### 2019-08-03 writing/short note on digital tax/DigitalTax.tex
added first version of the short note. Still needs some proof reading, which I will do tomorrow.

% document settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[final,5p,times,twocolumn,11pt,authoryear]{elsarticle}

% standard packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{empheq} 
\usepackage{comment}
\usepackage{enumerate}
\usepackage{setspace}
\usepackage[inline,shortlabels]{enumitem}

% other packages 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{balance} 					% to balance the last columns 
\usepackage[usenames,dvipsnames]{color} 	% to get color with fancy colornames
\usepackage{floatpag} 					% remove page number for figure that covers entire page
\usepackage{bbm}						% for indicator function with \mathbbm{1}
\usepackage[normalem]{ulem} 				% for tables
\useunder{\uline}{\ul}{} 					% for tables

% some settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\numberwithin{equation}{section} % numerates equations according to sections	
\linespread{1.2} 		           % space between lines

 % bibilography settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\biboptions{sort&compress} % cite as [1,2,3] and not [3,1,2] etc.

% bug fix in elsearticle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\def\@author#1{\g@addto@macro\elsauthors{\normalsize%
    \def\baselinestretch{1}%
    \upshape\authorsep#1\unskip\textsuperscript{%
      \ifx\@fnmark\@empty\else\unskip\sep\@fnmark\let\sep=,\fi
      \ifx\@corref\@empty\else\unskip\sep\@corref\let\sep=,\fi
      }%
    \def\authorsep{\unskip,\space}%
    \global\let\@fnmark\@empty
    \global\let\@corref\@empty  %% Added
    \global\let\sep\@empty}%
    \@eadauthor={#1}
}
\makeatother

% This removes the Preprint `submitted to "Journal_name"' footnote.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty 
 \let\@evenhead\@empty
 \def\@oddfoot{}%
 \let\@evenfoot\@oddfoot}
 \makeatother

 % specify the colors of links
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[table,xcdraw,svgnames]{xcolor}
\usepackage[colorlinks]{hyperref}
\AtBeginDocument{%
  \hypersetup{
    citecolor=SteelBlue,
    linkcolor=SteelBlue,   
    urlcolor=SteelBlue}
   }

  % shortcuts & makros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\red}[1]{\textcolor{WildStrawberry}{#1}} 					%  red text
\newcommand{\pd}[2]{ \frac{\partial #1}{\partial #2}} 						% first partial derivative
\newcommand{\pdt}[2]{\frac{\partial^2 #1}{\partial #2^2}} 					% second partial derivative 
\newcommand{\td}[2]{ \frac{\mathrm{d} #1}{\mathrm{d} #2}}				 % first total derivative
\newcommand{\tdt}[2]{ \frac{\mathrm{d}^2 #1}{\mathrm{d} #2^2}}			 % second total derivative
\newcommand{\nt}[3]{\int \limits_{#1}^{#2} \mathrm{d}#3~} 				% integral with boundaries
\newcommand{\dd}{\mathrm{d}} 									% differential d
\newcommand{\ord}[1]{\mathcal{O} \left( #1 \right)} 						% Landau
\newcommand{\mw}[1]{\left< #1 \right>} 								% mean value
\newcommand{\expt}[2]{\mathbb{E}_{#2} \left[ #1 \right]}					% expectation value
\newcommand{\exptn}[3]{\mathbb{E}_{#2}^{(#3)} \left[ #1 \right]}			% n-th order expectation value
\newcommand{\exptc}[3]{\mathbb{E}_{#2} \left[ #1 ~ \left|  #3 \right. \right]} 	% conditional expectation value

% title, authors and affiliations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\journal{~}
\begin{document}
\begin{frontmatter}

\title{Idiosyncratic, Ordinal Tax To Sustain a Digital Economy}

\author{Nate Dwyer}

\author{Sandro Claudio Lera\corref{cor1}}
\cortext[cor1]{corresponding author: Sandro Claudio Lera (slera@mit.edu)}

\author{Alex `Sandy' Pentland}

\address{Massachusetts Institute of Technology, 77 Massachusetts Avenue, 02139 Cambridge, Massachusetts, USA}

\begin{abstract}

Recently, the French Senate approved a law that imposes a $3\%$ tax on revenue generated from digital services by companies above a certain size. 
While there is a lot of debate about political consequences of this action, it is actually interesting to reverse the question and instead ask what are the long-term implications of an economy with no such digital tax. 
More generally, we can see a digital task as a special case of products with low or zero physical transportation costs. 
We show from basic economic models that such an economy is prone to monopolisation in that minuscule differences in quality are rewarded disproportionally. 
We then propose a distance-based tax to counter-balance the instabilities induced by low costs of transportation. 
Compared to an obvious tax based on physical (cardinal) distance, we instead show that a ranked (ordinal) distance tax leverages the benefits of digitalisation while keeping the economy stable.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{frontmatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Until not too long ago, people used to live in relatively self-contained tribes or villages. 
Trade would exist mostly for specialised products, whereas basic products such as bread or textiles would be produced locally. 
From the industrial to the technological revolution, more efficient distribution channels have emerged, enabling people to buy almost any product in online stores. 
Orders can be delivered often within one or two days, largely independent of the customer’s physical location. 
Pushing this development to the limit, we arrive at an economy where, at least within country borders, physical distance becomes irrelevant. 
For digital products, this is already reality and in direct contrast to established economic theories like \cite{Isard1954}'s gravity model of trade, stating that trade activity is inversely proportional to physical distance.

To analyse the potential impact of vanishing physical transaction costs, we consider the following model economy: 
Two firms, offering the same product, are competing for a total of $n$ potential buyers. 
Firms and buyers are randomly placed on a one-dimensional ring of length $\ell$ with periodic boundary conditions (figure \ref{fig:topology}). 
Hence, the maximum distance between any buyer and firm is $D=\ell/2$.

Firm $i$ $(i=1,2)$ produces $q_i$ units of the good at unit cost $c_i$ and offers to sell at a price $p_i$. 
Their profit calculates to $\Pi_i = p_i \hat{q}_i - c_i q_i$ where $\hat{q}_i$ is the quantity that is actually sold ($\hat{q}_i \leqslant q_i$).

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.3\textwidth]{topology.pdf}
	\caption{	Ring of length $\ell=1$ representing a `geography', on which we place two firms (circles) and $n=12$ buyers (crosses) at random. 
			Albeit random, here we have picked a balanced configuration where each seller has $n=6$ closest potential customers. 
			Throughout this article, we consider the buyer and firm arrangement fixed as shown here. 
			Any other generic arrangement or geography could be used and would not significantly alter our results.
			The two buyers compete for profit and set their production quantity and offered price according to the Nash equilibrium, 
			taking into consideration the different levels of taxation. 
			}
	\label{fig:topology}
\end{figure}

The buyers cannot buy at price $p_i$, but additionally have to pay a transaction cost $\lambda \cdot D^\gamma$ where $D$ is the idiosyncratic distance between buyer and firm $i$. 
We shall call this the \textit{cardinal tax} from hereon. 
In its most basic form, the gravity model predicts a value of $\gamma=2$, whereas here we have set $\gamma=1$ without loss of the generality of our results. 
The case of zero physical transaction cost is recovered in the limit where the scaling factor $\lambda$ approaches $0$. 
The buyers are all characterised by the same negatively sloped demand curve, $p = u - q$ with $u$ the upper price limit at which no good is bought.
In the remainder of this article, we set $\lambda = 0.1$ and $u = 120$. 
\footnote{
Changing these numbers does not alter the qualitative statements of our results, 
while some of the numbers quoted in figure \ref{fig:results} may change.
}

The two firms choose capacity and price to maximize their respective profit in equilibrium. 
Here, we assume they first compete on capacity, by simultaneously declaring how much of the product they plan to produce; 
next, they compete on price to determine the firms' non-tax prices. 
This process, consisting of these two sub-games, is similar to the games studied by \cite{Kreps1983}.
From a game-theoretical perspective, the major difference is the idiosyncratic tax, which alters the pricing sub-game.
The exact quantity and price offered by each firm are determined as the Nash equilibrium of this two-stage game. 
The firm's strategy-space is thus given by the quantity that they can produce and the prices that they can offer. 
Because of the idiosyncratic structure of the game, which depends on the exact location of buyers and firms, 
it is not possible to determine the Nash equilibrium analytically, for general cases. 
Instead, we use the Gambit library developed by \cite{McKelvey2016} to find the Nash equilibrium numerically. 
To this end, the strategy space of capacities and prices are discretised into a sufficiently fine grid. 
The quantity-price two-step game is solved in reverse order: 
For every choice of quantity, the equilibrium price is determined.
Then, the equilibrium quantity is determined.

As both firms are offering the same good, the only differentiating feature is their cost of production per unit good $c_i$.  
Let us consider the case where both sellers are equally competitive ($c_1 = c_2 = 100$), solve for Nash equilibrium prices and consider their profits. 
We then find that the relative difference in profit between the two sellers is $5\%$ (left bar and left axis in figure \ref{fig:results}). 
The slight difference stems from the fact that we have chosen a relatively homogeneous distribution of buyers and sellers (figure \ref{fig:topology}).
If the distribution of buyers were more irregular, so would be the profits, and the sellers would ultimately move to similar locations, as was already predicted by \cite{Hotelling1929}.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth]{performance}
	\caption{	On the left axis (blue bars), we show the relative difference in profit of the two firms.
			If both sellers have equal production cost, their revenue is similar. 
			This remains true if there is a marginal $1\%$ difference in cost, as long as there is a distance dependent tax. 
			Imbalance in revenue is increased drastically once that tax is removed, but is decreased in case it is replaced by an ordinal tax. 
			Major imbalances in production costs (i.e. competitive advantage) lead to significantly different revenue with and without tax. 
			On the right axis (orange bars), we show the relative difference in total market revenue, as generated by the two firms combined. 
			The revenue is rescaled to a value of $1$ for the case of no tax. 
			All other revenue values are in proportion thereof. 
			While the cardinal tax significantly decreases revenue, the ordinal tax brings it back to a similar level than without any tax. 
			}
	\label{fig:results}
\end{figure}

In case there was no cost of transportation, the difference in profit would be zero by symmetry. 
However, this equality is highly unstable. 
To see this, let us now consider the case where seller $1$ is marginally more competitive ($c_1 = 99, c_2 =100$). 
As long as there is a cost of transportation $(\lambda=0.1)$, the difference in profit merely increases from $5\%$ to $7\%$ (see left axis in figure \ref{fig:results} for a visualisation of this and subsequent results).
But in absence of such a cardinal tax ($\lambda=0$), the difference in revenue amounts to a whopping $33\%$!
This result is particularly bothersome as such profit can be used to further decrease costs of production. 
Either through genuine innovation, or temporary undercutting of prices, the difference in $c_2 - c_1$ is further increased and the second firm is run out of business quickly. 
\footnote{
This claim can be formalised by considering multi-stage games, but is omitted here for brevity.
} 
In general, the outpace of competition is natural and in many cases even desired, as efficiency is to be rewarded. 
However, we stress that a minor, essentially random difference of $1\%$ production cost disproportionally benefited one firm. 
We may rationalise this by going back to the example of self-contained villages from the introduction: 
Once there is no more cost of transportation, the economic agent has little incentive to favour local bread, if bread from another village is just marginally cheaper. 
Monopolisation initiated by minor, random initial differences in quality is thus to be expected.

These ever decreasing (or non-existing) cost of transportation can be counter-balanced by introducing a tax that scales with distance (e.g. a carbon tax). 
An immediate side-effect of such market interference is less consumption and hence decreased revenue for both firms. (second vs. third bar on right axis in figure \ref{fig:results}). 
While decentralised, locally self-contained economies may benefit consumers on a grand scheme, it certainly punishes remote buyers and is susceptible to potentially small changes in location. 
Therefore, we propose to introduce an \textit{ordinal tax} instead. 
For each buyer, the distance to the different sellers is enumerated in increasing order. 
They have a distance of $D=0$ from the physically (cardinally) closest seller, a distance $D=1$ from the second closest, and so forth. 
The advantages of this tax are manifold. 
First, it resolves the issue of remote buyers being worse off. 
Second, it is not susceptible to (small) changes in buyer or seller locations, and hence does not lead to physical centralisation. 
Third, the overall level of revenue is elevated compared to a cardinal tax, as now only remote purchases are taxed (right axis in figure \ref{fig:results}). 
Fourth, marginal differences in quality remain unnoticed, as the difference in production cost does not outweigh taxation costs. 
Fifth, major difference in quality (true competitive advantage), overcomes the tax and rewards the more competitive seller 
(cf. in figure \ref{fig:results} the $50$ times higher revenue in case of a production cost difference of $20\%$).

By tuning the scaling factor $\lambda$ once can interpolate between the two extremes of no transaction cost $(\lambda=0)$ and forced local monopolisation $(\lambda=\infty)$. 
The ordinal tax is similar in spirit to, but more broadly applicable and dynamic than a country-border based tax. 
Most importantly, specialised products are traded without tax ($D=0$ everywhere) such that innovation spreads globally. 
Products that are easy to reproduce remain local, to a degree that is largely controlled by $\lambda$. 
A self-regulating adjustment of $\lambda$ and targeted redistribution of tax money are part of ongoing research.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{References}
\bibliographystyle{apa}
\bibliography{bibliography.bib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2019-08-03 code/plot_util.py

@@ -1,15 +1,9 @@
 
 
+import numpy    as np
+import seaborn  as sb 
 
-# nf          = 3
-# xticks      = np.arange(nf)
-# xticklabels = ['firm %s'i for i in np.arange(1,nf+1)]
-
-# ax.set_xlabel('')
-
-
-
-
+from matplotlib import pyplot as plt 
 import matplotlib.ticker as mtick
 
 def customaxis( ax, 
@@ -217,3 +211,65 @@ def three_y_axes(hi):
                     location    = 1.1, 
                     )    
 
+
+
+def circle_plot( a_seller_pos, a_buyer_pos, a_color=None, seller_ind=None, ax=None ):
+    """
+    Plot a circle of length 2pi and annotate the location of buyers and sellers on that circle. 
+
+    input:
+    -----
+
+    a_seller_pos:       Array of seller locations (values between 0 and 2pi)
+    a_buyer_pos:        Array of buyer locations (values between 0 and 2pi)
+    a_color:            Array of length a_seller_pos, with one color per seller 
+    seller_ind:         If not None, should be for each buyer the index number of the seller they bought from the most. 
+                        This is then used to color the buyers in the same color as the respective sellers. If this 
+                        variable is set to None, all buyers will be plotted in grey. 
+    ax:                 Axis instance to plot into. 
+    """
+
+    # create the plot window and define other plotting related quantities
+    ####################################################################################################################
+    if ax is None:
+
+        fig = plt.figure(figsize=(7,7))
+        ax  = plt.gca()
+
+    if a_color is None: a_color = sb.color_palette("deep",2)
+
+    # plot a grey circle 
+    ####################################################################################################################    
+    r       = 1
+    angles  = np.linspace(0, 2*np.pi, 500)
+    xs      = r * np.sin(angles)                                    
+    ys      = r * np.cos(angles) 
+    ax.plot(xs, ys, color='grey', linestyle='--', zorder=1)
+
+    # plot the seller locations 
+    ####################################################################################################################    
+    for i, s in enumerate(a_seller_pos):                        
+        xcoord = [ r * np.sin( 2*np.pi*s ) ]
+        ycoord = [ r * np.cos( 2*np.pi*s ) ]
+        ax.scatter(xcoord, ycoord, marker='o', facecolor=a_color[i], alpha=0.8, 
[…]

### 2019-08-03 writing/short note on digital tax/DigitalTax.tex
finalised note on digital tax.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{footmisc} 					% multiple references to same footnote
 \usepackage{balance} 					% to balance the last columns 
@@
 While there is a lot of debate about political consequences of this action, it is actually interesting to reverse the question and instead ask what are the long-term implications of an economy with no such digital tax.
-More generally, we can see a digital task as a special case of products with low or zero physical transportation costs. 
-We show from basic economic models that such an economy is prone to monopolisation in that minuscule differences in quality are rewarded disproportionally. 
-We then propose a distance-based tax to counter-balance the instabilities induced by low costs of transportation. 
-Compared to an obvious tax based on physical (cardinal) distance, we instead show that a ranked (ordinal) distance tax leverages the benefits of digitalisation while keeping the economy stable.
+More generally, we can see a digital service as a special case of products with low or zero cost of transportation. 
+With basic economic models we show that an economy with no transportation cost is prone to monopolisation in that minuscule, random differences in quality are rewarded disproportionally. 
+We then propose a distance-based tax to counter-balance the tendencies of random centralisation.  
+Compared to an obvious tax that scales with physical (cardinal) distance, we show that a ranked (ordinal) distance tax leverages the benefits of digitalisation while keeping the economy stable.
 
@@
 From the industrial to the technological revolution, more efficient distribution channels have emerged, enabling people to buy almost any product in online stores. 
-Orders can be delivered often within one or two days, largely independent of the customer’s physical location. 
+Orders can be delivered often within one or two days, independent of the customer’s physical location. 
 Pushing this development to the limit, we arrive at an economy where, at least within country borders, physical distance becomes irrelevant. 
-For digital products, this is already reality and in direct contrast to established economic theories like \cite{Isard1954}'s gravity model of trade, stating that trade activity is inversely proportional to physical distance.
+For digital products and services, this is largely reality, and in direct contrast to established economic theories like \cite{Isard1954}'s gravity model of trade, stating that trade activity is inversely proportional to physical distance.
 
-To analyse the potential impact of vanishing physical transaction costs, we consider the following model economy: 
-Two firms, offering the same product, are competing for a total of $n$ potential buyers. 
-Firms and buyers are randomly placed on a one-dimensional ring of length $\ell$ with periodic boundary conditions (figure \ref{fig:topology}). 
+To analyse the potential impact of vanishing distance-based transaction costs, we consider the following model economy: 
+Two firms offering the same product are competing for a total of $n$ potential buyers. 
+Firms and buyers are randomly placed on a one-dimensional ring of length $\ell$ with periodic boundary conditions (Figure \ref{fig:topology}). 
 Hence, the maximum distance between any buyer and firm is $D=\ell/2$.
-
-Firm $i$ $(i=1,2)$ produces $q_i$ units of the good at unit cost $c_i$ and offers to sell at a price $p_i$. 
-Their profit calculates to $\Pi_i = p_i \hat{q}_i - c_i q_i$ where $\hat{q}_i$ is the quantity that is actually sold ($\hat{q}_i \leqslant q_i$).
 
@@
 	\includegraphics[width=0.3\textwidth]{topology.pdf}
-	\caption{	Ring of length $\ell=1$ representing a `geography', on which we place two firms (circles) and $n=12$ buyers (crosses) at random. 
-			Albeit random, here we have picked a balanced configuration where each seller has $n=6$ closest potential customers. 
+	\caption{	Ring of length $\ell=1$ representing a `geography', on which we place at random two firms (circles) and $n=12$ buyers (crosses). 
+			Here we have picked a balanced configuration where each firm has $n=6$ closest potential customers. 
 			Throughout this article, we consider the buyer and firm arrangement fixed as shown here. 
 			Any other generic arrangement or geography could be used and would not significantly alter our results.
-			The two buyers compete for profit and set their production quantity and offered price according to the Nash equilibrium, 
+			The two firms compete for profit.
+			They set their production quantity and prices according to the Nash equilibrium, 
 			taking into consideration the different levels of taxation. 
@@
 
-The buyers cannot buy at price $p_i$, but additionally have to pay a transaction cost $\lambda \cdot D^\gamma$ where $D$ is the idiosyncratic distance between buyer and firm $i$. 
-We shall call this the \textit{cardinal tax} from hereon. 
-In its most basic form, the gravity model predicts a value of $\gamma=2$, whereas here we have set $\gamma=1$ without loss of the generality of our results. 
-The case of zero physical transaction cost is recovered in the limit where the scaling factor $\lambda$ approaches $0$. 
+Firm $i$ $(i=1,2)$ produces $q_i$ units of the good at unit cost $c_i$ and offers to sell at a price $p_i$. 
+Their profit calculates to $\Pi_i = p_i \hat{q}_i - c_i q_i$ where $\hat{q}_i$ is the quantity that is actually sold ($\hat{q}_i \leqslant q_i$).
+
+The buyers cannot buy at price $p_i$, but additionally have to pay a transaction cost $\lambda \cdot D^\gamma \cdot p_i$ where $D$ is the idiosyncratic distance between a given buyer and firm $i$. 
+From hereon, we shall call this the \textit{cardinal tax}. 
+In its most basic form, the gravity model predicts a value of $\gamma=2$, whereas here we have set $\gamma=1$.  
+\footnote{
+\label{ftn:wlog}
+Changing these numbers does not alter the qualitative statements of our results, 
+while some of the numbers quoted in Figure \ref{fig:results} may change.
+} 
+The case of zero cost of transportation is recovered in the limit where the scaling factor $\lambda$ approaches zero. 
 The buyers are all characterised by the same negatively sloped demand curve, $p = u - q$ with $u$ the upper price limit at which no good is bought.
-In the remainder of this article, we set $\lambda = 0.1$ and $u = 120$. 
-\footnote{
-Changing these numbers does not alter the qualitative statements of our results, 
-while some of the numbers quoted in figure \ref{fig:results} may change.
-}
+In the remainder of this article, we set $\lambda = 0.1$ and $u = 120$. \footref{ftn:wlog}
 
 The two firms choose capacity and price to maximize their respective profit in equilibrium. 
-Here, we assume they first compete on capacity, by simultaneously declaring how much of the product they plan to produce; 
-next, they compete on price to determine the firms' non-tax prices. 
-This process, consisting of these two sub-games, is similar to the games studied by \cite{Kreps1983}.
-From a game-theoretical perspective, the major difference is the idiosyncratic tax, which alters the pricing sub-game.
-The exact quantity and price offered by each firm are determined as the Nash equilibrium of this two-stage game. 
-The firm's strategy-space is thus given by the quantity that they can produce and the prices that they can offer. 
-Because of the idiosyncratic structure of the game, which depends on the exact location of buyers and firms, 
+Here, we assume they first compete on capacity, by simultaneously declaring how many units they produce;
+next, they compete on price, taking into consideration the tax and assuming the location of buyers is known. 
+This process, consisting of these two dependent sub-games, is similar to the game theoretical problems studied by \cite{Kreps1983}, the major difference being the idiosyncratic tax.
+Quantity and price offered by each firm are determined as the Nash equilibrium of this two-stage game. 
+%The firm's strategy-space is thus given by the quantity that they can produce and the prices that they can offer. 
+Because the tax depends on the exact location of buyers and firms, 
 it is not possible to determine the Nash equilibrium analytically, for general cases. 
 Instead, we use the Gambit library developed by \cite{McKelvey2016} to find the Nash equilibrium numerically. 
-To this end, the strategy space of capacities and prices are discretised into a sufficiently fine grid. 
-The quantity-price two-step game is solved in reverse order: 
-For every choice of quantity, the equilibrium price is determined.
-Then, the equilibrium quantity is determined.
+%To this end, the strategy space of capacities and prices are discretised into a sufficiently fine grid. 
+%The quantity-price two-step game is solved in reverse order: 
+%For every choice of quantity, the equilibrium price is determined.
+%Then, the equilibrium quantity is determined.
 
-As both firms are offering the same good, the only differentiating feature is their cost of production per unit good $c_i$.  
-Let us consider the case where both sellers are equally competitive ($c_1 = c_2 = 100$), solve for Nash equilibrium prices and consider their profits. 
-We then find that the relative difference in profit between the two sellers is $5\%$ (left bar and left axis in figure \ref{fig:results}). 
-The slight difference stems from the fact that we have chosen a relatively homogeneous distribution of buyers and sellers (figure \ref{fig:topology}).
-If the distribution of buyers were more irregular, so would be the profits, and the sellers would ultimately move to similar locations, as was already predicted by \cite{Hotelling1929}.
+As both firms are offering the same good, they differ only in their marginal cost of production $c_i$ (and their physical location, as shown in Figure \ref{fig:topology}). 
+Let us consider the case where both firms are equally competitive ($c_1 = c_2 = 100$), solve for Nash equilibrium prices and consider their profits. 
+We find that their relative difference in profit is $5\%$ (see left axis in Figure \ref{fig:results} for a visualisation of this and subsequent results).
+This difference is relatively small as we have chosen a rather homogeneous distribution of buyers and firms (Figure \ref{fig:topology}).
+If the distribution of buyers were more irregular, so would be the profits, and the firms would ultimately move to similar locations, as was already predicted by \cite{Hotelling1929}.
 
@@
 	\caption{	On the left axis (blue bars), we show the relative difference in profit of the two firms.
-			If both sellers have equal production cost, their revenue is similar. 
-			This remains true if there is a marginal $1\%$ difference in cost, as long as there is a distance dependent tax. 
-			Imbalance in revenue is increased drastically once that tax is removed, but is decreased in case it is replaced by an ordinal tax. 
+			If both firms have equal production cost, their revenue is similar. 
+			This remains true if there is a marginal $1\%$ difference in cost, as long as there is a distance dependent cardinal tax. 
+			Imbalance in revenue is increased drastically once that tax is removed, but is decreased again in case it is replaced by an ordinal tax. 
 			Major imbalances in production costs (i.e. competitive advantage) lead to significantly different revenue with and without tax. 
@@
 
-In case there was no cost of transportation, the difference in profit would be zero by symmetry. 
+If there is no cost of transportation, the difference in profit is zero as predicted by symmetry (both firms are exactly equal).
 However, this equality is highly unstable. 
-To see this, let us now consider the case where seller $1$ is marginally more competitive ($c_1 = 99, c_2 =100$). 
-As long as there is a cost of transportation $(\lambda=0.1)$, the difference in profit merely increases from $5\%$ to $7\%$ (see left axis in figure \ref{fig:results} for a visualisation of this and subsequent results).
+To see this, let us now consider the case where firm $1$ is marginally more competitive ($c_1 = 99, c_2 =100$). 
+As long as there is a cost of transportation $(\lambda=0.1)$, the difference in profit merely increases from $5\%$ to $7\%$.
 But in absence of such a cardinal tax ($\lambda=0$), the difference in revenue amounts to a whopping $33\%$!
-This result is particularly bothersome as such profit can be used to further decrease costs of production. 
-Either through genuine innovation, or temporary undercutting of prices, the difference in $c_2 - c_1$ is further increased and the second firm is run out of business quickly. 
+This result is particularly bothersome as this excess profit can be used to further decrease costs of production.
+Either through genuine innovation, or temporary undercutting of prices, the difference between $c_1$ and $c_2$ is further enlarged and the second firm is run out of business quickly. 
 \footnote{
-This claim can be formalised by considering multi-stage games, but is omitted here for brevity.
+This claim can be formalised by considering multi-stage games.
 } 
@@
 These ever decreasing (or non-existing) cost of transportation can be counter-balanced by introducing a tax that scales with distance (e.g. a carbon tax). 
-An immediate side-effect of such market interference is less consumption and hence decreased revenue for both firms. (second vs. third bar on right axis in figure \ref{fig:results}). 
+An immediate side-effect of such market interference is less consumption and hence decreased revenue for both firms. (second vs. third bar on right axis in Figure \ref{fig:results}). 
 While decentralised, locally self-contained economies may benefit consumers on a grand scheme, it certainly punishes remote buyers and is susceptible to potentially small changes in location. 
 Therefore, we propose to introduce an \textit{ordinal tax} instead. 
-For each buyer, the distance to the different sellers is enumerated in increasing order. 
-They have a distance of $D=0$ from the physically (cardinally) closest seller, a distance $D=1$ from the second closest, and so forth. 
+For each buyer, the distance to the different firms is enumerated in increasing order. 
+A buyer has a distance of $D=0$ from the physically (cardinally) closest firm, a distance $D=1$ from the second closest, and so forth. 
 The advantages of this tax are manifold. 
 First, it resolves the issue of remote buyers being worse off. 
-Second, it is not susceptible to (small) changes in buyer or seller locations, and hence does not lead to physical centralisation. 
-Third, the overall level of revenue is elevated compared to a cardinal tax, as now only remote purchases are taxed (right axis in figure \ref{fig:results}). 
+Second, it is not susceptible to (small) changes in buyer or firm locations, and hence does not lead to physical centralisation (profits are exactly equal if $c_1=c_2$). 
+Third, the overall level of revenue is elevated compared to a cardinal tax, as now only remote purchases are taxed (right axis in Figure \ref{fig:results}). 
 Fourth, marginal differences in quality remain unnoticed, as the difference in production cost does not outweigh taxation costs. 
-Fifth, major difference in quality (true competitive advantage), overcomes the tax and rewards the more competitive seller 
-(cf. in figure \ref{fig:results} the $50$ times higher revenue in case of a production cost difference of $20\%$).
+Fifth, major difference in quality (true competitive advantage), overcomes the tax and rewards the more competitive firm 
+(cf. in Figure \ref{fig:results} the $50$ times higher revenue in case of a $20\%$ difference in production cost).
 
-By tuning the scaling factor $\lambda$ once can interpolate between the two extremes of no transaction cost $(\lambda=0)$ and forced local monopolisation $(\lambda=\infty)$. 
-The ordinal tax is similar in spirit to, but more broadly applicable and dynamic than a country-border based tax. 
+The ordinal tax is similar in spirit to, but more dynamic than a country border tax. 
 Most importantly, specialised products are traded without tax ($D=0$ everywhere) such that innovation spreads globally. 
-Products that are easy to reproduce remain local, to a degree that is largely controlled by $\lambda$. 
-A self-regulating adjustment of $\lambda$ and targeted redistribution of tax money are part of ongoing research.
+Products that are easy to produce remain local. 
+Competition is encouraged and independent of a firms location, so there is no a priori protectionism. 
+However, to actually outperform, significant competitive advantages must be present. 
+As such, the ordinal tax acts as a type of centralisation threshold that must be overcome. 
+The value of that threshold is tuned by the scaling factor $\lambda$. 
+One can interpolate between the two extremes of no transportation tax $(\lambda=0)$ and forced local monopolisation $(\lambda=\infty)$. 
+A self-regulating adjustment of $\lambda$ based on different market conditions, targeted redistribution of tax money and a practical implementation of this tax on digital markets are part of ongoing research.
 

### 2019-08-03 writing/short note on digital tax/DigitalTax.tex
adjusted paper based on Nate's feedback.

@@
 More generally, we can see a digital service as a special case of products with low or zero cost of transportation. 
-With basic economic models we show that an economy with no transportation cost is prone to monopolisation in that minuscule, random differences in quality are rewarded disproportionally. 
+With basic economic models we show that an economy with no transportation costs is prone to monopolisation in that minuscule, random differences in quality are rewarded disproportionally. 
 We then propose a distance-based tax to counter-balance the tendencies of random centralisation.  
@@
 Firms and buyers are randomly placed on a one-dimensional ring of length $\ell$ with periodic boundary conditions (Figure \ref{fig:topology}). 
-Hence, the maximum distance between any buyer and firm is $D=\ell/2$.
+Hence, the maximum distance between any buyer and firm is $d=\ell/2$.
 
@@
 	\centering
-	\includegraphics[width=0.3\textwidth]{topology.pdf}
+	\includegraphics[width=0.3\textwidth]{circle_topology}
 	\caption{	Ring of length $\ell=1$ representing a `geography', on which we place at random two firms (circles) and $n=12$ buyers (crosses). 
@@
 
-The buyers cannot buy at price $p_i$, but additionally have to pay a transaction cost $\lambda \cdot D^\gamma \cdot p_i$ where $D$ is the idiosyncratic distance between a given buyer and firm $i$. 
+The buyers cannot buy at price $p_i$, but additionally have to pay a transaction cost $\lambda \cdot d^\gamma \cdot p_i$ where $d$ is the distance between a given buyer and firm $i$. 
 From hereon, we shall call this the \textit{cardinal tax}. 
@@
 next, they compete on price, taking into consideration the tax and assuming the location of buyers is known. 
-This process, consisting of these two dependent sub-games, is similar to the game theoretical problems studied by \cite{Kreps1983}, the major difference being the idiosyncratic tax.
+This process, consisting of these two dependent sub-games, is similar to the game theoretical problems studied by \cite{Kreps1983}, the major difference being the buyer-seller specific tax.
 Quantity and price offered by each firm are determined as the Nash equilibrium of this two-stage game. 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{performance}
+	\includegraphics[width=0.5\textwidth]{performance_histogram}
 	\caption{	On the left axis (blue bars), we show the relative difference in profit of the two firms.

### 2019-08-03 code/plot_util.py

@@ -161,11 +161,6 @@ def plot_with_smart_legend(hi) :
 
 
 
-
-
-
-
-
 def three_y_axes(hi):
 
     _  = plt.figure(figsize=(12,4))
@@ -211,65 +206,3 @@ def three_y_axes(hi):
                     location    = 1.1, 
                     )    
 
-
-
-def circle_plot( a_seller_pos, a_buyer_pos, a_color=None, seller_ind=None, ax=None ):
-    """
-    Plot a circle of length 2pi and annotate the location of buyers and sellers on that circle. 
-
-    input:
-    -----
-
-    a_seller_pos:       Array of seller locations (values between 0 and 2pi)
-    a_buyer_pos:        Array of buyer locations (values between 0 and 2pi)
-    a_color:            Array of length a_seller_pos, with one color per seller 
-    seller_ind:         If not None, should be for each buyer the index number of the seller they bought from the most. 
-                        This is then used to color the buyers in the same color as the respective sellers. If this 
-                        variable is set to None, all buyers will be plotted in grey. 
-    ax:                 Axis instance to plot into. 
-    """
-
-    # create the plot window and define other plotting related quantities
-    ####################################################################################################################
-    if ax is None:
-
-        fig = plt.figure(figsize=(7,7))
-        ax  = plt.gca()
-
-    if a_color is None: a_color = sb.color_palette("deep",2)
-
-    # plot a grey circle 
-    ####################################################################################################################    
-    r       = 1
-    angles  = np.linspace(0, 2*np.pi, 500)
-    xs      = r * np.sin(angles)                                    
-    ys      = r * np.cos(angles) 
-    ax.plot(xs, ys, color='grey', linestyle='--', zorder=1)
-
-    # plot the seller locations 
-    ####################################################################################################################    
-    for i, s in enumerate(a_seller_pos):                        
-        xcoord = [ r * np.sin( 2*np.pi*s ) ]
-        ycoord = [ r * np.cos( 2*np.pi*s ) ]
-        ax.scatter(xcoord, ycoord, marker='o', facecolor=a_color[i], alpha=0.8, 
-                color=a_color[i], s=400, zorder=3, label='Firm %d'%(i+1))
-
-    # for each buyer, find index of his seller
-    ####################################################################################################################
[…]

### 2019-08-04 writing/short note on digital tax/DigitalTax.tex
minor changes in short note.

@@
 We then propose a distance-based tax to counter-balance the tendencies of random centralisation.  
-Compared to an obvious tax that scales with physical (cardinal) distance, we show that a ranked (ordinal) distance tax leverages the benefits of digitalisation while keeping the economy stable.
+Compared to an obvious tax that scales with physical (cardinal) distance, we show that a ranked (ordinal) distance tax leverages the benefits of digitalization while keeping the economy stable.
 
@@
 As long as there is a cost of transportation $(\lambda=0.1)$, the difference in profit merely increases from $5\%$ to $7\%$.
-But in absence of such a cardinal tax ($\lambda=0$), the difference in revenue amounts to a whopping $33\%$!
+But in absence of such a cardinal tax ($\lambda=0$), the difference in profit amounts to a whopping $33\%$!
 This result is particularly bothersome as this excess profit can be used to further decrease costs of production.
-Either through genuine innovation, or temporary undercutting of prices, the difference between $c_1$ and $c_2$ is further enlarged and the second firm is run out of business quickly. 
+Either through genuine innovation, or temporary undercutting of prices, the difference between $c_1$ and $c_2$ is further enlarged and the second firm is eventually run out of business. 
 \footnote{
@@
 Second, it is not susceptible to (small) changes in buyer or firm locations, and hence does not lead to physical centralisation (profits are exactly equal if $c_1=c_2$). 
-Third, the overall level of revenue is elevated compared to a cardinal tax, as now only remote purchases are taxed (right axis in Figure \ref{fig:results}). 
+Third, the overall level of revenue is elevated compared to a cardinal tax, as now only remote purchases $(D > 0)$ are taxed (right axis in Figure \ref{fig:results}). 
 Fourth, marginal differences in quality remain unnoticed, as the difference in production cost does not outweigh taxation costs. 

### 2019-08-05 writing/short note on digital tax/DigitalTax.tex
minor adjustments in the writing.

@@
 
-\title{Idiosyncratic, Ordinal Tax To Sustain a Digital Economy}
+\title{Ordinal Tax To Sustain a Digital Economy}
 
@@
 Recently, the French Senate approved a law that imposes a $3\%$ tax on revenue generated from digital services by companies above a certain size. 
-While there is a lot of debate about political consequences of this action, it is actually interesting to reverse the question and instead ask what are the long-term implications of an economy with no such digital tax.
-More generally, we can see a digital service as a special case of products with low or zero cost of transportation. 
-With basic economic models we show that an economy with no transportation costs is prone to monopolisation in that minuscule, random differences in quality are rewarded disproportionally. 
+While there is a lot of political debate about economic consequences of this action, it is actually interesting to reverse the question: 
+We consider the long-term implications of an economy with no such digital tax. 
+More generally, we can think of digital services as a special case of products with low or zero cost of transportation. 
+With basic economic models we show that a market with no transportation costs is prone to monopolization as minuscule, random differences in quality are rewarded disproportionally. 
 We then propose a distance-based tax to counter-balance the tendencies of random centralisation.  
-Compared to an obvious tax that scales with physical (cardinal) distance, we show that a ranked (ordinal) distance tax leverages the benefits of digitalization while keeping the economy stable.
+Unlike a tax that scales with physical (cardinal) distance, a ranked (ordinal) distance tax leverages the benefits of digitalization while maintaining a stable economy.
 
@@
 
+\section*{Acknowledgements} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+SC Lera acknowledges stimulating discussions with S. Donick.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-08-05 writing/short note on digital tax/DigitalTax.tex
added more paper revisions.

@@
 Until not too long ago, people used to live in relatively self-contained tribes or villages. 
-Trade would exist mostly for specialised products, whereas basic products such as bread or textiles would be produced locally. 
-From the industrial to the technological revolution, more efficient distribution channels have emerged, enabling people to buy almost any product in online stores. 
-Orders can be delivered often within one or two days, independent of the customer’s physical location. 
-Pushing this development to the limit, we arrive at an economy where, at least within country borders, physical distance becomes irrelevant. 
-For digital products and services, this is largely reality, and in direct contrast to established economic theories like \cite{Isard1954}'s gravity model of trade, stating that trade activity is inversely proportional to physical distance.
+Basic products such as bread or textiles were produced locally. 
+Trade primarily existed for specialised products.  
+Over time, from the industrial revolution through present technological advancements, more efficient distribution channels have emerged.
+Online orders are often delivered within a couple days, independent of a customer’s physical location. 
+Extrapolated, this trend leads to an economy where, at least domestically, physical shipping distance becomes irrelevant. 
+For digital products and services, this has largely become a reality and contradicts established economic theories, like \cite{Isard1954}'s gravity model of trade which states that trade activity is inversely proportional to physical distance.
 

### 2019-08-05 writing/short note on digital tax/DigitalTax.tex
more minor changes in the short note.

@@
 Until not too long ago, people used to live in relatively self-contained tribes or villages. 
-Basic products such as bread or textiles were produced locally. 
+Basic products such as bread and textiles were produced locally. 
 Trade primarily existed for specialised products.  
-Over time, from the industrial revolution through present technological advancements, more efficient distribution channels have emerged.
+Over time, from the industrial revolution through present technological advancements in AI, more efficient distribution channels have emerged.
 Online orders are often delivered within a couple days, independent of a customer’s physical location. 
@@
 
-To analyse the potential impact of vanishing distance-based transaction costs, we consider the following model economy: 
+To formally analyse the potential impact of vanishing distance-based transaction costs, we consider the following simple model: 
 Two firms offering the same product are competing for a total of $n$ potential buyers. 

### 2019-08-10 writing/short note on digital tax/DigitalTax.tex
added technical appendix to short note.

@@
 Quantity and price offered by each firm are determined as the Nash equilibrium of this two-stage game. 
-%The firm's strategy-space is thus given by the quantity that they can produce and the prices that they can offer. 
 Because the tax depends on the exact location of buyers and firms, 
-it is not possible to determine the Nash equilibrium analytically, for general cases. 
-Instead, we use the Gambit library developed by \cite{McKelvey2016} to find the Nash equilibrium numerically. 
-%To this end, the strategy space of capacities and prices are discretised into a sufficiently fine grid. 
-%The quantity-price two-step game is solved in reverse order: 
-%For every choice of quantity, the equilibrium price is determined.
-%Then, the equilibrium quantity is determined.
+it is in general not possible to determine the Nash equilibrium analytically. 
+We thus revert to numerical techniques described in \ref{apx:Nash_numerical}.
 
@@
 
-SC Lera acknowledges stimulating discussions with S. Donick.
+S. Lera acknowledges stimulating discussions with S. Donick.
 
@@
 
+\appendix
+\section{Numerical Solution of Nash Equilibrium} 
+\label{apx:Nash_numerical}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to maximise their profit, firms first compete on capacity, by simultaneously declaring how many units they produce.
+Subsequently, they compete on price. 
+This amounts to a two-step game theoretical problem, whereby quantity and price are determined as the Nash equilibrium. 
+Each firm's strategy-space is given by the quantity that they can produce and the prices that they can offer. 
+We use the Gambit library developed by \cite{McKelvey2016} to find this equilibrium numerically. 
+To this end, the strategy space of capacities and prices are discretised into a sufficiently fine grid. 
+The quantity-price two-step game is then solved in reverse order: 
+For every choice of quantity, the equilibrium price is determined.
+Then, the equilibrium quantity is determined. 
+%A detailed description and code is available from the authors upon request.
+
 \end{document}
